### 2010-09-15 intro.tex
Intro and model

\section{Introduction}
The system of Poisson and Nernst-Planck (further denoted PNP) 
equations has been widely
used to describe the charge transport --- which includes the ionic
migration, diffusion, and convection --- in a medium. 
The charge transport process is a key mechanism
for electromechanical transduction in some of the electroactive polymer
(EAP) materials, for instance, in ionic polymer-metal composites (IPMCs)~
\cite{basu1997membrane,shahinpoor2001smartmat,
nasser2002applied,newbury2003intelligent, wallmersperger2007appliedphysics,
pugal2008appliedphysics,pugal2010polymer}.
As the system of equations is nonlinear and for a domain with two
electrodes, the charge concentration differences occur in a very narrow
region near the boundaries, the required computing power for a full
scale domain is, especially in 3D, rather significant. This
requires a mesh that is optimal in terms of calculation time and calculation
error.

The Nernst-Planck equation for a mobile species ---
in this case for counter ions --- and without the convection term is:
\begin{equation}
  \frac{\partial C}{\partial t}+\nabla\cdot(-D\nabla C-z\mu FC\nabla\phi)=0,
  \label{eq:nernst-planck}
\end{equation}
where $C$ is the counter ion concentration, $D$ diffusion, $\mu$ mobility,
$F$ Faraday constant, $\phi$ voltage, and $z$ charge number. The Poisson
equation is
\begin{equation}
  -\nabla^2\phi=\frac{F\rho}{\varepsilon},
  \label{eq:poisson}
\end{equation}
where $\varepsilon$ is an absolute dielectric permittivity and the
charge density $\rho$ is expressed
\begin{equation}
  \rho=C-C_{0}
  \label{eq:rho}
\end{equation}
with $C_{0}$ being a constant anion concentration.

In the following section we give a brief overview of the motivation
of the study and a practical application of the results. 
Thereafter the weak-form~\cite{Hermes-book} derivation of the PNP system of equations
and time dependent adaptive \emph{hp}-FEM solutions of the system is presented
for different adaptivity algorithms. 
Also, advantages of a multi-mesh solution over a single-mesh solution are discussed.

### 2010-09-15 model.tex
Intro and model

\section{Model}
\begin{figure}
  \begin{centering}
  \includegraphics[scale=0.4]{domain}
  \caption{\label{fig:domain} Calculation domain $\Omega\subset\mathbb{R}^2$
  	with boundaries $\partial\Omega_{1\ldots 4}\subset\partial\Omega$.}
  \end{centering}
\end{figure}

The model for solving NPN system is implemented in Hermes2D. In this work
a rectangular 2D domain $\Omega\subset\mathbb{R}^2$ with boundaries 
$\partial\Omega_{1\ldots 4}\subset\partial\Omega$  is considered (see Fig.~\ref{fig:domain}). 
As there is now flow considered in or out of the domain and there is no
constant concentration at the boundaries, zero Neumann boundary conditions are used 
for Eq.~\eqref{eq:nernst-planck}:
\begin{equation}
  -D \frac{\partial C}{\partial n} - z \mu F C \frac{\partial \phi} {\partial n} = 0.
  \label{eq:nernst-planck-boundary}
\end{equation}
As a positive voltage $V_{pos}$ is applied on $\Omega_1$ and $V_{neg}=0$ is applied
on $\Omega_3$, Dirichlet boundary conditions are used for Eq.~\eqref{eq:poisson} for
boundaries $\Omega_1$ and $\Omega_3$:
\begin{eqnarray}
  \phi_{\partial\Omega_1}&=&V_{pos},\\
  \phi_{\partial\Omega_3}&=&0,
  \label{eq:dirichlet}
\end{eqnarray}
and Neumann boundaries for $\Omega_2$ and $\Omega_4$:
\begin{equation}
  \frac{\partial \phi_{\Omega_2}}{\partial n}=\frac{\partial \phi_{\Omega_4}}{\partial n}=0.
\end{equation}

\subsection{Weak form of Poisson-Nernst-Planck system}

To make the derivation of the weak forms more convenient, the following
helper constants will be used: 
\begin{eqnarray}
  K & = &z \mu F,\\
  L&=&\frac{F}{\varepsilon}.
  \label{eq:KL}
\end{eqnarray}
So Eq.~\eqref{eq:nernst-planck} and Eq.~\eqref{eq:poisson} become after 
substituting Eq.~\eqref{eq:rho} and the constants $K$ and $L$:
\begin{eqnarray}
  \frac{\partial C}{\partial t}-D\nabla^2 C-K\nabla\cdot \left(C\nabla\phi\right)&=&0,\label{eq:nernst-planck-2}\\
  -\nabla^2\phi-L\left(C-C_{0}\right)&=&0.\label{eq:poisson-2}
\end{eqnarray}
The boundary condition Eq.~\eqref{eq:nernst-planck-boundary} becomes:
\begin{equation}
  -D\frac{\partial C}{\partial n}-KC\frac{\partial\phi}{\partial n}=0.
  \label{eq:nernst-planck-boundary-2}
\end{equation}
The space for solution is $V=H^1\left(\Omega\right)$ where 
$H^1\left(\Omega\right)=\left\{v\in L^2\left(\Omega\right);\ \nabla v \in \left[L^2\left(\Omega\right)\right]^2\right\}$.
Let's choose a test function $v^C\in V$.
The weak form the Nernst-Planck equation Eq.~\eqref{eq:nernst-planck-2}
is found by multiplying it with the test function $v^C$ and then integrating over the domain~$\Omega$:
\begin{equation}
  \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}
  -\int_{\Omega}D\nabla^2Cv^C d\mathbf{x}-\int_{\Omega}K\nabla C\cdot
  \nabla\phi v^C d\mathbf{x} - \int_{\Omega}KC\nabla^2\phi v^C d\mathbf{x}=0.
  \label{eq:nernst-planck-weak1}
\end{equation}
After adding the weak form of the boundary term 
(Eq.~\eqref{eq:nernst-planck-boundary-2}) and applying
the Green's first identity to the terms that contain Laplacian $\nabla^2$ we get
\begin{eqnarray}
 && \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}+
  D\int_{\Omega}\nabla C\cdot\nabla v^C d\mathbf{x}-
  K\int_{\Omega}\nabla C \cdot \nabla \phi v^C d\mathbf{x}+
  K\int_{\Omega}\nabla\left(Cv^C\right)\cdot \nabla \phi d\mathbf{x}\\
  &&-D\int_{\partial\Omega}\frac{\partial C}{\partial n}v^C d\mathbf{S}-
  \int_{\partial\Omega}K\frac{\partial\phi}{\partial n}Cv^C d\mathbf{S}=0.
  \label{eq:nernst-planck-weak2}
\end{eqnarray}
After expanding the nonlinear term and given that the boundary terms
do not contribute, the weak form becomes
\begin{equation}
  \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}+
  D\int_{\Omega}\nabla C \cdot \nabla v^C d\mathbf{x}-
  K\int_{\Omega}\nabla C \cdot \nabla \phi v^C d\mathbf{x}+
  K\int_{\Omega}\nabla \phi \cdot \nabla C v^C d\mathbf{x}+
  K\int_{\Omega} C \left(\nabla\phi\cdot\nabla v^C\right) d\mathbf{x}=0.
  \label{eq:nernst-planck-weak3}
\end{equation}
As the second and third term cancel out, the final weak from of 
the Nernst-Planck equation is
\begin{equation}
  \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}+
  D\int_{\Omega}\nabla C \cdot \nabla v^C d\mathbf{x}+
  K\int_{\Omega} C \left(\nabla\phi\cdot\nabla v^C\right) d\mathbf{x}=0.
  \label{eq:nernst-planck-weak-final}
\end{equation}
Similarly the weak form of Poisson equation Eq.~\ref{eq:poisson-2}
with a test function $v^\phi\subset V$ is:
\begin{equation}
  -\int_{\Omega}\nabla^2\phi v^\phi d\mathbf{x}-\int_{\Omega}LCv^\phi d\mathbf{x}+
  \int_{\Omega}LC_{0}v^\phi d\mathbf{x}=0.
  \label{eq:poisson-weak1}
\end{equation}
After expanding the $\nabla^2$ terms, the final form becomes
\begin{equation}
  \int_{\Omega}\nabla\phi\cdot\nabla v^\phi d\mathbf{x}-\int_{\Omega}LCv^\phi d\mathbf{x}+
  \int_{\Omega}LC_{0}v^\phi d\mathbf{x}=0.
  \label{eq:poisson-weak-final}
\end{equation}

\subsection{Implementation in Hermes2D}
To implement the system of equations Eq.~\eqref{eq:nernst-planck-weak-final}
and Eq.~\eqref{eq:poisson-weak-final}, the residuals and the Jacobian
matrix must be derived. For that, Crank-Nicolson time stepping was
used
\begin{equation}
  \frac{\partial C}{\partial t} \approx \frac{C^{n+1} - C^n}{\tau},
  \label{eq:cranic}
\end{equation}
where $\tau$ is a time step. For the variables $C^{n+1}$ and $\phi^{n+1}$ the
following notation will be used:
\begin{eqnarray}
  C^{n+1} &=& \sum_{k=1}^{N^C} y_k^{C} v_k^{C}, \label{eq:cnotation}j\\
  \phi^{n+1} &=& \sum_{k=1}^{N^{\phi}} y_k^{\phi} v_k^{\phi}\label{eq:phinotation},
\end{eqnarray}
where $v_k^C$ and $v_k^\phi$ are piecewise polynomial functions in $V$.
Considering the Crank-Nicolson time stepping and the notation~\eqref{eq:cnotation},
the time discretized Eq.~\eqref{eq:nernst-planck-weak-final} becomes
\begin{eqnarray}
  F_i^C\left(Y\right) & = & \int_{\Omega} \frac{C^{n+1}}{\tau}v_i^C d\mathbf{x} - 
  \int_{\Omega} \frac{C^{n}}{\tau}v_i^C d\mathbf{x}\nonumber\\
  &&+\frac 12 \left[D\int_{\Omega} \nabla C^{n+1} \cdot \nabla v_i^C d\mathbf{x}+ 
  	D\int_{\Omega} \nabla C^{n} \cdot \nabla v_i^C d\mathbf{x}\right]\nonumber\\
  &&+ \frac 12 \left[K\int_{\Omega}C^{n+1} \left(\nabla \phi^{n+1} \cdot \nabla v_i^C\right) d\mathbf{x}+
  K\int_{\Omega}C^{n} \left(\nabla \phi^{n} \cdot \nabla v_i^C\right) d\mathbf{x}\right]\label{eq:Fc},
\end{eqnarray}
and in the notation~\eqref{eq:phinotation}, Eq.~\eqref{eq:poisson-weak-final} becomes
\begin{equation}
  F_i^{\phi}\left(Y\right) = \int_{\Omega} \nabla \phi^{n+1} \cdot \nabla v_i^{\phi} d\mathbf{x} 
  - \int_{\Omega} LC^{n+1}v_i^{\phi} d\mathbf{x} + \int_{\Omega} LC_0 v_i^{\phi} d\mathbf{x}.
  \label{eq:Fphi}
\end{equation}
For the implementation the $2\times 2$ Jacobian matrix $DF/DY$ with elements corresponding to
\begin{equation}
  \frac{\partial F_i^C}{\partial y_j^C}, \ \frac{\partial F_i^C}{\partial y_j^{\phi}},\  
  \frac{\partial F_i^{\phi}}{\partial y_j^C}, \ \frac{\partial F_i^{\phi}}{\partial y_j^{\phi}},
\end{equation}
must be derived: 
\begin{eqnarray}
  \frac{\partial F_i^C}{\partial y_j^C} &=& 
  \int_{\Omega} \frac{1}{\tau} v_j^C v_i^C d\mathbf{x} + 
  \frac 12 D\int_{\Omega} \nabla v_j^C \cdot \nabla v_i^C d\mathbf{x}
  + \frac 12 K\int_{\Omega} v_j^C \left(\nabla \phi^{n+1} \cdot \nabla v_i^C\right) d\mathbf{x},\label{eq:dFcdyc}\\
  \frac{\partial F_i^C}{\partial y_j^{\phi}} &=&
  \frac 12 K \int_{\Omega} C^{n+1} \left(\nabla v_j^{\phi} \cdot \nabla v_i^C\right) d\mathbf{x},\\
  \frac{\partial F_i^{\phi}}{\partial y_j^C} &=&
  - \int_{\Omega} L v_j^C v_i^{\phi} d\mathbf{x},\\
  \frac{\partial F_i^{\phi}}{\partial y_j^{\phi}} &=&
  \int_{\Omega} \nabla v_j^{\phi} \cdot \nabla v_i^{\phi} d\mathbf{x}\label{eq:dFphidyphi}.
\end{eqnarray}
In Hermes2D Eq.~\eqref{eq:Fc} and \eqref{eq:Fphi} define the residuum $F$ and
Eq.~\eqref{eq:dFcdyc}---\eqref{eq:dFphidyphi} define the Jacobian matrix $J$.

\subsection{Adaptive multi-mesh solution}

The defined Jacobian $J$ and residuum $F$ can be simply solved in Hermes2D by
using Newton's iteration. However, we were more interested in the automatic
adaptivity and the calculation differences with a single-mesh and multi-mesh.

In case of the single mesh, the same basis function base was used, i.e.
$v_i^\phi=v_i^C$. For multi mesh, the meshes and therefore the basis functions
were different. Regardless of the meshing, automatic adaptivity was applied
during each time step, till the error converged to the acceptable level.
In analogy to the most successful adaptive ODE solvers, Hermes2D uses a pair of 
approximations with different orders of accuracy to obtain this information: 
coarse mesh solution and fine mesh solution. The initial coarse mesh is read 
from the mesh file, and the initial fine mesh is created through its 
global refinement both in $h$ and $p$. For more
information, see~\cite{Hermes-project}. In the calculations, the coarse
mesh solution was not calculated at each time step, but the fine mesh
solution was projected to the coarse mesh by using orthogonal projection. This
yielded better convergence and also faster calculation.

Hermes2D supports 8 different refinement modes, namely,
3 isotropic and 5 anisotropic refinements. The isotropic refinements are
\emph{h}-isotropic (H\_ISO), \emph{p}-isotropic (P\_ISO), \emph{hp}-isotropic (HP\_ISO).
Anisotropic refinement modes are
\emph{h}-anisotropic (H\_ANISO),
\emph{hp}-anisotropic-\emph{h} (HP\_ANISO\_H), \emph{p}-anisotropic (P\_ANISO),
\emph{hp}-anisotropic-p (HP\_ANISO\_P), and \emph{hp}-anisotropic (HP\_ANISO).
Once the refinement mode is selected (by user), Hermes2D selects a particular
refinement scheme from several candiates based on the score. More information
can be found in~\cite{Hermes-project}.

### 2010-09-15 motivation.tex
Intro and model

\section{Motivation}
\begin{figure}
  \begin{centering}
      \includegraphics[scale=0.4]{comsol_conc_volt}
  \caption{\label{fig:comsol-conc-volt}Calculated concentration $C$ and voltage $\phi$
  in a 1D domain $\Omega\subset\mathbb{R}$.
  Dirichlet boundary conditions ($V_{\partial \Omega_1}=0\ V$
  and $V_{\partial \Omega_2}=4\ V$) were
	applied to the Poisson equation Eq.~\eqref{eq:poisson} and Neumann boundaries
	to the Nernst-Planck equation Eq.~\eqref{eq:nernst-planck}.}
  \end{centering}
\end{figure}
Fig.~\ref{fig:comsol-conc-volt} shows a solution for $C$ and $\phi$ in
the time dependent NPN system at $t=0.1\ s$ and $t=3.0\ s$. Solution
constants are shown in Table~\ref{Table:used-constants}.
It can be seen that the solution has two notable characteristics. 
Firstly, $\nabla C$ at $\partial \Omega_2$ is
moving in time, whereas $\nabla C$ at $\partial \Omega_1$ is very
sharp. For the large part of the domain $\Omega$ $\nabla C=0$.
At the same time, $\phi$ is a rather smooth fucntion in $\Omega$.
This clearly makes the choice of mesh for the time dependent NPN
system difficult. By creating a too fine mesh, the problem gets
too big. By choosing a coarser mesh, the calculation error goes up.
Furthermore, from the shape of the solution in Fig.~\ref{fig:comsol-conc-volt}
can be seen that the polynomial degree of the elements in the middle
of the domain $\Omega$ and near the boundaries $\partial \Omega_1,\ \partial \Omega_2$
should be different --- namely higher degree near the boundaries. 
Overall shape of the solutions suggest that
using different meshes for variables $C$ and $\phi$ can be beneficial
in terms of resources and calculation time.

All the aforementioned difficulties can be solved by using
a time dependent adaptive multimesh \emph{hp}-FEM solver.
Automatic time dependent adaptivity in conjuction with \emph{hp}-FEM 
helps to limit the error of the calculations by choosing
a suitable mesh and polynomial degrees of the elements at each time step.
In this work Hermes2D~\cite{Hermes-project} was used to study
the problem size, error convergence and solution time of NPN system 
with different adaptivity algorithms.

\begin{table}
\caption{Constants used in the Poisson-Nernst-Planck system of equations.}
\centering
\label{Table:used-constants}
{
\begin{tabular}{llll}
  \hline \hline
  Constant&Value&Unit&Description\\
  \hline
  $D$&$10\times10^{-11}$&$\frac{m^2}{s}$&Diffusion constant\\
  $z$&1&-&Charge number\\
  $F$&96,485&$\frac{C}{mol}$&Faraday number\\
  $R$&8.31&$\frac{J}{mol\cdot K}$&The gas constant\\
  $\mu\ \left( = \frac{D}{RT}\right)$&$4.11\times 10^{-14}$&$\frac{s}{mol\cdot K}$&Mobility\\
  $C_{0}$&1,200&$\frac{mol}{m^3}$&Anion concentration\\
  $\varepsilon$&0.025&$\frac{F}{m}$&Electric permittivity\\
  \hline
  \hline
\end{tabular}
}
\end{table}

\subsection{Practical application}
IPMCs have been studied in past two decades in view of using them
as noiseless mechanoelectrical or electromechanical transducers.
The advantages of the IPMCs over other electroactive polymer actuators
are low voltage bending, high strains ($>1\%$), and ability to work
in wet environments. A typical IPMC consists of a thin sheet of polymer
(often Nafion or Teflon) which is sandwiched between noble
metal electrodes such as platinum or gold. When fabricated, the polymer 
membrane is saturated with certain solvent and ions, e.g water and $H^+$.
When a voltage is applied to the eletrodes, the counter ions start
migrating due to the imposed electric field. By dragging along the solvent,
the osmotic pressure difference near the electrodes occur which in turn
results in bending of the material (see Fig.~\ref{fig:conceptual}).
\begin{figure}
  \begin{centering}
    \subfloat[~]{\begin{centering}
      \includegraphics[scale=0.6]{IPMC}
      \par\end{centering}}~
    \subfloat[~]{\begin{centering}
      \includegraphics[scale=0.6]{IPMC_bent}
      \par\end{centering}}
  \par\end{centering}
  \caption{\label{fig:conceptual}Conceptual model of the actuation
 	of IPMC. Initial counter ion distribution (a) and
	the distribution and resulting bending after applying a voltage (b).}
\end{figure}
The derived and implemented model helps to predict the actuation of the
material. Furthermore, it is expected that the \emph{hp}-FEM implementation
results in a smaller problem size, thus likely allowing faster calculation
in both 2D and 3D.

### 2010-09-15 pugal-esco2010.tex
Intro and model

\documentclass[letterpaper,3p]{elsarticle}

\journal{Applied Mathematics and Computation}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{subfig}

\begin{document}
\begin{frontmatter}

\title{\emph{hp}-Finite Element Model of Poisson and Nernst-Planck System of Equations}

\author[unrme,tartu]{D.~Pugal}
\ead{david.pugal@gmail.com}

\author[unrmath,czech]{P.~Solin\corref{cor2}}
\ead{solin@unr.edu}

\author[unrme]{K.~J.~Kim\corref{cor1}}
\ead{kwangkim@unr.edu}

\author[tartu]{A.~Aabloo}
\ead{alvo@ut.ee}

\address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
\address[unrmath]{FEM group, Department of Mathematics and Statistics,\\
University of Nevada, Reno, NV, U.S.A.}
\address[czech]{Institute of Thermomechanics, Prague, Czech Republic}
\address[tartu]{Institute of Technology, Tartu University, Estonia}

\cortext[cor1]{Corresponding author}
\cortext[cor2]{Principal correpsonding auhtor}

\begin{abstract}
 In this paper we present a \emph{hp}-finite element
model (\emph{hp}-FEM) of Nernst-Planck and Poisson equation system.
The model is implemented in Hermes2D which is a
space- and space-time adaptive \emph{hp}-FEM solver. The time dependent
adaptivity is used to control the error of the solution. Full mathematical
derivation of the weak formulation of the system of equations and
the solution comparison with a nonadaptive conventional FEM is presented.
Furthermore, we extend the discussion on Hermes3D as a modeling tool that can
help in studying and improving the IPMC materials.
\end{abstract}

\begin{keyword}
  \emph{hp}-FEM \sep Nernst-Planck \sep Poisson \sep weak form
\end{keyword}

\end{frontmatter}

\input{intro}
\input{motivation}
\input{model}
\section{Results}
Some convergence grahps

\section{Conclusion, future works}

\bibliographystyle{elsarticle-num}    % Bibliography: Author-Date system
\bibliography{pugal-esco2010}      % pls. call your database here

\end{document}

### 2010-09-21 results.tex
Started results section, some images

\section{Results}

We ran the calculation for all the adaptivity types 
in both single-mesh and multi-mesh configurations. The following results
were recorded: converged error at each time step, cumulative CPU
time at each time step, and the problem size in terms of number
of degrees of freedoms (NDOFs) at each time step.  
Two types of initial meshes were used --- in case of only \emph{p}-adaptivity,
more refined mesh was used. When also the element size refinement
was enabled (all \emph{h} adaptivity types), very coarse initial mesh
was used. In any case, the initial mesh was loaded at each time step.

Some initial observations
helped to select the graphs for this work --- it would have been unreasonable 
to present all recorded results for each adaptivity type.
First of all, the multi-mesh configuration resulted smaller problem size, faster
calculation, and better or similar error convergence than the single-mesh
configuration for all but HP\_ANISO\_H adaptivity type. In this case
the single-mesh configuration resulted slightly but not significantly
smaller problem size. It must be also noted that in case of isotropic
refinements, only P\_ISO resulted in a reasonable problem size.
Secondly, H\_ISO did not converge very well in terms of the
calculation time and the problem size. The term ``reasonable problem size''
means that the number of degrees of freedom in time converges
to so that $N_{dof}<500$, and the term ``reasonable calculation time''
means that the calculation (step $\tau=0.01\ s$, physical
time $t_{end}=3.0\ s$) time $t$ on a givem system was $t<500\ s$.
Although these parameters are empirical, they are reasonable given
that the most adaptivity modes gave significantly smaller results,
e.g. $t<<500\ s$ and $N_{dof} << 500$.
Therefore the multi-mesh calculation results H\_ISO, H\_ANSIO, P\_ANISO,
HP\_ANISO, HP\_ANISO\_P and the single-mesh calculation results of HP\_ANISO\_H
adaptivity mode are compared. In all cases, the error at each time step remained below
the threshold which were set to $e_{th}=0.5\%$ between the coarse mesh
and fine mesh solutions.

\begin{figure}
  \begin{centering}
  \includegraphics[width=\columnwidth]{cpu}
  \caption{\label{fig:cpu} Cumulative CPU time for different adaptivity modes.}
  \end{centering}
\end{figure}

\begin{figure}
  \begin{centering}
  \includegraphics[width=\columnwidth]{dof}
  \caption{\label{fig:dof} NDOFs at each time step for different adaptivity modes.}
  \end{centering}
\end{figure}

Fig.~\ref{fig:cpu} shows the cumulative CPU time for different adaptivity
modes at each time step. All the calculations were done on the same computer
at similar conditions. Here we see that HP\_ANISO takes the most
resources, which is also expected as this adaptivity mode contains the most
candidates (see XXX) from which the refinement methode is chosen from.
At the same time, HP\_ANISO\_H is the fastest.
Fig.~\ref{fig:dof} shows the NDOFs at each time step for different adaptivity modes.
There we see that the HP\_ANISO results in the smallest problem size. All other
adaptivity modes result in a similar problem size ($N_{dof} \approx 250$), however,
\emph{p}-adaptivity modes P\_ISO and P\_ANISO start off with relatively large $N_{dof}$.

TODO, some conclusions TODO

a) HP\_ANISO is the best in terms of problem size

b) P\_ANISO and P\_ISO are good during most part of the problem, however,
initial time step would benefit from the h adaptivity

c) P\_ISO and HP\_ANISO\_H and HP\_ANISO\_P are the fastest, but here
we have to consider, that P\_ISO starts off from more refined mesh.

### 2010-09-24 results.tex
uncommited changes

@@
 
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=.75\columnwidth]{cphi}
+  \caption{\label{fig:cphi} Concentration $C$
+  and voltage $\phi$ at two different time steps
+  (HP\_ANISO adaptivity was used).}
+  \end{centering}
+\end{figure}
+
 We ran the calculation for all the adaptivity types 
-in both single-mesh and multi-mesh configurations. The following results
-were recorded: converged error at each time step, cumulative CPU
+in both single-mesh and multi-mesh configurations. 
+Example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
+with adaptivity type HP\_ANISO is shown
+in Fig.~\ref{fig:cphi}. The time $t=0.7\ s$ was chosen because
+by that time, some ionic migration has already taken place, i.e.
+concentration gradient near the $\partial\Omega_1$ and
+$\partial\Omega_3$ has formed. The automatic mesh refinements
+at different time steps are clearly visible --- especially
+near the top boundary, where the concentration gradient is
+moving in time (as seen in Fig.~\ref{fig:comsol-conc-volt}).
+
+The following numeric results were recorded for each 
+adaptivity type: converged error at each time step, cumulative CPU
 time at each time step, and the problem size in terms of number
@@
 was used. In any case, the initial mesh was loaded at each time step.
+
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=.8\columnwidth]{mesh}
+  \caption{\label{fig:mesh} Initial coarse mesh (a),
+  	half refined mesh (b) and refined mesh (c). The coarse mesh
+	and refined mesh were used in the initial calcualtions, the latter one
+	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
+	used later to optimize \emph{hp}-adaptive mode solutions.}
+  \end{centering}
+\end{figure}
 
@@
 the single-mesh configuration resulted slightly but not significantly
-smaller problem size. It must be also noted that in case of isotropic
-refinements, only P\_ISO resulted in a reasonable problem size.
+smaller problem size, therefore, single-mesh results of HP\_ANISO\_H
+are considered in further comparisons. It must be also noted that in case of the isotropic
+refinements, only P\_ISO adaptivity mode resulted in a reasonable problem size.
 Secondly, H\_ISO did not converge very well in terms of the
@@
 time $t_{end}=3.0\ s$) time $t$ on a givem system was $t<500\ s$.
-Although these parameters are empirical, they are reasonable given
+Although these parameters are empirical, they serve as an upper limit, given
 that the most adaptivity modes gave significantly smaller results,
 e.g. $t<<500\ s$ and $N_{dof} << 500$.
-Therefore the multi-mesh calculation results H\_ISO, H\_ANSIO, P\_ANISO,
+Therefore, the multi-mesh calculation results H\_ISO, H\_ANSIO, P\_ANISO,
 HP\_ANISO, HP\_ANISO\_P and the single-mesh calculation results of HP\_ANISO\_H
-adaptivity mode are compared. In all cases, the error at each time step remained below
+adaptivity mode will be compared. In all of the cases, the relative 
+error at each time step remained below
 the threshold which were set to $e_{th}=0.5\%$ between the coarse mesh
@@
 Fig.~\ref{fig:cpu} shows the cumulative CPU time for different adaptivity
-modes at each time step. All the calculations were done on the same computer
-at similar conditions. Here we see that HP\_ANISO takes the most
-resources, which is also expected as this adaptivity mode contains the most
-candidates (see XXX) from which the refinement methode is chosen from.
+modes at each time step. All the calculations were done on the same computer.
+Here we see that HP\_ANISO requires the most
+resources which can be understood from the fact that this adaptivity mode has the largest number of 
+candidates (see XXX) from which the refinement methode is chosen.
 At the same time, HP\_ANISO\_H is the fastest.
 Fig.~\ref{fig:dof} shows the NDOFs at each time step for different adaptivity modes.
-There we see that the HP\_ANISO results in the smallest problem size. All other
-adaptivity modes result in a similar problem size ($N_{dof} \approx 250$), however,
-\emph{p}-adaptivity modes P\_ISO and P\_ANISO start off with relatively large $N_{dof}$.
+There we see that the HP\_ANISO results in the smallest problem size --- $N_{dof} \approx 125$. 
+All the other adaptivity modes result in  the problem size approximately ($N_{dof} \approx 300$), 
+however, \emph{p}-adaptivity modes P\_ISO and P\_ANISO start off with relatively large $N_{dof}$.
+We can see from the graphs and also from the Fig.~\ref{fig:mesh} that
+\emph{p}-adaptivity is used for the most part of the problem. The initially high
+$N_{dof}$ for \emph{p}-adaptive modes indicate that only first time steps benefit
+greatly from the \emph{h}-adaptivity. P\_ISO, HP\_ANISO\_H
+and HP\_ANISO\_P are the fastest in terms of CPU time, however, we have to consider
+that P\_ISO  and HP\_ANISO\_P start off from more refined mesh.
 
-TODO, some conclusions TODO
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{refined_cpu}
+  \caption{\label{fig:refined-cpu} Cumulative CPU time for HP\_ANISO and HP\_ANISO\_P
+  with different initial meshes.}
+  \end{centering}
+\end{figure}
 
-a) HP\_ANISO is the best in terms of problem size
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{refined_dof}
+  \caption{\label{fig:refined-dof} NDOFs at each time step for
+  HP\_ANISO and HP\_ANISO\_P with different meshes.}
+  \end{centering}
+\end{figure}
 
-b) P\_ANISO and P\_ISO are good during most part of the problem, however,
-initial time step would benefit from the h adaptivity
+So far we have seen that HP\_ANISO results in the smallest problem size, but takes
+most CPU time. When it comes to a large domain or 3D modeling the problem
+size becomes the most important factor. Therefore, we consider HP\_ANISO the most
+suitable adaptivity type to the given problem. Thus some ways to optimize the time
+factor was considered. We neglected HP\_ANISO\_H as this uses single mesh only
+and for large 3D domains, we believe the multi-mesh approach would be
+more reasonable. The performance of HP\_ANISO\_P with refined mesh and half-refined
+mesh, and performance of HP\_ANISO with unrefined, half-refined, and refined
+meshes was calculated (see Fig.~\ref{fig:mesh}).
+The results are shown in Fig.~\ref{fig:refined-cpu} and Fig.~\ref{fig:refined-dof}.
 
-c) P\_ISO and HP\_ANISO\_H and HP\_ANISO\_P are the fastest, but here
-we have to consider, that P\_ISO starts off from more refined mesh.
+TODO(more explanation) It can be seen that some initial refinemts help to reduce the CPU time,
+however, it increases the problem size.

### 2010-09-28 results.tex
some modifications in figure order in results

@@
   \begin{centering}
-  \includegraphics[width=.75\columnwidth]{cphi}
-  \caption{\label{fig:cphi} Concentration $C$
-  and voltage $\phi$ at two different time steps
-  (HP\_ANISO adaptivity was used).}
+  \includegraphics[width=.8\columnwidth]{mesh}
+  \caption{\label{fig:mesh} Initial coarse mesh (a),
+  	half refined mesh (b) and refined mesh (c). The coarse mesh
+	and refined mesh were used in the initial calcualtions, the latter one
+	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
+	used later to optimize \emph{hp}-adaptive mode solutions.}
   \end{centering}
 \end{figure}
-
 We ran the calculation for all the adaptivity types 
 in both single-mesh and multi-mesh configurations. 
-Example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
-with adaptivity type HP\_ANISO is shown
-in Fig.~\ref{fig:cphi}. The time $t=0.7\ s$ was chosen because
-by that time, some ionic migration has already taken place, i.e.
-concentration gradient near the $\partial\Omega_1$ and
-$\partial\Omega_3$ has formed. The automatic mesh refinements
-at different time steps are clearly visible --- especially
-near the top boundary, where the concentration gradient is
-moving in time (as seen in Fig.~\ref{fig:comsol-conc-volt}).
-
 The following numeric results were recorded for each 
@@
   \begin{centering}
-  \includegraphics[width=.8\columnwidth]{mesh}
-  \caption{\label{fig:mesh} Initial coarse mesh (a),
-  	half refined mesh (b) and refined mesh (c). The coarse mesh
-	and refined mesh were used in the initial calcualtions, the latter one
-	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
-	used later to optimize \emph{hp}-adaptive mode solutions.}
+  \includegraphics[width=.75\columnwidth]{cphi}
+  \caption{\label{fig:cphi} Concentration $C$
+  and voltage $\phi$ at two different time steps
+  (HP\_ANISO adaptivity was used).}
   \end{centering}
 \end{figure}
+Example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
+with adaptivity type HP\_ANISO is shown
+in Fig.~\ref{fig:cphi}. The time $t=0.7\ s$ was chosen because
+by that time, some ionic migration has already taken place, i.e.
+concentration gradient near the $\partial\Omega_1$ and
+$\partial\Omega_3$ has formed. The automatic mesh refinements
+at different time steps are clearly visible --- especially
+near the top boundary, where the concentration gradient is
+moving in time (as seen in Fig.~\ref{fig:comsol-conc-volt}).
 
@@
 however, \emph{p}-adaptivity modes P\_ISO and P\_ANISO start off with relatively large $N_{dof}$.
-We can see from the graphs and also from the Fig.~\ref{fig:mesh} that
+We can see from the graphs and also from the Fig.~\ref{fig:cphi} that
 \emph{p}-adaptivity is used for the most part of the problem. The initially high

### 2010-10-05 results.tex
Results sectioned better

@@
 Two types of initial meshes were used --- in case of only \emph{p}-adaptivity,
-more refined mesh was used. When also the element size refinement
+more refined mesh was used (see Fig.~\ref{fig:mesh}~(a)).
+When also the element size refinement
 was enabled (all \emph{h} adaptivity types), very coarse initial mesh
-was used. In any case, the initial mesh was loaded at each time step.
+was used (see Fig.~\ref{fig:mesh}~(b)). 
+In any case, the initial mesh was loaded at each time step.
 
@@
 
-Some initial observations
-helped to select the graphs for this work --- it would have been unreasonable 
-to present all recorded results for each adaptivity type.
-First of all, the multi-mesh configuration resulted smaller problem size, faster
-calculation, and better or similar error convergence than the single-mesh
-configuration for all but HP\_ANISO\_H adaptivity type. In this case
-the single-mesh configuration resulted slightly but not significantly
-smaller problem size, therefore, single-mesh results of HP\_ANISO\_H
-are considered in further comparisons. It must be also noted that in case of the isotropic
-refinements, only P\_ISO adaptivity mode resulted in a reasonable problem size.
-Secondly, H\_ISO did not converge very well in terms of the
-calculation time and the problem size. The term ``reasonable problem size''
+TODO COMpare ISO and ANiso meshes at some timesteps
+
+\subsection{Adapted meshes and polynomial degrees}
+
+Running the simulation with different adaptivity
+types and meshes showed that the multi-mesh configuration generally results in
+smaller problem size, faster calculation, and better or similar error convergence
+compared to the single-mesh configuration. The only exception was HP\_ANISO\_H
+adaptivity type for which the single mesh configuration resulted slightly
+smaller problem size. It must be also noted that in case of the
+isotropic refinements, only P\_ISO adaptivity mode resulted in a
+reasonable problem size whereas H\_ISO and HP\_ISO did not converge
+very well in terms of the calculation time and the problem size.
+The term ``reasonable problem size''
 means that the number of degrees of freedom in time converges
@@
 e.g. $t<<500\ s$ and $N_{dof} << 500$.
-Therefore, the multi-mesh calculation results H\_ISO, H\_ANSIO, P\_ANISO,
+Some comparisons of problem sizes with a single-mesh configuration
+vs. multi-mesh configurations are shown in: XXX
+
+TODO SHOW SOME SAMPLE MESHES FOR DIFFERENT ADAPTIVITY TYPES
+
+\subsection{Quantitative analysis of different adaptivity types}
+
+Based on the results of the previous subsection, H\_ISO, H\_ANSIO, P\_ANISO,
 HP\_ANISO, HP\_ANISO\_P and the single-mesh calculation results of HP\_ANISO\_H
-adaptivity mode will be compared. In all of the cases, the relative 
+adaptivity mode will be compared in terms of problem size and cumulative
+CPU time. In all of the cases, the relative 
 error at each time step remained below
 the threshold which were set to $e_{th}=0.5\%$ between the coarse mesh
-and fine mesh solutions.
+and fine mesh solutions, therefore the error vs. time plot is not considered.
 

### 2010-10-06 results.tex
Results section rewritten

@@
 in both single-mesh and multi-mesh configurations. 
-The following numeric results were recorded for each 
-adaptivity type: converged error at each time step, cumulative CPU
-time at each time step, and the problem size in terms of number
+The following numerical results were recorded for each 
+adaptivity type: converged relative error, cumulative CPU
+time, and the problem size in terms of number
 of degrees of freedoms (NDOFs) at each time step.  
 Two types of initial meshes were used --- in case of only \emph{p}-adaptivity,
-more refined mesh was used (see Fig.~\ref{fig:mesh}~(a)).
+more refined mesh was used (see Fig.~\ref{fig:mesh}~(b)) to ensure
+the error convergence.
 When also the element size refinement
 was enabled (all \emph{h} adaptivity types), very coarse initial mesh
-was used (see Fig.~\ref{fig:mesh}~(b)). 
-In any case, the initial mesh was loaded at each time step.
+was used (see Fig.~\ref{fig:mesh}~(a)) to let the adaptivity
+algorithm find the most optimal mesh. 
+In both case, the initial mesh was loaded at each time step of the
+calculation.
 
@@
 
-TODO COMpare ISO and ANiso meshes at some timesteps
+The following subsections provide a detailed comparison of
+different adaptivity types and estimate the most suitable
+one for the given problem.
 
-\subsection{Adapted meshes and polynomial degrees}
+\subsection{Optimal adaptivity types}
+
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{singlemulti_dof}
+  \caption{\label{fig:singlemultidof} NDOFs in case 
+  of single-mesh and multi-mesh solutions with HP\_ISO
+  and HP\_ANISO adaptivities. (Notice log Y scale)}
+  \end{centering}
+\end{figure}
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{singlemulti_cpu}
+  \caption{\label{fig:singlemulticpu} CPU times in case
+  of single-mesh and multi-mesh solutions with HP\_ISO
+  and HP\_ANISO adaptivities. (Notice log Y scale)}
+  \end{centering}
+\end{figure}
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=.75\columnwidth]{poly}
+  \caption{\label{fig:poly} Polynomial degree space
+  for $C$ and $\phi$ at $t=0.7\ s$ The color indicates
+  the maximum polynomial degree of the corresponding element.}
+  \end{centering}
+\end{figure}
 
@@
 smaller problem size, faster calculation, and better or similar error convergence
-compared to the single-mesh configuration. The only exception was HP\_ANISO\_H
-adaptivity type for which the single mesh configuration resulted slightly
-smaller problem size. It must be also noted that in case of the
-isotropic refinements, only P\_ISO adaptivity mode resulted in a
-reasonable problem size whereas H\_ISO and HP\_ISO did not converge
-very well in terms of the calculation time and the problem size.
-The term ``reasonable problem size''
-means that the number of degrees of freedom in time converges
+compared to the single-mesh configuration.
+This is well illustrated in Fig.~\ref{fig:singlemultidof} 
+and Fig.~\ref{fig:singlemulticpu}.
+This can be well understood from Fig.~\ref{fig:comsol-conc-volt} --- in the boundary
+regions $\partial \Omega_1$ and $\partial\Omega_3$ the concentration gradient
+is greater than voltage gradient, namely $\nabla C >> \nabla \phi$. Therefore
+refining the mesh for both variables is not reasonable. For instance,
+the solution space with corresponding mesh in case of
+HP\_ANISO at $t=0.7\ s$ is shown in Fig.~\ref{fig:cphi}. The corresponding polynomial
+degree space is shown in Fig.~\ref{fig:poly}. Notice that the adaptive algorithm
+has increased the maximum polynomial degree for $C$ space to 7, however,
+at the same time, maximum polynomial degree for $\phi$ is one. Furthermore,
+the mesh is more refined for $C$.
+For most cases using the multi-mesh results in similar or better CPU time, i.e.
+multi-mesh takes less computational resources. Only excpetion was HP\_ANISO\_H 
+adaptivity type for which the single mesh configuration resulted slightly faster
+calculation time. 
+Based on the results only multi-mesh configurations will be considered
+in the following comparisons.
+
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{isoaniso_dof}
+  \caption{\label{fig:isoanisodof} NDOFs in case 
+  of multi-mesh solutions with H\_ISO, H\_ANISO,
+  HP\_ISO, HP\_ANISO, and single-mesh solution with HP\_ANISO\_H
+  adaptivities. (Notice log Y scale)}
+  \end{centering}
+\end{figure}
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{isoaniso_cpu}
+  \caption{\label{fig:isoanisocpu} CPU times in case 
+  of multi-mesh solutions with H\_ISO, H\_ANISO,
+  HP\_ISO, HP\_ANISO, and single-mesh solution with HP\_ANISO\_H
+  adaptivities. (notice log Y scale)}
+  \end{centering}
+\end{figure}
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{isoanisop_dof}
+  \caption{\label{fig:isoanisopdof} NDOFs in case 
+  of multi-mesh solutions with P\_ISO, P\_ANISO, and
+  HP\_ANISO\_P adaptivities.}
+  \end{centering}
+\end{figure}
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{isoanisop_cpu}
+  \caption{\label{fig:isoanisopcpu} CPU times in case 
+  of multi-mesh solutions with P\_ISO, P\_ANISO, and
+  HP\_ANISO\_P adaptivities.}
+  \end{centering}
+\end{figure}
+To narrow down the list of adaptivity modes for the given problem, first the
+isotropic and anisotropic adaptivities were compared. Here \emph{p}-adaptivity
+modes are compared separately as they use more refined mesh.
+Fig.~\ref{fig:isoanisodof} and Fig.~\ref{fig:isoanisocpu} show the comparison
+of H\_ISO, H\_ANISO, HP\_ISO, HP\_ANISO, and HP\_ANISO\_H modes in terms of CPU time
+and problem size.
+Fig.~\ref{fig:isoanisopdof} and Fig.~\ref{fig:isoanisopcpu} show the similar
+comparsion for the P\_ISO, P\_ANISO, and HP\_ANISO\_P modes.
+Here we see that the anisotropic adaptivities result in a reasonable problem
+size and the problems solve within a reasonable calculation time. It is interesting
+to note that HP\_ANISO results in the smallest problem size. Also, in
+\emph{p}-adaptivity group, HP\_ANISO\_P results in the smallest problem size
+at each time step, whereas P\_ISO and P\_ANISO have a very largy problem size
+during the first time steps of the solution.
+Here the term ``reasonable problem size''
+means here that the number of degrees of freedom in time converges
 to so that $N_{dof}<500$, and the term ``reasonable calculation time''
@@
 e.g. $t<<500\ s$ and $N_{dof} << 500$.
-Some comparisons of problem sizes with a single-mesh configuration
-vs. multi-mesh configurations are shown in: XXX
-
-TODO SHOW SOME SAMPLE MESHES FOR DIFFERENT ADAPTIVITY TYPES
 
@@
 
-Based on the results of the previous subsection, H\_ISO, H\_ANSIO, P\_ANISO,
-HP\_ANISO, HP\_ANISO\_P and the single-mesh calculation results of HP\_ANISO\_H
-adaptivity mode will be compared in terms of problem size and cumulative
-CPU time. In all of the cases, the relative 
+Based on the results of the previous subsection, H\_ANISO, HP\_ANISO,
+and HP\_ANISO\_H from the \emph{hp/h} adaptivity group and HP\_ANISO\_P
+from \emph{p} adaptivity group will be compared
+in terms of problem size and cumulative CPU time. 
+In all of the cases, the relative 
 error at each time step remained below
 the threshold which were set to $e_{th}=0.5\%$ between the coarse mesh
-and fine mesh solutions, therefore the error vs. time plot is not considered.
+and fine mesh solutions, therefore the error vs. time plot will not be considered.
 
@@
   \includegraphics[width=\columnwidth]{cpu}
-  \caption{\label{fig:cpu} Cumulative CPU time for different adaptivity modes.}
+  \caption{\label{fig:cpu} Comparative CPU time for different adaptivity modes.}
   \end{centering}
@@
   \includegraphics[width=\columnwidth]{dof}
-  \caption{\label{fig:dof} NDOFs at each time step for different adaptivity modes.}
+  \caption{\label{fig:dof} Comparative NDOFs at each time step for 
+  different adaptivity modes.}
   \end{centering}
@@
 modes at each time step. All the calculations were done on the same computer.
-Here we see that HP\_ANISO requires the most
-resources which can be understood from the fact that this adaptivity mode has the largest number of 
+Here we see that HP\_ANISO\_H and HP\_ANISO require the most
+resources which can be understood from the fact that these 
+adaptivity modes have the largest number of 
 candidates (see XXX) from which the refinement methode is chosen.
-At the same time, HP\_ANISO\_H is the fastest.
 Fig.~\ref{fig:dof} shows the NDOFs at each time step for different adaptivity modes.
-There we see that the HP\_ANISO results in the smallest problem size --- $N_{dof} \approx 125$. 
-All the other adaptivity modes result in  the problem size approximately ($N_{dof} \approx 300$), 
-however, \emph{p}-adaptivity modes P\_ISO and P\_ANISO start off with relatively large $N_{dof}$.
-We can see from the graphs and also from the Fig.~\ref{fig:cphi} that
-\emph{p}-adaptivity is used for the most part of the problem. The initially high
-$N_{dof}$ for \emph{p}-adaptive modes indicate that only first time steps benefit
-greatly from the \emph{h}-adaptivity. P\_ISO, HP\_ANISO\_H
-and HP\_ANISO\_P are the fastest in terms of CPU time, however, we have to consider
-that P\_ISO  and HP\_ANISO\_P start off from more refined mesh.
+There we see that the HP\_ANISO results in the 
+smallest problem size --- $N_{dof} \approx 125$. 
+All the other adaptivity modes result in the 
+problem size of approximately ($N_{dof} \approx 250$),
 
@@
 
-So far we have seen that HP\_ANISO results in the smallest problem size, but takes
-most CPU time. When it comes to a large domain or 3D modeling the problem
+So far we have seen that HP\_ANISO results in the smallest problem size, but requires
+quite a lot CPU time. At the same time, HP\_ANISO\_P is the fastest, whereas
+it does not result in that small problem. When it comes to a large domain 
+or 3D modeling the problem
 size becomes the most important factor. Therefore, we consider HP\_ANISO the most
 suitable adaptivity type to the given problem. Thus some ways to optimize the time
-factor was considered. We neglected HP\_ANISO\_H as this uses single mesh only
-and for large 3D domains, we believe the multi-mesh approach would be
-more reasonable. The performance of HP\_ANISO\_P with refined mesh and half-refined
+factor will be considered.
+
+The performance of HP\_ANISO\_P with refined mesh and half-refined
 mesh, and performance of HP\_ANISO with unrefined, half-refined, and refined

### 2010-10-07 model.tex
Finished the results section

@@
   \begin{centering}
-  \includegraphics[scale=0.4]{domain}
+  \includegraphics[width=0.2\columnwidth]{domain}
   \caption{\label{fig:domain} Calculation domain $\Omega\subset\mathbb{R}^2$
@@
 
-The model for solving NPN system is implemented in Hermes2D. In this work
-a rectangular 2D domain $\Omega\subset\mathbb{R}^2$ with boundaries 
+The model for solving NPN system is implemented in Hermes.
+A rectangular 2D domain $\Omega\subset\mathbb{R}^2$ with boundaries 
 $\partial\Omega_{1\ldots 4}\subset\partial\Omega$  is considered (see Fig.~\ref{fig:domain}). 
@@
 
-\subsection{Implementation in Hermes2D}
+\subsection{Implementation in Hermes}
 To implement the system of equations Eq.~\eqref{eq:nernst-planck-weak-final}
@@
 \end{eqnarray}
-In Hermes2D Eq.~\eqref{eq:Fc} and \eqref{eq:Fphi} define the residuum $F$ and
+In Hermes Eq.~\eqref{eq:Fc} and \eqref{eq:Fphi} define the residuum $F$ and
 Eq.~\eqref{eq:dFcdyc}---\eqref{eq:dFphidyphi} define the Jacobian matrix $J$.
@@
 
-The defined Jacobian $J$ and residuum $F$ can be simply solved in Hermes2D by
+The defined Jacobian $J$ and residuum $F$ can be simply solved with Hermes by
 using Newton's iteration. However, we were more interested in the automatic
-adaptivity and the calculation differences with a single-mesh and multi-mesh.
+adaptivity to control the error and problem size.
+
+In a traditional low-order FEM, refining an element is not algorithmically complicated,
+and so the most difficult part is to find out what elements should be refined. 
+To do this, various techniques ranging from rigorous guaranteed a-posteriori 
+error estimates to heuristic criteria such as residual error indicators, 
+error indicators based on steep gradients, etc are employed. 
+Unfortunately, none of these approaches are suitable for real-life 
+multiphysics coupled problems or higher-order finite element methods: 
+rigorous guaranteed error estimates only exist for very simple problems 
+(such as linear elliptic PDE), and moreover only for low-order finite elements 
+(such as piecewise linear approximations). These heuristic techniques 
+are not employed in Hermes since they may fail 
+in non-standard situations, and because they lack a 
+transparent relation to the true approximation error.
+In order to obtain fast, usable adaptivity, one has to resort to adaptive \emph{hp}-FEM.
+Automatic adaptivity in the \emph{hp}-FEM is substantially different from adaptivity 
+in low-order FEM, since every element can be refined in many different ways. 
+Fig.~\ref{fig:refinements} shows several illustrative refinement candidates for a fourth-order element.
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=0.5\columnwidth]{refinements}
+  \caption{\label{fig:refinements} Refinement candidates for a fourth-order
+  element.}
+  \end{centering}
+\end{figure}
+The number of possible element refinements is implementation-dependent. 
+In general it is very low in \emph{h} or \emph{p} adaptivity, 
+but much higher in \emph{hp}-adaptivity, and it rises even more when 
+anisotropic refinements are enabled.
+Hermes supports 8 different refinement modes, namely,
+3 isotropic and 5 anisotropic refinements. The isotropic refinements are
+\emph{h}-isotropic (H\_ISO), \emph{p}-isotropic (P\_ISO), \emph{hp}-isotropic (HP\_ISO).
+Anisotropic refinement modes are
+\emph{h}-anisotropic (H\_ANISO),
+\emph{hp}-anisotropic-\emph{h} (HP\_ANISO\_H), \emph{p}-anisotropic (P\_ANISO),
+\emph{hp}-anisotropic-p (HP\_ANISO\_P), and \emph{hp}-anisotropic (HP\_ANISO).
+Once the refinement mode is selected (by user), Hermes selects a particular
+refinement scheme from several candidates based on the score. More information
+can be found in~\cite{Hermes-project}.
 
@@
 during each time step, till the error converged to the acceptable level.
-In analogy to the most successful adaptive ODE solvers, Hermes2D uses a pair of 
+In analogy to the most successful adaptive ODE solvers, Hermes uses a pair of 
 approximations with different orders of accuracy to obtain this information: 
@@
 yielded better convergence and also faster calculation.
-
-Hermes2D supports 8 different refinement modes, namely,
-3 isotropic and 5 anisotropic refinements. The isotropic refinements are
-\emph{h}-isotropic (H\_ISO), \emph{p}-isotropic (P\_ISO), \emph{hp}-isotropic (HP\_ISO).
-Anisotropic refinement modes are
-\emph{h}-anisotropic (H\_ANISO),
-\emph{hp}-anisotropic-\emph{h} (HP\_ANISO\_H), \emph{p}-anisotropic (P\_ANISO),
-\emph{hp}-anisotropic-p (HP\_ANISO\_P), and \emph{hp}-anisotropic (HP\_ANISO).
-Once the refinement mode is selected (by user), Hermes2D selects a particular
-refinement scheme from several candiates based on the score. More information
-can be found in~\cite{Hermes-project}.

### 2010-10-07 results.tex
Finished the results section

@@
   and voltage $\phi$ at two different time steps
-  (HP\_ANISO adaptivity was used).}
+  (HP\_ANISO adaptivity was used). This is a 2D solution shown
+  as in 3D, where the height indicates the value.}
   \end{centering}
@@
 Here the term ``reasonable problem size''
-means here that the number of degrees of freedom in time converges
+means that the number of degrees of freedom in time converges
 to so that $N_{dof}<500$, and the term ``reasonable calculation time''
@@
 
+\subsection{Optimizations}
+
 \begin{figure}
@@
 suitable adaptivity type to the given problem. Thus some ways to optimize the time
-factor will be considered.
+factor will be considered. The desirable output would be HP\_ANISO problem size
+close to HP\_ANISO\_P CPU time. One way to optimize the problem
+is to choose somewhat more refined initial mesh. Other way one could think
+to optimize the problem would be to change
+the refinement frequency in a time dependent way. Recall that up to this point,
+the initial mesh has been loaded in the beginning of each time step. True,
+by employing the optimizations, we already must know something about the problem
+and its solution beforehand. However, it could still be practial when solving a real problem
+in a large domain.
 
-The performance of HP\_ANISO\_P with refined mesh and half-refined
-mesh, and performance of HP\_ANISO with unrefined, half-refined, and refined
-meshes was calculated (see Fig.~\ref{fig:mesh}).
-The results are shown in Fig.~\ref{fig:refined-cpu} and Fig.~\ref{fig:refined-dof}.
+The problem size and CPU time with HP\_ANISO
+and HP\_ANISO\_P adaptivities on more refined initial mesh (see Fig.~\ref{fig:mesh}~(c))
+compared to the coarse initial mesh (Fig.~\ref{fig:mesh}~(a)) and 
+HP\_ANISO\_P solution is shown in Fig.~\ref{fig:refined-cpu} and Fig.~\ref{fig:refined-dof}.
+It can be seen that by using initially more refined mesh, et problem solving time
+can be reduced in case of HP\_ANISO, at the same time, the problem size increases.
+In this situation, HP\_ANISO\_P and HP\_ANISO perform equally well.
 
-TODO(more explanation) It can be seen that some initial refinemts help to reduce the CPU time,
-however, it increases the problem size.
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{unreffreq_dof}
+  \caption{\label{fig:unreffreq-dof} NDOFs at each time step for
+  HP\_ANISO and HP\_ANISO\_P with mesh unrefinement at each time step and at over each
+  	time step after first $0.5\ s$ physical solution time.}
+  \end{centering}
+\end{figure}
+The next proposed optimization involved changing the unrefinement frequency.
+It is known that the concentration gradient $\partial C$ changes the most in the initial phase
+of the calculation, therefore, the unrefinement after each time step was performed
+until $t=0.5\ s$ (physical time). After that, the
+unrefinement was performed in $0.10\ s$ interval.
+It appears that this type
+of optimization does not result in a stable solution, i.e. the problem size 
+does not remain steady, but starts to oscillate depending on the unrefinement
+frequency. This is demonstrated in 
+Fig.~\ref{fig:unreffreq-dof}. Therefore this kind of optimization did not
+prove to be efficient.
+
+\subsection{More general results}
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=.75\columnwidth]{cphiorders}
+  \caption{\label{fig:cphi-orders} Solutions $C$ and $\phi$
+  and corresponding polynomial degrees of the elements at
+  $t=0.7\ s$. HP\_ANISO adaptivity type was used. The height
+  in the solution graphs indicates the value.}
+  \end{centering}
+\end{figure}
+
+Based on the results, cation concentration and voltage was calculated
+for different boundary conditions.
+For instance, when voltage $\phi_{\Omega_1}=0.5\frac{x}{width_{\Omega_1}}+0.5$, the
+concentration gradient $\nabla C$ and the voltage gradient $\nabla \phi$ are no
+longer effectively 1D.
+The calculated $C$ and $\phi$ in $\Omega$ and corresponding meshes and polynomial
+degrees of the elements are shown in Fig.~\ref{fig:cphi-orders}.
+HP\_ANISO adaptivity type was used. Notice that the solution
+is different to the one in Fig.~\ref{fig:cphi} and the adapted mesh and the
+polynomial degrees are also more complicated than in Fig.~\ref{fig:poly}.
+It must be also noted that in case of non uniform boundary conditions which
+results in 2D problem, refined initial mesh is more efficient to use.

### 2010-10-09 conclusions.tex
Draft getting ready

\section{Conclusions}

In this work the system of Nernst-Planck-Poisson equations
was solved using \emph{hp}-finite element method with adaptive
multimesh configuration. The weak form, residuals and
the Jacobian matrix of the system were explicitly derived
and implemented in Hermes \emph{hp}-FEM adaptive solver.
The solution for Nernst-Planck-Poisson
problem with two field variables $C$ and $\phi$ results in 
very different field gradients in the space and time.
Conventional finite element solvers do not provide the means 
how to deal with such problems such that both the error of
the solution and problem size remain small throughout the
time dependent solving process.

It was shown that using time dependent adaptivity, multi-mesh
configuration, and anisotropic \emph{hp} refinements, the problem
size remains acceptably small throughout the solving process.
Namely, hermes refinement modes HP\_ANISO and HP\_ANISO\_P
resulted the smallest and fastest problem, respectively.
At the same time, relative error of the solution was known.
Furthermore, using the multi-mesh configuration for the variables
$C$ and $\phi$ was justified --- the adaptivity algorithm
did not refine the mesh of $\phi$ nor did increase the
polynomial degree throughout the adaptivity process. However,
the mesh was significantly refined for $C$ and also the
maximum polynomial degree was varied in the range of
$2\ldots 9$. So it is efficient to use multi-mesh in terms of
the number of degrees of freedom.

Conclusively, by using \emph{hp}-FEM with adaptive multi-mesh
configuration we can possibly reduce the problem size
of the Nernst-Planck-Poisson equation system significantly while
still maintaining prescribed precision of the solution. 
We believe, and this
is yet to be demonstrated, that this becomes especially
important when dealing with 3D problems with a large physical
domain.

### 2010-10-09 intro.tex
Draft getting ready

@@
 used to describe the charge transport --- which includes the ionic
-migration, diffusion, and convection --- in a medium. 
+migration, diffusion, and convection --- in a material. 
 The charge transport process is a key mechanism
@@
 
-In the following section we give a brief overview of the motivation
-of the study and a practical application of the results. 
+Brief overview of the motivation
+of the study and a practical application of the results is given in the following section. 
 Thereafter the weak-form~\cite{Hermes-book} derivation of the PNP system of equations
 and time dependent adaptive \emph{hp}-FEM solutions of the system is presented
-for different adaptivity algorithms. 
-Also, advantages of a multi-mesh solution over a single-mesh solution are discussed.
+for different refinement modes. 
+Also, advantages of a multi-mesh solution over a single-mesh solution are presented.

### 2010-10-09 model.tex
Draft getting ready

@@
 \section{Model}
+\label{sec:model}
+
 \begin{figure}
@@
 
-The model for solving NPN system is implemented in Hermes.
+The model for solving PNP system is implemented in Hermes.
 A rectangular 2D domain $\Omega\subset\mathbb{R}^2$ with boundaries 
 $\partial\Omega_{1\ldots 4}\subset\partial\Omega$  is considered (see Fig.~\ref{fig:domain}). 
-As there is now flow considered in or out of the domain and there is no
-constant concentration at the boundaries, zero Neumann boundary conditions are used 
+As there is no flow considered into or out from the domain and there is no
+constant concentration at the boundaries, zero Neumann boundary conditions were used 
 for Eq.~\eqref{eq:nernst-planck}:
@@
 \end{equation}
-As a positive voltage $V_{pos}$ is applied on $\Omega_1$ and $V_{neg}=0$ is applied
-on $\Omega_3$, Dirichlet boundary conditions are used for Eq.~\eqref{eq:poisson} for
+As a positive constant voltage $V_{pos}$ was applied on $\Omega_1$ and $V_{neg}=0$ was applied
+on $\Omega_3$, Dirichlet boundary conditions were used for Eq.~\eqref{eq:poisson} for
 boundaries $\Omega_1$ and $\Omega_3$:
@@
 
+The initial more implicit version of the derived weak form of PNP
+was derived in~\cite{pugal2010spie}.
 To make the derivation of the weak forms more convenient, the following
-helper constants will be used: 
+constants are used: 
 \begin{eqnarray}
@@
 and Eq.~\eqref{eq:poisson-weak-final}, the residuals and the Jacobian
-matrix must be derived. For that, Crank-Nicolson time stepping was
+matrix were derived. For that, Crank-Nicolson time stepping was
 used
@@
 
-\subsection{Adaptive multi-mesh solution}
+\subsection{Adaptive multi-mesh solution in Hermes}
 
@@
 \end{figure}
-The number of possible element refinements is implementation-dependent. 
+The number of possible element refinements is implementation dependent. 
 In general it is very low in \emph{h} or \emph{p} adaptivity, 
@@
 \emph{hp}-anisotropic-p (HP\_ANISO\_P), and \emph{hp}-anisotropic (HP\_ANISO).
-Once the refinement mode is selected (by user), Hermes selects a particular
-refinement scheme from several candidates based on the score. More information
-can be found in~\cite{Hermes-project}.
+Due to the large number of refinement options, classical error estimators 
+that provide a constant error estimate per element, cannot be used to 
+guide automatic \emph{hp}-adaptivity. 
+For this, one needs to know the shape of the approximation error.
+Hermes uses a pair of approximations with different orders of accuracy 
+to obtain this information: coarse mesh solution and fine mesh solution. 
+The initial coarse mesh is read from the mesh file, and the initial 
+fine mesh is created through its global refinement both in \emph{h}
+and \emph{p}. The fine mesh solution is the approximation of 
+interest both during the adaptive process and at the end of computation. 
+The coarse mesh solution represents its low-order part.
+Here global orthogonal projection of the fine mesh solution 
+on the coarse mesh was used instead instead of solving on the coarse mesh.
 
-In case of the single mesh, the same basis function base was used, i.e.
-$v_i^\phi=v_i^C$. For multi mesh, the meshes and therefore the basis functions
-were different. Regardless of the meshing, automatic adaptivity was applied
-during each time step, till the error converged to the acceptable level.
-In analogy to the most successful adaptive ODE solvers, Hermes uses a pair of 
-approximations with different orders of accuracy to obtain this information: 
-coarse mesh solution and fine mesh solution. The initial coarse mesh is read 
-from the mesh file, and the initial fine mesh is created through its 
-global refinement both in $h$ and $p$. For more
-information, see~\cite{Hermes-project}. In the calculations, the coarse
-mesh solution was not calculated at each time step, but the fine mesh
-solution was projected to the coarse mesh by using orthogonal projection. This
-yielded better convergence and also faster calculation.
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=0.5\columnwidth]{cand_list_quads}
+  \caption{\label{fig:candlist} Refinement candidates for every
+  refinement mode for quad type elements.}
+  \end{centering}
+\end{figure}
+Refinement mode is selected by a user from among 8 modes listed before.
+Hermes selects a particular
+refinement scheme from several candidates based on the score which is
+calculated as follows
+\begin{equation}
+	s=\frac{\log_{10} e_0 - \log_{10} e}{\left( d_0-d \right)^{\xi}},
+\end{equation}
+where $e$ and $d$ are an estimated error and an estimated
+number of DOF of a candidate respectively, $e_0$ and $d_0$
+are are an estimated error and an estimated number of DOF
+of the examined element, respectively, and $\xi$ is a
+convergence exponent. Here candidate
+refers to a proposed refinement. Fig.~\ref{fig:candlist} shows all the proposed
+refinements for all refinement modes in case of quad elements.
+More information about the refinement modes and technical details
+about the score calculation can be found in~\cite{Hermes-project}.
+
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=0.5\columnwidth]{multimesh1}
+  \caption{\label{fig:multimesh1} Master mesh (A) and 
+  three different meshes for a coupled problem (B)~---~(D),
+  and the virtual union mesh (E).}
+  \end{centering}
+\end{figure}
+\begin{figure}
+  \begin{centering}
+  \includegraphics[width=0.5\columnwidth]{multimesh2}
+  \caption{\label{fig:multimesh2} Integration over an element
+  $Q_k$ of the virtual union mesh and the appropriate subelements
+  of the existing elements where this integration is performed.}
+  \end{centering}
+\end{figure}
+In multiphysics PDE systems such as Poisson-Nernst-Planck system it can 
+happen that one physical field is very smooth whereas other one is not.
+This is well shown in Fig.~\ref{fig:comsol-conc-volt}. 
+If all the fields are approximated on the same mesh, then the necessity 
+to refine the mesh at the steep gradient of a field implies new degrees 
+of freedom for the smooth fields as well. This can be very wasteful.
+Hermes makes it possible to approximate them on individual meshes. 
+These meshes are not completely independent of each other --- they have 
+a common coarse mesh that we call master mesh. The master mesh is 
+there for algorithmic purposes only, it may not even be used for 
+discretization purposes: Every mesh in the system is obtained from 
+it via an arbitrary sequence of elementary refinements. 
+This is illustrated in Fig.~\ref{fig:multimesh1}, where (A) is the master mesh, 
+(B)~---~(D) three different meshes (say, for a coupled problem with three equations),
+and (E) is the virtual union mesh that is used for assembling.
+The union mesh is not constructed physically in the computer 
+memory --- it merely serves as a hint to correctly transform  the 
+integration points while integrating over sub-elements of an elements 
+of the existing meshes. Fig.~\ref{fig:multimesh2} shows the integration
+over an element $Q_k$ of the virtual union mesh.
+As a result, the multimesh discretization of the PDE system is 
+monolithic in the sense that no physics is lost --- all integrals 
+in the discrete weak formulations are evaluated exactly up to 
+the error in the numerical quadrature.

### 2010-10-09 motivation.tex
Started results section, some images
Draft getting ready

@@
   \begin{centering}
-      \includegraphics[scale=0.4]{comsol_conc_volt}
+      \includegraphics[]{comsol_conc_volt}
   \caption{\label{fig:comsol-conc-volt}Calculated concentration $C$ and voltage $\phi$
@@
 moving in time, whereas $\nabla C$ at $\partial \Omega_1$ is very
-sharp. For the large part of the domain $\Omega$ $\nabla C=0$.
+large. For the most part of the domain $\Omega$ $\nabla C=0$.
 At the same time, $\phi$ is a rather smooth fucntion in $\Omega$.
-This clearly makes the choice of mesh for the time dependent NPN
-system difficult. By creating a too fine mesh, the problem gets
-too big. By choosing a coarser mesh, the calculation error goes up.
+This clearly makes the choice of the mesh for the time dependent NPN
+system difficult. By choosing a too fine mesh, the problem gets
+too big. By choosing a coarse mesh, the calculation error might
+get too large.
 Furthermore, from the shape of the solution in Fig.~\ref{fig:comsol-conc-volt}
@@
 of the domain $\Omega$ and near the boundaries $\partial \Omega_1,\ \partial \Omega_2$
-should be different --- namely higher degree near the boundaries. 
-Overall shape of the solutions suggest that
+should be different --- namely higher degree elements near the boundaries
+and lower degree element in the middle of domain. 
+Overall shape of the solutions also suggest that
 using different meshes for variables $C$ and $\phi$ can be beneficial
-in terms of resources and calculation time.
+in terms of number of degrees of freedom and calculation time.
 
-All the aforementioned difficulties can be solved by using
+All the aforementioned concerns can be solved by using
 a time dependent adaptive multimesh \emph{hp}-FEM solver.
 Automatic time dependent adaptivity in conjuction with \emph{hp}-FEM 
-helps to limit the error of the calculations by choosing
+helps to limit the error of the calculations by automatically choosing
 a suitable mesh and polynomial degrees of the elements at each time step.
-In this work Hermes2D~\cite{Hermes-project} was used to study
-the problem size, error convergence and solution time of NPN system 
-with different adaptivity algorithms.
+In this work Hermes~\cite{Hermes-project} was used to implement
+the PNP system and study
+the problem size, error convergence and solution time 
+with different refinement modes.
 
@@
 results in a smaller problem size, thus likely allowing faster calculation
-in both 2D and 3D.
+in both 2D and 3D domains.

### 2010-10-09 pugal-esco2010.tex
Started results section, some images
Finished the results section
Draft getting ready

@@
 model (\emph{hp}-FEM) of Nernst-Planck and Poisson equation system.
-The model is implemented in Hermes2D which is a
+The model is implemented in Hermes which is a
 space- and space-time adaptive \emph{hp}-FEM solver. The time dependent
@@
 \input{model}
-\section{Results}
-Some convergence grahps
+\input{results}
+\input{conclusions}
 
-\section{Conclusion, future works}
+\section*{Acknowledgments}
+KJK thanks the financial support from the Office of Naval Research under Award N000140910218.
 

### 2010-10-09 results.tex
Draft getting ready

@@
   	half refined mesh (b) and refined mesh (c). The coarse mesh
-	and refined mesh were used in the initial calcualtions, the latter one
+	and refined mesh were used in the initial calculations, the latter one
 	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
-	used later to optimize \emph{hp}-adaptive mode solutions.}
+	used later to optimize the \emph{hp}-adaptive refinement solutions.}
   \end{centering}
 \end{figure}
-We ran the calculation for all the adaptivity types 
+Calculation for all the refinement modes were performed
 in both single-mesh and multi-mesh configurations. 
 The following numerical results were recorded for each 
-adaptivity type: converged relative error, cumulative CPU
+refinement mode: converged relative error, cumulative CPU
 time, and the problem size in terms of number
@@
 Two types of initial meshes were used --- in case of only \emph{p}-adaptivity,
-more refined mesh was used (see Fig.~\ref{fig:mesh}~(b)) to ensure
+more refined mesh was used (Fig.~\ref{fig:mesh}~(c)) to ensure
 the error convergence.
-When also the element size refinement
-was enabled (all \emph{h} adaptivity types), very coarse initial mesh
+When the element size refinement
+was also enabled (all \emph{h}/\emph{hp} refinement modes), very coarse initial mesh
 was used (see Fig.~\ref{fig:mesh}~(a)) to let the adaptivity
-algorithm find the most optimal mesh. 
-In both case, the initial mesh was loaded at each time step of the
+algorithm find the most optimal mesh. So coarse initial mesh might not be
+suitable for all the practical applications, as will be demonstrated in the
+end of this section, however, it provides a good insight into the
+adaptivity performance of Hermes.
+In both cases, the initial mesh was loaded at each time step of the
 calculation.
@@
   (HP\_ANISO adaptivity was used). This is a 2D solution shown
-  as in 3D, where the height indicates the value.}
+  as in 3D, where the height indicates the values of $C$ and $\phi$.}
   \end{centering}
@@
 Example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
-with adaptivity type HP\_ANISO is shown
+with refinement mode HP\_ANISO is shown
 in Fig.~\ref{fig:cphi}. The time $t=0.7\ s$ was chosen because
@@
 $\partial\Omega_3$ has formed. The automatic mesh refinements
-at different time steps are clearly visible --- especially
+at different time steps are clearly visible in the figure --- especially
 near the top boundary, where the concentration gradient is
-moving in time (as seen in Fig.~\ref{fig:comsol-conc-volt}).
+moving in time (as was also seen in Fig.~\ref{fig:comsol-conc-volt}).
 
 The following subsections provide a detailed comparison of
-different adaptivity types and estimate the most suitable
+the different refinement modes and try to estimate the most suitable
 one for the given problem.
 
-\subsection{Optimal adaptivity types}
+\subsection{Optimal refinement modes}
 
@@
   of single-mesh and multi-mesh solutions with HP\_ISO
-  and HP\_ANISO adaptivities. (Notice log Y scale)}
+  and HP\_ANISO refinements. (Notice log Y scale)}
   \end{centering}
@@
 
-Running the simulation with different adaptivity
-types and meshes showed that the multi-mesh configuration generally results in
-smaller problem size, faster calculation, and better or similar error convergence
+Running the simulation with different refinement modes 
+and meshes showed that the multi-mesh configuration generally results in
+a smaller problem, faster calculation, and better or similar error convergence
 compared to the single-mesh configuration.
@@
 and Fig.~\ref{fig:singlemulticpu}.
-This can be well understood from Fig.~\ref{fig:comsol-conc-volt} --- in the boundary
+The result can be understood from Fig.~\ref{fig:comsol-conc-volt} --- in the boundary
 regions $\partial \Omega_1$ and $\partial\Omega_3$ the concentration gradient
 is greater than voltage gradient, namely $\nabla C >> \nabla \phi$. Therefore
-refining the mesh for both variables is not reasonable. For instance,
+refining the mesh for both variables is not reasonable in terms of
+number of degrees of freedom. For instance,
 the solution space with corresponding mesh in case of
@@
 has increased the maximum polynomial degree for $C$ space to 7, however,
-at the same time, maximum polynomial degree for $\phi$ is one. Furthermore,
-the mesh is more refined for $C$.
+at the same time, the maximum polynomial degree for the $\phi$ space is one. Furthermore,
+the mesh is significantly more refined for $C$.
 For most cases using the multi-mesh results in similar or better CPU time, i.e.
 multi-mesh takes less computational resources. Only excpetion was HP\_ANISO\_H 
-adaptivity type for which the single mesh configuration resulted slightly faster
+refinement mode for which the single mesh configuration resulted slightly faster
 calculation time. 
-Based on the results only multi-mesh configurations will be considered
+Based on the results, only multi-mesh configurations will be considered
 in the following comparisons.
@@
   HP\_ISO, HP\_ANISO, and single-mesh solution with HP\_ANISO\_H
-  adaptivities. (Notice log Y scale)}
+  refinement modes. (Notice log Y scale)}
   \end{centering}
@@
   HP\_ISO, HP\_ANISO, and single-mesh solution with HP\_ANISO\_H
-  adaptivities. (notice log Y scale)}
+  refinement modes. (notice log Y scale)}
   \end{centering}
@@
   of multi-mesh solutions with P\_ISO, P\_ANISO, and
-  HP\_ANISO\_P adaptivities.}
+  HP\_ANISO\_P refinement modes.}
   \end{centering}
@@
   of multi-mesh solutions with P\_ISO, P\_ANISO, and
-  HP\_ANISO\_P adaptivities.}
+  HP\_ANISO\_P refinement modes.}
   \end{centering}
 \end{figure}
-To narrow down the list of adaptivity modes for the given problem, first the
-isotropic and anisotropic adaptivities were compared. Here \emph{p}-adaptivity
-modes are compared separately as they use more refined mesh.
+To narrow down the list of refinement modes for the given problem, first the
+isotropic and anisotropic adaptivities were compared. The \emph{p}-adaptivity
+modes were compared separately as they used more refined mesh (Fig.~\ref{fig:mesh}~(c)).
 Fig.~\ref{fig:isoanisodof} and Fig.~\ref{fig:isoanisocpu} show the comparison
@@
 comparsion for the P\_ISO, P\_ANISO, and HP\_ANISO\_P modes.
-Here we see that the anisotropic adaptivities result in a reasonable problem
+It can be clearly seen that the anisotropic refinement modes result in a reasonable problem
 size and the problems solve within a reasonable calculation time. It is interesting
@@
 Although these parameters are empirical, they serve as an upper limit, given
-that the most adaptivity modes gave significantly smaller results,
-e.g. $t<<500\ s$ and $N_{dof} << 500$.
+that the most refinement modes give significantly smaller results:
+$t<<500\ s$ and $N_{dof} << 500$.
 
-\subsection{Quantitative analysis of different adaptivity types}
+\subsection{Quantitative analysis of the refinement modes}
 
-Based on the results of the previous subsection, H\_ANISO, HP\_ANISO,
-and HP\_ANISO\_H from the \emph{hp/h} adaptivity group and HP\_ANISO\_P
-from \emph{p} adaptivity group will be compared
+Based on the results in the previous subsection, H\_ANISO, HP\_ANISO,
+and HP\_ANISO\_H from the \emph{hp/h}-adaptivity group and HP\_ANISO\_P
+from \emph{p}-adaptivity group will be compared
 in terms of problem size and cumulative CPU time. 
@@
 the threshold which were set to $e_{th}=0.5\%$ between the coarse mesh
-and fine mesh solutions, therefore the error vs. time plot will not be considered.
+and fine mesh solutions, therefore the error-time plot will not be considered.
 
@@
   \includegraphics[width=\columnwidth]{cpu}
-  \caption{\label{fig:cpu} Comparative CPU time for different adaptivity modes.}
+  \caption{\label{fig:cpu} Comparative CPU time for different refinement modes.}
   \end{centering}
@@
   \caption{\label{fig:dof} Comparative NDOFs at each time step for 
-  different adaptivity modes.}
+  different refinement modes.}
   \end{centering}
@@
 
-Fig.~\ref{fig:cpu} shows the cumulative CPU time for different adaptivity
+Fig.~\ref{fig:cpu} shows the cumulative CPU time for different refinement 
 modes at each time step. All the calculations were done on the same computer.
@@
 resources which can be understood from the fact that these 
-adaptivity modes have the largest number of 
-candidates (see XXX) from which the refinement methode is chosen.
-Fig.~\ref{fig:dof} shows the NDOFs at each time step for different adaptivity modes.
-There we see that the HP\_ANISO results in the 
+refinement modes have the largest number of 
+candidates (see Section.~\ref{sec:model}) from which the refinement method is chosen.
+At the same time, HP\_ANISO\_P is the fastest among all the other refinement modes.
+Fig.~\ref{fig:dof} shows the NDOFs at each time step.
+It can be seen that the HP\_ANISO results in the 
 smallest problem size --- $N_{dof} \approx 125$. 
-All the other adaptivity modes result in the 
-problem size of approximately ($N_{dof} \approx 250$),
+All the other refinement modes result in a 
+problem size of approximately ($N_{dof} \approx 250$). So we have
+two notable refinement modes --- HP\_ANISO\_P because of the fast
+solution, and HP\_ANISO because of the small problem size. In the following
+subsection, optimization of those two modes will be considered.
 
-\subsection{Optimizations}
+\subsection{Optimizations of HP\_ANISO and HP\_ANISO\_P refinement modes}
 
@@
 So far we have seen that HP\_ANISO results in the smallest problem size, but requires
-quite a lot CPU time. At the same time, HP\_ANISO\_P is the fastest, whereas
-it does not result in that small problem. When it comes to a large domain 
-or 3D modeling the problem
+quite a lot CPU time compared to HP\_ANISO\_P that is the fastest.
+When it comes to a large domain or 3D modeling the problem
 size becomes the most important factor. Therefore, we consider HP\_ANISO the most
-suitable adaptivity type to the given problem. Thus some ways to optimize the time
+suitable refinement mode to the given problem. Thus some ways to optimize the time
 factor will be considered. The desirable output would be HP\_ANISO problem size
@@
 to optimize the problem would be to change
-the refinement frequency in a time dependent way. Recall that up to this point,
+the refinement frequency during the solving process. Recall that up to this point,
 the initial mesh has been loaded in the beginning of each time step. True,
@@
 HP\_ANISO\_P solution is shown in Fig.~\ref{fig:refined-cpu} and Fig.~\ref{fig:refined-dof}.
-It can be seen that by using initially more refined mesh, et problem solving time
+By using initially more refined mesh, the problem solving time
 can be reduced in case of HP\_ANISO, at the same time, the problem size increases.
@@
 The next proposed optimization involved changing the unrefinement frequency.
-It is known that the concentration gradient $\partial C$ changes the most in the initial phase
+It is known that the concentration gradient $\nabla C$ changes the most in the initial phase
 of the calculation, therefore, the unrefinement after each time step was performed
 until $t=0.5\ s$ (physical time). After that, the
-unrefinement was performed in $0.10\ s$ interval.
-It appears that this type
-of optimization does not result in a stable solution, i.e. the problem size 
+unrefinement was performed in $\Delta t = 0.10\ s$ interval.
+However, this optimization did not result in a stable solution, i.e. the problem size 
 does not remain steady, but starts to oscillate depending on the unrefinement
-frequency. This is demonstrated in 
-Fig.~\ref{fig:unreffreq-dof}. Therefore this kind of optimization did not
-prove to be efficient.
+frequency. This is shown in 
+Fig.~\ref{fig:unreffreq-dof}.
+
+Therefore varying the unrefinement frequency will
+not likely result in desired results in real applications for given system of equation.
+At the same time, by varying a mesh size, optimal initial mesh could be found
+for both HP\_ANISO and HP\_ANISO\_P refinement modes.
 
@@
   and corresponding polynomial degrees of the elements at
-  $t=0.7\ s$. HP\_ANISO adaptivity type was used. The height
+  $t=0.7\ s$. HP\_ANISO refinement mode was used. The height
   in the solution graphs indicates the value.}
@@
 for different boundary conditions.
-For instance, when voltage $\phi_{\Omega_1}=0.5\frac{x}{width_{\Omega_1}}+0.5$, the
-concentration gradient $\nabla C$ and the voltage gradient $\nabla \phi$ are no
+For instance, when voltage is applied as follows
+\begin{equation}
+  \phi_{\Omega_1}=0.5\frac{x}{width_{\Omega_1}}+0.5,
+\end{equation}
+the concentration gradient $\nabla C$ and the voltage gradient $\nabla \phi$ are no
 longer effectively 1D.
@@
 degrees of the elements are shown in Fig.~\ref{fig:cphi-orders}.
-HP\_ANISO adaptivity type was used. Notice that the solution
+HP\_ANISO refinement mode was used. Notice that the solution
 is different to the one in Fig.~\ref{fig:cphi} and the adapted mesh and the
 polynomial degrees are also more complicated than in Fig.~\ref{fig:poly}.
-It must be also noted that in case of non uniform boundary conditions which
-results in 2D problem, refined initial mesh is more efficient to use.
+It must be noted that in case of non uniform boundary conditions which
+results in 2D problem, refined initial mesh was more efficient to use.
+
+\emph{
+PAVEL: Should I try to include the similar solution from comsol and do
+some comparison here? I got this idea just before commiting the final
+draft to you?}

### 2010-10-11 pugal-esco2010.tex
Minor changes (address etc).

@@
 
-\title{\emph{hp}-Finite Element Model of Poisson and Nernst-Planck System of Equations}
+\title{\emph{hp}-Finite Element Model of Poisson and Nernst-Planck\\ System of Equations}
 
@@
 \address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
-\address[unrmath]{FEM group, Department of Mathematics and Statistics,\\
+\address[unrmath]{Department of Mathematics and Statistics,
 University of Nevada, Reno, NV, U.S.A.}
@@
 \cortext[cor1]{Corresponding author}
-\cortext[cor2]{Principal correpsonding auhtor}
+\cortext[cor2]{Principal corresponding author}
 

### 2010-10-11 intro.tex
Work on the first two pages.

@@
 \section{Introduction}
-The system of Poisson and Nernst-Planck (further denoted PNP) 
-equations has been widely
-used to describe the charge transport --- which includes the ionic
-migration, diffusion, and convection --- in a material. 
-The charge transport process is a key mechanism
-for electromechanical transduction in some of the electroactive polymer
-(EAP) materials, for instance, in ionic polymer-metal composites (IPMCs)~
+
+Ionic Polymer-Metal Composites (IPMC) have been studied during the past two 
+decades for their potential to serve as noiseless mechanoelectrical and electromechanical transducers.
+The advantages of IPMC over other electroactive polymer actuators
+are low voltage bending, high strains ($>1\%$), and an ability to work
+in wet environments. A typical IPMC consists of a thin sheet of polymer
+(often Nafion or Teflon) which is sandwiched between noble
+metal electrodes such as platinum or gold. When fabricated, the polymer 
+membrane is saturated with certain solvent and ions such as water and $H^+$.
+When a voltage is applied to the electrodes, the counter ions start
+migrating due to the imposed electric field. By dragging along the solvent,
+the osmotic pressure difference near the electrodes
+results in bending of the material (see Fig.~\ref{fig:conceptual}).
+\begin{figure}[!ht]
+  \begin{centering}
+    \subfloat[~]{\begin{centering}
+      \includegraphics[scale=0.6]{IPMC}
+      \par\end{centering}}~
+    \subfloat[~]{\begin{centering}
+      \includegraphics[scale=0.6]{IPMC_bent}
+      \par\end{centering}}
+  \par\end{centering}
+  \caption{\label{fig:conceptual}Conceptual model of the actuation
+ 	of IPMC. Initial counter ion distribution (a) and
+	the distribution and resulting bending after applying a voltage (b).}
+\vspace{-1cm}
+\end{figure}
+\newpage
+%The derived and implemented model helps to predict the actuation of the
+%material. Furthermore, it is expected that the \emph{hp}-FEM implementation
+%results in a smaller problem size, thus likely allowing faster calculation
+%in both 2D and 3D domains.
+
+In this study we will model IPMC materials via a multiphysics coupled problem 
+consisting of the Poisson and Nernst-Planck equations (abbreviated by PNP in
+the following). These equations are used to model charge transport in materials 
+that includes ionic migration, diffusion, and convection. The charge transport 
+process is a key mechanism for electromechanical transduction 
 \cite{basu1997membrane,shahinpoor2001smartmat,
@@
 pugal2008appliedphysics,pugal2010polymer}.
-As the system of equations is nonlinear and for a domain with two
-electrodes, the charge concentration differences occur in a very narrow
-region near the boundaries, the required computing power for a full
-scale domain is, especially in 3D, rather significant. This
-requires a mesh that is optimal in terms of calculation time and calculation
-error.
+
+The PNP system is highly nonlinear and for a typical domain with two
+electrodes, largest differences in charge concentration occur in a very narrow
+region near the boundary. The computing power required for a full scale problem 
+is significant. This is why we are interested in exploring adaptive algorithms
+-- we hope to obtain meshes that are optimal in terms of calculation time and 
+calculation error.
 
 The Nernst-Planck equation for a mobile species ---
-in this case for counter ions --- and without the convection term is:
+in our case for counter ions --- has the form
 \begin{equation}
-  \frac{\partial C}{\partial t}+\nabla\cdot(-D\nabla C-z\mu FC\nabla\phi)=0,
+  \frac{\partial C}{\partial t}+\nabla\cdot(-D\nabla C-z\mu FC\nabla\phi)=0.
   \label{eq:nernst-planck}
 \end{equation}
-where $C$ is the counter ion concentration, $D$ diffusion, $\mu$ mobility,
-$F$ Faraday constant, $\phi$ voltage, and $z$ charge number. The Poisson
-equation is
+Here $C$ stands for the counter ion concentration, $D$ is diffusion, $\mu$ mobility,
+$F$ Faraday constant, $\phi$ voltage, and $z$ the charge number. We have neglected 
+the velocity of the species as in our case it can be assumed zero. 
+The Poisson equation has the form
 \begin{equation}
-  -\nabla^2\phi=\frac{F\rho}{\varepsilon},
+  -\nabla^2\phi=\frac{F\rho}{\varepsilon}
   \label{eq:poisson}
 \end{equation}
-where $\varepsilon$ is an absolute dielectric permittivity and the
-charge density $\rho$ is expressed
+where $\varepsilon$ is the absolute dielectric permittivity. The
+charge density $\rho$ is defined via
 \begin{equation}
@@
 \end{equation}
-with $C_{0}$ being a constant anion concentration.
+where $C_{0}$ is a constant anion concentration.
 
-Brief overview of the motivation
-of the study and a practical application of the results is given in the following section. 
-Thereafter the weak-form~\cite{Hermes-book} derivation of the PNP system of equations
-and time dependent adaptive \emph{hp}-FEM solutions of the system is presented
-for different refinement modes. 
-Also, advantages of a multi-mesh solution over a single-mesh solution are presented.
+The outline of the paper is as follows: Section \ref{sec:moti} explains why 
+it is extremely difficult to find a good mesh for the PNP problem, and 
+hence why we are interested in exploring adaptive algorithms. The PNP model 
+is presented in Section \ref{sec:model} where also its weak formulation is derived. 
+Numerical results and comparisons are presented in Section \ref{sec:results},
+and conclusion and outlook are drawn in Section \ref{sec:conc}.

### 2010-10-11 motivation.tex
Work on the first two pages.

--- 2010-09-15 motivation.tex
@@
-\section{Motivation}
-\begin{figure}
+\section{Motivation} \label{sec:moti}
+Fig.~\ref{fig:comsol-conc-volt} shows a typical solution for $C$ and $\phi$
+at $t=0.1\ s$ and $t=3.0\ s$ for a simplified one-dimensional problem. The corresponding solution
+constants are summarized below in Table~\ref{Table:used-constants}.\begin{figure}[!ht]
   \begin{centering}
-      \includegraphics[scale=0.4]{comsol_conc_volt}
-  \caption{\label{fig:comsol-conc-volt}Calculated concentration $C$ and voltage $\phi$
+      \includegraphics[]{comsol_conc_volt}
+  \caption{Sample concentration $C$ and voltage $\phi$
            in a 1D domain $\Omega\subset\mathbb{R}$.
@@
            and $V_{\partial \Omega_2}=4\ V$) were
-	applied to the Poisson equation Eq.~\eqref{eq:poisson} and Neumann boundaries
-	to the Nernst-Planck equation Eq.~\eqref{eq:nernst-planck}.}
+	   applied to the Poisson equation \eqref{eq:poisson} and Neumann conditions
+	   to the Nernst-Planck equation \eqref{eq:nernst-planck}.}
+\label{fig:comsol-conc-volt}
   \end{centering}
 \end{figure}
-Fig.~\ref{fig:comsol-conc-volt} shows a solution for $C$ and $\phi$ in
-the time dependent NPN system at $t=0.1\ s$ and $t=3.0\ s$. Solution
-constants are shown in Table~\ref{Table:used-constants}.
-It can be seen that the solution has two notable characteristics. 
-Firstly, $\nabla C$ at $\partial \Omega_2$ is
-moving in time, whereas $\nabla C$ at $\partial \Omega_1$ is very
-sharp. For the large part of the domain $\Omega$ $\nabla C=0$.
-At the same time, $\phi$ is a rather smooth fucntion in $\Omega$.
-This clearly makes the choice of mesh for the time dependent NPN
-system difficult. By creating a too fine mesh, the problem gets
-too big. By choosing a coarser mesh, the calculation error goes up.
-Furthermore, from the shape of the solution in Fig.~\ref{fig:comsol-conc-volt}
-can be seen that the polynomial degree of the elements in the middle
+
+The solution shown in Fig.~\ref{fig:comsol-conc-volt} has 
+two notable characteristics: For the most part of the domain $\Omega$,
+the gradient $\nabla C = 0$. Close to $\partial \Omega_2$, $\nabla C$ is
+nonzero and moving in time, and $\nabla C$ is very large at $\partial \Omega_1$.
+At the same time, $\phi$ is a "nice" smooth function for the most part of 
+$\Omega$ but it has a large gradient at $\partial \Omega_2$.
+This makes the choice of an optimal mesh extremely difficult. Even if the 
+solution was stationary, an optimal mesh for $C$ could never be 
+optimal for $\phi$ and vice versa.
+
+Furthermore, the shape of the solution in Fig.~\ref{fig:comsol-conc-volt}
+suggests that the polynomial degree of finite elements in the middle
 of the domain $\Omega$ and near the boundaries $\partial \Omega_1,\ \partial \Omega_2$
-should be different --- namely higher degree near the boundaries. 
-Overall shape of the solutions suggest that
-using different meshes for variables $C$ and $\phi$ can be beneficial
-in terms of resources and calculation time.
+should be different --- large high-degree elements should be used in the middle of the 
+domain while small low-degree ones should be used in the boundary layers.  
+The qualitative differences in the solution components $C$ and $\phi$ 
+also suggest that using different meshes would be beneficial.
 
-All the aforementioned difficulties can be solved by using
-a time dependent adaptive multimesh \emph{hp}-FEM solver.
-Automatic time dependent adaptivity in conjuction with \emph{hp}-FEM 
-helps to limit the error of the calculations by choosing
-a suitable mesh and polynomial degrees of the elements at each time step.
-In this work Hermes2D~\cite{Hermes-project} was used to study
-the problem size, error convergence and solution time of NPN system 
-with different adaptivity algorithms.
+% THIS DOES NOT BELONG HERE
+%All the aforementioned concerns can be solved by using
+%a time dependent adaptive multimesh \emph{hp}-FEM solver.
+%Automatic time dependent adaptivity in conjuction with \emph{hp}-FEM 
+%helps to limit the error of the calculations by automatically choosing
+%a suitable mesh and polynomial degrees of the elements at each time step.
+%In this work Hermes~\cite{Hermes-project} was used to implement
+%the PNP system and study
+%the problem size, error convergence and solution time 
+%with different refinement modes.
 
@@
 \end{table}
-
-\subsection{Practical application}
-IPMCs have been studied in past two decades in view of using them
-as noiseless mechanoelectrical or electromechanical transducers.
-The advantages of the IPMCs over other electroactive polymer actuators
-are low voltage bending, high strains ($>1\%$), and ability to work
-in wet environments. A typical IPMC consists of a thin sheet of polymer
-(often Nafion or Teflon) which is sandwiched between noble
-metal electrodes such as platinum or gold. When fabricated, the polymer 
-membrane is saturated with certain solvent and ions, e.g water and $H^+$.
-When a voltage is applied to the eletrodes, the counter ions start
-migrating due to the imposed electric field. By dragging along the solvent,
-the osmotic pressure difference near the electrodes occur which in turn
-results in bending of the material (see Fig.~\ref{fig:conceptual}).
-\begin{figure}
-  \begin{centering}
-    \subfloat[~]{\begin{centering}
-      \includegraphics[scale=0.6]{IPMC}
-      \par\end{centering}}~
-    \subfloat[~]{\begin{centering}
-      \includegraphics[scale=0.6]{IPMC_bent}
-      \par\end{centering}}
-  \par\end{centering}
-  \caption{\label{fig:conceptual}Conceptual model of the actuation
- 	of IPMC. Initial counter ion distribution (a) and
-	the distribution and resulting bending after applying a voltage (b).}
-\end{figure}
-The derived and implemented model helps to predict the actuation of the
-material. Furthermore, it is expected that the \emph{hp}-FEM implementation
-results in a smaller problem size, thus likely allowing faster calculation
-in both 2D and 3D.

### 2010-10-11 pugal-esco2010.tex
Work on the first two pages.

@@
 
-\title{\emph{hp}-Finite Element Model of Poisson and Nernst-Planck\\ System of Equations}
+%\title{\emph{hp}-Finite Element Model of Poisson and Nernst-Planck\\ System of Equations}
+\title{Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM}
 
@@
 \begin{abstract}
- In this paper we present a \emph{hp}-finite element
-model (\emph{hp}-FEM) of Nernst-Planck and Poisson equation system.
-The model is implemented in Hermes which is a
-space- and space-time adaptive \emph{hp}-FEM solver. The time dependent
-adaptivity is used to control the error of the solution. Full mathematical
-derivation of the weak formulation of the system of equations and
-the solution comparison with a nonadaptive conventional FEM is presented.
-Furthermore, we extend the discussion on Hermes3D as a modeling tool that can
-help in studying and improving the IPMC materials.
+In this paper we study a multiphysics coupled problem consisting 
+of the Poisson and Nernst-Planck equations, that is used to 
+model ionic polymer-metal composite (IPMC) materials. 
+The problem is discretized using the finite element method (FEM) and solved using 
+space-time adaptive \emph{hp}-FEM algorithms provided by the Hermes 
+library. Numerical results are presented and discussed, including 
+comparison of various versions of adaptive $hp$-FEM and conventional 
+low-order FEM. In particular, we discuss the performance of a novel
+adaptive multimesh $hp$-FEM algorithm that is part of the Hermes
+library.
 \end{abstract}
@@
 \begin{keyword}
-  \emph{hp}-FEM \sep Nernst-Planck \sep Poisson \sep weak form
+  Ionic polymer-metal composites \sep IPMC \sep Nernst-Planck equation \sep Poisson equation 
+  \sep finite element method \sep space-time adaptive \emph{hp}-FEM 
 \end{keyword}
@@
 \section*{Acknowledgments}
-KJK thanks the financial support from the Office of Naval Research under Award N000140910218.
+The second author was partially supported by the Grant Agency of the Academy of 
+Sciences of the Czech Republic under Grant No. IAA100760702, and by the U.S.
+Department of Energy Research Subcontract No. 00089911. 
+The third author acknowledges the financial support of the U.S. Office of Naval Research 
+under Award N000140910218.
 

### 2010-10-17 intro.tex
Editing sections 1 - 4.

@@
 
-The outline of the paper is as follows: Section \ref{sec:moti} explains why 
-it is extremely difficult to find a good mesh for the PNP problem, and 
-hence why we are interested in exploring adaptive algorithms. The PNP model 
-is presented in Section \ref{sec:model} where also its weak formulation is derived. 
+The outline of the paper is as follows: Section \ref{sec:moti} shows that 
+the solution components $C$ and $\phi$ have very different behavior, which
+is the reason why it is difficult to find a common mesh that would be optimal 
+for each of them. This explains why we are interested in applying the novel
+multimesh $hp$-FEM method [ADD COUPLE OF REFERENCES TO SOLIN-MULTIMESH].
+The PNP model is presented in Section \ref{sec:model} where also its weak 
+formulation for the Newton's method is derived. Section \ref{sec:hermes}
+describes briefly the open source adaptive $hp$-FEM library Hermes
+that is used to solve the problem numerically. 
 Numerical results and comparisons are presented in Section \ref{sec:results},

### 2010-10-17 model.tex
Work on the first two pages.
Editing sections 1 - 4.

--- 2010-10-07 model.tex
@@
-\section{Model}
-\begin{figure}
+\section{Model}\label{sec:model}
+
+We consider a rectangular 2D domain $\Omega\subset\mathbb{R}^2$ with boundaries 
+$\partial\Omega_{1\ldots 4}\subset\partial\Omega$, shown in Fig.~\ref{fig:domain}.
+
+\begin{figure}[!ht]
   \begin{centering}
@@
 
-The model for solving NPN system is implemented in Hermes.
-A rectangular 2D domain $\Omega\subset\mathbb{R}^2$ with boundaries 
-$\partial\Omega_{1\ldots 4}\subset\partial\Omega$  is considered (see Fig.~\ref{fig:domain}). 
-As there is now flow considered in or out of the domain and there is no
-constant concentration at the boundaries, zero Neumann boundary conditions are used 
-for Eq.~\eqref{eq:nernst-planck}:
+As there is no flow through the domain's boundary, Eq.~\eqref{eq:nernst-planck}
+is equipped with a Neumann boundary condition 
 \begin{equation}
@@
 \end{equation}
-As a positive voltage $V_{pos}$ is applied on $\Omega_1$ and $V_{neg}=0$ is applied
-on $\Omega_3$, Dirichlet boundary conditions are used for Eq.~\eqref{eq:poisson} for
-boundaries $\Omega_1$ and $\Omega_3$:
+Furthermore, we prescribe a positive constant voltage $V_{pos}$ 
+on $\Omega_1$ and zero voltage on $\Omega_3$:
 \begin{eqnarray}
   \phi_{\partial\Omega_1}&=&V_{pos},\\
-  \phi_{\partial\Omega_3}&=&0,
+  \phi_{\partial\Omega_3}&=&0.
   \label{eq:dirichlet}
 \end{eqnarray}
-and Neumann boundaries for $\Omega_2$ and $\Omega_4$:
+On the rest of the boundary, $\phi$ has zero normal derivatives, and thus we prescribe 
+a Neumann boundary condition
 \begin{equation}
@@
 
-To make the derivation of the weak forms more convenient, the following
-helper constants will be used: 
+% IF YOU WANT TO CITE THIS WORK< YOU HAVE TO SAY WHY WE ARE DOING 
+% THE DERIVATION AGAIN -- OTHERWISE IT IS CONTRAPRODUCTIVE. SO 
+% I COMMENTED THIS OUT.
+%An implicit version of the weak form of PNP was derived in~\cite{pugal2010spie}.
+To make our results easily reproducible, we present a rather detailed
+derivation of weak forms of Eqs.~\eqref{eq:nernst-planck} and 
+\eqref{eq:poisson}, as well as formulas for the Jacobian matrix and residual 
+vector that are used in actual computations.
+To facilitate the derivation, we introduce two additional constants 
 \begin{eqnarray}
@@
 \end{eqnarray}
-So Eq.~\eqref{eq:nernst-planck} and Eq.~\eqref{eq:poisson} become after 
-substituting Eq.~\eqref{eq:rho} and the constants $K$ and $L$:
+After using Eq.~\eqref{eq:rho} and the constants $K$ and $L$, 
+Eq.~\eqref{eq:nernst-planck} and Eq.~\eqref{eq:poisson} become
 \begin{eqnarray}
@@
 \end{eqnarray}
-The boundary condition Eq.~\eqref{eq:nernst-planck-boundary} becomes:
+The boundary condition Eq.~\eqref{eq:nernst-planck-boundary} now has the form
 \begin{equation}
@@
 \end{equation}
-The space for solution is $V=H^1\left(\Omega\right)$ where 
+As the second derivatives of both $C$ and $\phi$ are present in the 
+equations, the appropriate function space for them is the Sobolev space 
+$V=H^1\left(\Omega\right)$, where 
 $H^1\left(\Omega\right)=\left\{v\in L^2\left(\Omega\right);\ \nabla v \in \left[L^2\left(\Omega\right)\right]^2\right\}$.
-Let's choose a test function $v^C\in V$.
-The weak form the Nernst-Planck equation Eq.~\eqref{eq:nernst-planck-2}
-is found by multiplying it with the test function $v^C$ and then integrating over the domain~$\Omega$:
+
+In order to derive the weak form of the Nernst-Planck equation Eq.~\eqref{eq:nernst-planck-2},
+we first multiply it with a test function $v^C \in V$ and integrate over the domain~$\Omega$,
 \begin{equation}
@@
 \end{equation}
-After adding the weak form of the boundary term 
-(Eq.~\eqref{eq:nernst-planck-boundary-2}) and applying
-the Green's first identity to the terms that contain Laplacian $\nabla^2$ we get
+Applying the Green's first identity to the terms that contain second derivatives,
+we obtain
 \begin{eqnarray}
@@
 \end{eqnarray}
-After expanding the nonlinear term and given that the boundary terms
-do not contribute, the weak form becomes
+Expanding the nonlinear term and using the boundary condition 
+\eqref{eq:nernst-planck-boundary-2}, we have
 \begin{equation}
@@
 \end{equation}
-As the second and third term cancel out, the final weak from of 
-the Nernst-Planck equation is
+After the second and third terms cancel out, we obtain the final weak form of 
+the Nernst-Planck equation
 \begin{equation}
@@
 \end{equation}
-Similarly the weak form of Poisson equation Eq.~\ref{eq:poisson-2}
-with a test function $v^\phi\subset V$ is:
+Analogously we derive also the weak form of the Poisson equation (\ref{eq:poisson-2}),
 \begin{equation}
@@
 \end{equation}
-After expanding the $\nabla^2$ terms, the final form becomes
+Performing integration by parts and taking into account the boundary 
+conditions for $\phi$, we obtain
 \begin{equation}
@@
 
-\subsection{Implementation in Hermes}
-To implement the system of equations Eq.~\eqref{eq:nernst-planck-weak-final}
-and Eq.~\eqref{eq:poisson-weak-final}, the residuals and the Jacobian
-matrix must be derived. For that, Crank-Nicolson time stepping was
-used
+\subsection{Jacobian matrix and residual vector for the Newton's method}
+To employ the Newton's method for the nonlinear system \eqref{eq:nernst-planck-weak-final},
+\eqref{eq:poisson-weak-final}, formulas for the Jacobian matrix and residual vector need to
+be derived. Time discretization will be performed using the second-order Crank-Nicolson 
+method. The unknown solution components 
+$C^{n+1}$ and $\phi^{n+1}$ at the end of the time step are expressed 
+as linear combinations of finite element basis functions $v_k^{C}$ 
+and $v_k^{\phi}$ with unknown coefficients,
+\begin{eqnarray}
+  C^{n+1} = C(Y^{n+1}) &=& \sum_{k=1}^{N^C} y_k^{C} v_k^{C}, \label{eq:cnotation}\\
+  \phi^{n+1} = \phi(Y^{n+1}) &=& \sum_{k=1}^{N^{\phi}} y_k^{\phi} v_k^{\phi}\label{eq:phinotation}.
+\end{eqnarray}
+Here $Y^{n+1}$ is a coefficient vector of length $N^C + N^{\phi}$ comprising the unknown 
+solution coefficients $y_k^{C}$ and $y_k^{\phi}$ (in this order). We will also be 
+using $C^n = C(Y^n)$ and $\phi^n = \phi(Y^n)$ for the previous time step solutions.
+
+With the notation~\eqref{eq:cnotation}, \eqref{eq:phinotation}, the time discretized 
+Eq.~\eqref{eq:nernst-planck-weak-final} leads to the formula for the 
+first part $F^C$ of the residual vector $F$,
+\begin{eqnarray}
+  F_i^C\left(Y\right) & = & \int_{\Omega} \frac{C(Y)}{\tau}v_i^C d\mathbf{x} - 
+  \int_{\Omega} \frac{C^{n}}{\tau}v_i^C d\mathbf{x}\nonumber\\
+  &&+\frac 12 \left[D\int_{\Omega} \nabla C(Y) \cdot \nabla v_i^C d\mathbf{x}+ 
+  	D\int_{\Omega} \nabla C^{n} \cdot \nabla v_i^C d\mathbf{x}\right]\nonumber\\
+  &&+ \frac 12 \left[K\int_{\Omega}C(Y) \left(\nabla \phi(Y) \cdot \nabla v_i^C\right) d\mathbf{x}+
+  K\int_{\Omega}C^{n} \left(\nabla \phi^{n} \cdot \nabla v_i^C\right) d\mathbf{x}\right]\label{eq:Fc}
+\end{eqnarray}
+where $i = 1, 2, \ldots, N^C$.
+Analogously, Eq.~\eqref{eq:poisson-weak-final} defines the second part $F^{\phi}$ 
+of the residual vector $F$,
 \begin{equation}
-  \frac{\partial C}{\partial t} \approx \frac{C^{n+1} - C^n}{\tau},
-  \label{eq:cranic}
-\end{equation}
-where $\tau$ is a time step. For the variables $C^{n+1}$ and $\phi^{n+1}$ the
-following notation will be used:
-\begin{eqnarray}
-  C^{n+1} &=& \sum_{k=1}^{N^C} y_k^{C} v_k^{C}, \label{eq:cnotation}j\\
-  \phi^{n+1} &=& \sum_{k=1}^{N^{\phi}} y_k^{\phi} v_k^{\phi}\label{eq:phinotation},
-\end{eqnarray}
-where $v_k^C$ and $v_k^\phi$ are piecewise polynomial functions in $V$.
-Considering the Crank-Nicolson time stepping and the notation~\eqref{eq:cnotation},
-the time discretized Eq.~\eqref{eq:nernst-planck-weak-final} becomes
-\begin{eqnarray}
-  F_i^C\left(Y\right) & = & \int_{\Omega} \frac{C^{n+1}}{\tau}v_i^C d\mathbf{x} - 
-  \int_{\Omega} \frac{C^{n}}{\tau}v_i^C d\mathbf{x}\nonumber\\
-  &&+\frac 12 \left[D\int_{\Omega} \nabla C^{n+1} \cdot \nabla v_i^C d\mathbf{x}+ 
-  	D\int_{\Omega} \nabla C^{n} \cdot \nabla v_i^C d\mathbf{x}\right]\nonumber\\
-  &&+ \frac 12 \left[K\int_{\Omega}C^{n+1} \left(\nabla \phi^{n+1} \cdot \nabla v_i^C\right) d\mathbf{x}+
-  K\int_{\Omega}C^{n} \left(\nabla \phi^{n} \cdot \nabla v_i^C\right) d\mathbf{x}\right]\label{eq:Fc},
-\end{eqnarray}
-and in the notation~\eqref{eq:phinotation}, Eq.~\eqref{eq:poisson-weak-final} becomes
-\begin{equation}
-  F_i^{\phi}\left(Y\right) = \int_{\Omega} \nabla \phi^{n+1} \cdot \nabla v_i^{\phi} d\mathbf{x} 
-  - \int_{\Omega} LC^{n+1}v_i^{\phi} d\mathbf{x} + \int_{\Omega} LC_0 v_i^{\phi} d\mathbf{x}.
+  F_i^{\phi}\left(Y\right) = \int_{\Omega} \nabla \phi(Y) \cdot \nabla v_i^{\phi} d\mathbf{x} 
+  - \int_{\Omega} LC(Y)v_i^{\phi} d\mathbf{x} + \int_{\Omega} LC_0 v_i^{\phi} d\mathbf{x}
   \label{eq:Fphi}
 \end{equation}
-For the implementation the $2\times 2$ Jacobian matrix $DF/DY$ with elements corresponding to
+where $i = N^C + 1, N^C + 2, \ldots, N^C + N^{\phi}$. The nonlinear discrete problem 
+that needs to be solved at the end of each time step thus has the form 
+$F(Y) = 0$.
+
+The Jacobian matrix $J(Y) = DF/DY$ has a $2\times 2$ block structure,
 \begin{equation}
-  \frac{\partial F_i^C}{\partial y_j^C}, \ \frac{\partial F_i^C}{\partial y_j^{\phi}},\  
-  \frac{\partial F_i^{\phi}}{\partial y_j^C}, \ \frac{\partial F_i^{\phi}}{\partial y_j^{\phi}},
+J(Y) = \left(
+\begin{array}{cc}
+  \displaystyle \frac{\partial F_i^C}{\partial y_j^C} & \displaystyle \frac{\partial F_i^C}{\partial y_j^{\phi}} \\ 
+  \displaystyle \frac{\partial F_i^{\phi}}{\partial y_j^C} & \displaystyle \frac{\partial F_i^{\phi}}{\partial y_j^{\phi}}
+\end{array}
+\right),
 \end{equation}
-must be derived: 
+and its entries are obtained by calculating the partial derivatives of $F$ with
+respect to the components of the coefficient vector $Y$. For this it is useful to 
+realize that 
+$$
+\frac{\partial C(Y)}{\partial y_j^C} = v_j^C, \ \ \ 
+\frac{\partial \nabla C(Y)}{\partial y_j^C} = \nabla v_j^C,\ \ \ \mbox{etc.}.
+$$
+We obtain
 \begin{eqnarray}
-  \frac{\partial F_i^C}{\partial y_j^C} &=& 
+  \frac{\partial F_i^C}{\partial y_j^C}(Y) &=& 
   \int_{\Omega} \frac{1}{\tau} v_j^C v_i^C d\mathbf{x} + 
   \frac 12 D\int_{\Omega} \nabla v_j^C \cdot \nabla v_i^C d\mathbf{x}
-  + \frac 12 K\int_{\Omega} v_j^C \left(\nabla \phi^{n+1} \cdot \nabla v_i^C\right) d\mathbf{x},\label{eq:dFcdyc}\\
-  \frac{\partial F_i^C}{\partial y_j^{\phi}} &=&
-  \frac 12 K \int_{\Omega} C^{n+1} \left(\nabla v_j^{\phi} \cdot \nabla v_i^C\right) d\mathbf{x},\\
-  \frac{\partial F_i^{\phi}}{\partial y_j^C} &=&
+  + \frac 12 K\int_{\Omega} v_j^C \left(\nabla \phi(Y) \cdot \nabla v_i^C\right) d\mathbf{x},\label{eq:dFcdyc}\\
+  \frac{\partial F_i^C}{\partial y_j^{\phi}}(Y) &=&
+  \frac 12 K \int_{\Omega} C(Y) \left(\nabla v_j^{\phi} \cdot \nabla v_i^C\right) d\mathbf{x},\\
+  \frac{\partial F_i^{\phi}}{\partial y_j^C}(Y) &=&
   - \int_{\Omega} L v_j^C v_i^{\phi} d\mathbf{x},\\
-  \frac{\partial F_i^{\phi}}{\partial y_j^{\phi}} &=&
+  \frac{\partial F_i^{\phi}}{\partial y_j^{\phi}}(Y) &=&
   \int_{\Omega} \nabla v_j^{\phi} \cdot \nabla v_i^{\phi} d\mathbf{x}\label{eq:dFphidyphi}.
 \end{eqnarray}
-In Hermes Eq.~\eqref{eq:Fc} and \eqref{eq:Fphi} define the residuum $F$ and
-Eq.~\eqref{eq:dFcdyc}---\eqref{eq:dFphidyphi} define the Jacobian matrix $J$.
 
-\subsection{Adaptive multi-mesh solution}
+\subsection{Newton's iteration}
+At the beginning of the $(n+1)$st time step we 
+set $Y^{n+1}_0 = Y^n$, where $Y^n$ is the coefficient vector  
+that was calculated in the $n$th time step (or coming from the 
+initial condition if $n = 0$). We set $k = 0$ and run the 
+Newton's iteration 
+\begin{eqnarray*}
+J(Y^{n+1}_k) \delta Y^{n+1}_{k+1} &=& -F(Y^{n+1}_k), \\ 
+Y^{n+1}_{k+1} &=& Y^{n+1}_k + \delta Y^{n+1}_{k+1}, \\
+k &:=& k+1
+\end{eqnarray*}
+over $k$ until it converges. Then we set $Y^{n+1} := Y^{n+1}_{k+1}$. 
+We use a combined stopping criterion 
+that makes sure that both the norm of the residual vector $\Vert F(Y^{n+1})\Vert$ 
+as well as the norm of the increment $\Vert \delta Y^{n+1}\Vert$ are sufficiently 
+small.
 
-The defined Jacobian $J$ and residuum $F$ can be simply solved with Hermes by
-using Newton's iteration. However, we were more interested in the automatic
-adaptivity to control the error and problem size.
+\section{Adaptive $hp$-FEM and the Open-Source Library Hermes}
+\label{sec:hermes}
 
@@
 (such as piecewise linear approximations). These heuristic techniques 
-are not employed in Hermes since they may fail 
-in non-standard situations, and because they lack a 
+may fail in more complicated situations, and moreover they lack a 
 transparent relation to the true approximation error.
-In order to obtain fast, usable adaptivity, one has to resort to adaptive \emph{hp}-FEM.
+
+In order to obtain fast, usable adaptivity, one has to resort to higher-order finite 
+elements and adaptive \emph{hp}-FEM.
 Automatic adaptivity in the \emph{hp}-FEM is substantially different from adaptivity 
 in low-order FEM, since every element can be refined in many different ways. 
-Fig.~\ref{fig:refinements} shows several illustrative refinement candidates for a fourth-order element.
-\begin{figure}
+For illustration, Fig.~\ref{fig:refinements} shows several illustrative 
+refinement candidates for a fourth-order element.
+\begin{figure}[!ht]
   \begin{centering}
   \includegraphics[width=0.5\columnwidth]{refinements}
-  \caption{\label{fig:refinements} Refinement candidates for a fourth-order
+  \caption{\label{fig:refinements} Many possible refinement candidates for a fourth-order
   element.}
   \end{centering}
+\vspace{-0.5cm}
 \end{figure}
-The number of possible element refinements is implementation-dependent. 
+
+\newpage
+The number of possible element refinements is implementation dependent. 
 In general it is very low in \emph{h} or \emph{p} adaptivity, 
-but much higher in \emph{hp}-adaptivity, and it rises even more when 
-anisotropic refinements are enabled.
-Hermes supports 8 different refinement modes, namely,
-3 isotropic and 5 anisotropic refinements. The isotropic refinements are
+and higher in \emph{hp}-adaptivity. It rises very fast when 
+anisotropic refinements are considered.
+
+\subsection{The Hermes Library}
+
+Hermes\footnote{http://hpfem.org/hermes} is a free and open-source C++ library 
+that implements higher-order finite elements approximations and adaptive $hp$-FEM.
+It supports 8 different adaptivity modes -- three isotropic and five anisotropic. 
+The isotropic refinements are
 \emph{h}-isotropic (H\_ISO), \emph{p}-isotropic (P\_ISO), \emph{hp}-isotropic (HP\_ISO).
@@
 \emph{hp}-anisotropic-p (HP\_ANISO\_P), and \emph{hp}-anisotropic (HP\_ANISO).
-Once the refinement mode is selected (by user), Hermes selects a particular
-refinement scheme from several candidates based on the score. More information
-can be found in~\cite{Hermes-project}.
+The eight adaptivity modes are summarized in Fig. \ref{fig:candlist}.
 
-In case of the single mesh, the same basis function base was used, i.e.
-$v_i^\phi=v_i^C$. For multi mesh, the meshes and therefore the basis functions
-were different. Regardless of the meshing, automatic adaptivity was applied
-during each time step, till the error converged to the acceptable level.
-In analogy to the most successful adaptive ODE solvers, Hermes uses a pair of 
-approximations with different orders of accuracy to obtain this information: 
-coarse mesh solution and fine mesh solution. The initial coarse mesh is read 
-from the mesh file, and the initial fine mesh is created through its 
-global refinement both in $h$ and $p$. For more
-information, see~\cite{Hermes-project}. In the calculations, the coarse
-mesh solution was not calculated at each time step, but the fine mesh
-solution was projected to the coarse mesh by using orthogonal projection. This
-yielded better convergence and also faster calculation.
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=0.7\columnwidth]{cand_list_quads}
+  \caption{\label{fig:candlist} Refinement candidates for every
+  refinement mode for quad type elements.}
+  \end{centering}
+\end{figure}
+Note that triangular elements do not support anisotropic refinements.
+Due to the large number of refinement options, classical error estimators 
+that provide a constant error estimate per element, cannot be used to 
+guide automatic \emph{hp}-adaptivity. 
+For this, one needs to know the shape of the approximation error.
+Hermes uses a pair of approximations with different orders of accuracy 
+to obtain this information: coarse mesh solution and fine mesh solution. 
+The initial coarse mesh is read from the mesh file, and the initial 
+fine mesh is created through its global refinement both in \emph{h}
+and \emph{p}. The fine mesh solution is the approximation of 
+interest both during the adaptive process and at the end of computation. 
+Global orthogonal projection of the fine mesh solution on the coarse mesh 
+is used to extract the low-order part from the reference solution.
+The adaptivity algorithm is guided by the difference between the 
+reference solution and its low-order part [ADD CITATION SOLIN-SIMKO].
+Note that this approach to automatic adaptivity is PDE-independent
+and thus naturally applicable to a large variety of multiphysics 
+coupled problems.
+
+\subsection{Multimesh $hp$-FEM}
+In multiphysics PDE systems such as Poisson-Nernst-Planck it can 
+happen that one physical field is very smooth where others are not,
+as we illustrated in Fig.~\ref{fig:comsol-conc-volt}. 
+If all the fields are approximated on the same mesh, then 
+unnecessary refinements will be present in smooth areas
+where they are not necessary. This can be very wasteful.
+
+Hermes implements a novel adaptive multimesh $hp$-FEM [ADD REFERENCES]
+that makes it possible to approximate different fields on individual meshes,
+without breaking the monolithic structure of the coupling mechanism.
+For practical reasons, the meshes in the system are not allowed to be 
+completely independent -- they have a common coarse mesh that we call {\em 
+master mesh}. The master mesh is 
+there for algorithmic purposes only and it may not even be used for 
+discretization purposes. Every mesh in the system is obtained from 
+the master mesh via an arbitrary sequence of elementary refinements. 
+Assembling is done on a {\em union mesh}, a geometrical union of 
+all meshes in the system (imagine printing all meshes on transparencies and 
+positioning them on top of each other).
+
+The union mesh is not constructed physically in the computer 
+memory -- it merely serves as a hint to correctly transform the 
+integration points while integrating over sub-elements of elements 
+in the existing meshes. 
+As a result, the multimesh discretization of the PDE system is 
+monolithic in the sense that no physics is lost --- all integrals 
+in the discrete weak formulations are evaluated exactly up to 
+the error in the numerical quadrature. The exact preservation of 
+the coupling structure of multiphysics coupled problems makes 
+the multimesh $hp$-FEM very different from various interpolation 
+and projection based methods that suffer from errors made
+while transferring data between different meshes in the system.

### 2010-10-17 motivation.tex
Editing sections 1 - 4.

@@
 \section{Motivation} \label{sec:moti}
-Fig.~\ref{fig:comsol-conc-volt} shows a typical solution for $C$ and $\phi$
-at $t=0.1\ s$ and $t=3.0\ s$ for a simplified one-dimensional problem. The corresponding solution
-constants are summarized below in Table~\ref{Table:used-constants}.\begin{figure}[!ht]
-  \begin{centering}
-      \includegraphics[]{comsol_conc_volt}
-  \caption{Sample concentration $C$ and voltage $\phi$
-           in a 1D domain $\Omega\subset\mathbb{R}$.
-           Dirichlet boundary conditions ($V_{\partial \Omega_1}=0\ V$
-           and $V_{\partial \Omega_2}=4\ V$) were
-	   applied to the Poisson equation \eqref{eq:poisson} and Neumann conditions
-	   to the Nernst-Planck equation \eqref{eq:nernst-planck}.}
-\label{fig:comsol-conc-volt}
-  \end{centering}
-\end{figure}
 
-The solution shown in Fig.~\ref{fig:comsol-conc-volt} has 
-two notable characteristics: For the most part of the domain $\Omega$,
-the gradient $\nabla C = 0$. Close to $\partial \Omega_2$, $\nabla C$ is
-nonzero and moving in time, and $\nabla C$ is very large at $\partial \Omega_1$.
-At the same time, $\phi$ is a "nice" smooth function for the most part of 
-$\Omega$ but it has a large gradient at $\partial \Omega_2$.
-This makes the choice of an optimal mesh extremely difficult. Even if the 
-solution was stationary, an optimal mesh for $C$ could never be 
-optimal for $\phi$ and vice versa.
+In this section we use a simplified one-dimensional model to illustrate the 
+principal difficulties encountered in the numerical solution of the 
+PNP system.
+Table~\ref{Table:used-constants} shows constants that we will use in 
+computations in this section as well as in the rest of the paper:
 
-Furthermore, the shape of the solution in Fig.~\ref{fig:comsol-conc-volt}
-suggests that the polynomial degree of finite elements in the middle
-of the domain $\Omega$ and near the boundaries $\partial \Omega_1,\ \partial \Omega_2$
-should be different --- large high-degree elements should be used in the middle of the 
-domain while small low-degree ones should be used in the boundary layers.  
-The qualitative differences in the solution components $C$ and $\phi$ 
-also suggest that using different meshes would be beneficial.
-
-% THIS DOES NOT BELONG HERE
-%All the aforementioned concerns can be solved by using
-%a time dependent adaptive multimesh \emph{hp}-FEM solver.
-%Automatic time dependent adaptivity in conjuction with \emph{hp}-FEM 
-%helps to limit the error of the calculations by automatically choosing
-%a suitable mesh and polynomial degrees of the elements at each time step.
-%In this work Hermes~\cite{Hermes-project} was used to implement
-%the PNP system and study
-%the problem size, error convergence and solution time 
-%with different refinement modes.
-
-\begin{table}
+\begin{table}[!ht]
 \caption{Constants used in the Poisson-Nernst-Planck system of equations.}
@@
 \end{table}
+
+Fig.~\ref{fig:comsol-conc-volt} shows a typical solution for $C$ and $\phi$
+at $t=0.1\ s$ and $t=3.0\ s$. 
+The solution has 
+two notable characteristics: For the most part of the domain $\Omega$,
+the gradient $\nabla C = 0$. Close to $\partial \Omega_2$, $\nabla C$ is
+nonzero and moving in time, and $\nabla C$ is very large at $\partial \Omega_1$.
+At the same time, $\phi$ is a "nice" smooth function for the most part of 
+$\Omega$ but it has a large gradient at $\partial \Omega_2$.
+This makes the choice of an optimal mesh extremely difficult. Even if the 
+solution was stationary, an optimal mesh for $C$ could never be 
+optimal for $\phi$ and vice versa.
+
+\begin{figure}[!ht]
+  \begin{centering}
+      \includegraphics[]{comsol_conc_volt}
+  \caption{Sample concentration $C$ and voltage $\phi$
+           in a 1D domain $\Omega\subset\mathbb{R}$.
+           Dirichlet boundary conditions ($V_{\partial \Omega_1}=0\ V$
+           and $V_{\partial \Omega_2}=4\ V$) were
+	   applied to the Poisson equation \eqref{eq:poisson} and Neumann conditions
+	   to the Nernst-Planck equation \eqref{eq:nernst-planck}.}
+\label{fig:comsol-conc-volt}
+  \end{centering}
+\end{figure}
+
+Furthermore, the shape of the solution in Fig.~\ref{fig:comsol-conc-volt}
+suggests that the polynomial degree of finite elements in the middle
+of the domain $\Omega$ and near the boundaries $\partial \Omega_1,\ \partial \Omega_2$
+should be different --- large high-degree elements should be used in the middle of the 
+domain while small low-degree ones should be used in the boundary layers.  
+The qualitative differences in the solution components $C$ and $\phi$ 
+also suggest that using different meshes would be beneficial.
+
+% THIS DOES NOT BELONG HERE
+%All the aforementioned concerns can be solved by using
+%a time dependent adaptive multimesh \emph{hp}-FEM solver.
+%Automatic time dependent adaptivity in conjuction with \emph{hp}-FEM 
+%helps to limit the error of the calculations by automatically choosing
+%a suitable mesh and polynomial degrees of the elements at each time step.
+%In this work Hermes~\cite{Hermes-project} was used to implement
+%the PNP system and study
+%the problem size, error convergence and solution time 
+%with different refinement modes.

### 2010-10-17 pugal-esco2010.tex
Editing sections 1 - 4.

@@
 low-order FEM. In particular, we discuss the performance of a novel
-adaptive multimesh $hp$-FEM algorithm that is part of the Hermes
-library.
+adaptive multimesh $hp$-FEM algorithm.
 \end{abstract}
@@
   Ionic polymer-metal composites \sep IPMC \sep Nernst-Planck equation \sep Poisson equation 
-  \sep finite element method \sep space-time adaptive \emph{hp}-FEM 
+  \sep finite element method \sep space-time adaptivity, multimesh \emph{hp}-FEM 
 \end{keyword}

### 2010-10-19 model.tex
Pavel's suggestions, improving the results section

@@
 % I COMMENTED THIS OUT.
+% I guess it can be left out as the work in SPIE is quite preliminary
+% and not that complete
 %An implicit version of the weak form of PNP was derived in~\cite{pugal2010spie}.
@@
 \emph{hp}-anisotropic-p (HP\_ANISO\_P), and \emph{hp}-anisotropic (HP\_ANISO).
-The eight adaptivity modes are summarized in Fig. \ref{fig:candlist}.
+The eight adaptivity modes are summarized in Fig.~\ref{fig:candlist}.
 
@@
 The adaptivity algorithm is guided by the difference between the 
-reference solution and its low-order part [ADD CITATION SOLIN-SIMKO].
+reference solution and its low-order part~\cite{solin2010pde}.
 Note that this approach to automatic adaptivity is PDE-independent

### 2010-10-19 results.tex
Work on the first two pages.
Editing sections 1 - 4.
Pavel's suggestions, improving the results section

@@
-\section{Results}
+\section{Numerical Results and Comparisons}\label{sec:results}
 
-\begin{figure}
+\begin{figure}[!ht]
   \begin{centering}
@@
 algorithm find the most optimal mesh. So coarse initial mesh might not be
-suitable for all the practical applications, as will be demonstrated in the
+suitable for most the practical applications, as will be demonstrated in the
 end of this section, however, it provides a good insight into the
@@
 
-\begin{figure}
+\begin{figure}[!ht]
   \begin{centering}
@@
   and voltage $\phi$ at two different time steps
-  (HP\_ANISO adaptivity was used). This is a 2D solution shown
+  (HP\_ANISO refinement mode was used). This is a 2D solution shown
   as in 3D, where the height indicates the values of $C$ and $\phi$.}
@@
 Example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
-with refinement mode HP\_ANISO is shown
+calculated with HP\_ANISO refinement mode is shown
 in Fig.~\ref{fig:cphi}. The time $t=0.7\ s$ was chosen because
-by that time, some ionic migration has already taken place, i.e.
-concentration gradient near the $\partial\Omega_1$ and
-$\partial\Omega_3$ has formed. The automatic mesh refinements
+by that time (with given constants in Table~\ref{Table:used-constants}),
+some ionic migration has already taken place and
+the concentration gradients near the boundaries $\partial\Omega_1$ and
+$\partial\Omega_3$ have formed. The automatic mesh refinements
 at different time steps are clearly visible in the figure --- especially
-near the top boundary, where the concentration gradient is
-moving in time (as was also seen in Fig.~\ref{fig:comsol-conc-volt}).
+near $\partial\Omega_1$, where the $C_{\Omega_1}\approx 0$ and
+the gradient $\nabla C$ is
+moving in time (this was also demonstrated in Fig.~\ref{fig:comsol-conc-volt}).
 
@@
   of single-mesh and multi-mesh solutions with HP\_ISO
-  and HP\_ANISO refinements. (Notice log Y scale)}
+  and HP\_ANISO refinement modes. (Notice log Y scale)}
   \end{centering}
 \end{figure}
-\begin{figure}
+
+\begin{figure}[!ht]
   \begin{centering}
@@
 and Fig.~\ref{fig:singlemulticpu}.
-The result can be understood from Fig.~\ref{fig:comsol-conc-volt} --- in the boundary
-regions $\partial \Omega_1$ and $\partial\Omega_3$ the concentration gradient
-is greater than voltage gradient, namely $\nabla C >> \nabla \phi$. Therefore
-refining the mesh for both variables is not reasonable in terms of
+The result can be understood when considering Fig.~\ref{fig:cphi} --- in the vicinity
+of the boundaries $\partial \Omega_1$ and $\partial\Omega_3$ the concentration gradient
+is greate than voltage gradient, namely $\nabla C >> \nabla \phi$. Therefore,
+adapting the mesh for both variables is not reasonable in terms of
 number of degrees of freedom. For instance,
@@
 HP\_ANISO at $t=0.7\ s$ is shown in Fig.~\ref{fig:cphi}. The corresponding polynomial
-degree space is shown in Fig.~\ref{fig:poly}. Notice that the adaptive algorithm
-has increased the maximum polynomial degree for $C$ space to 7, however,
-at the same time, the maximum polynomial degree for the $\phi$ space is one. Furthermore,
+degree space for multi-mesh configuration is shown in Fig.~\ref{fig:poly}. 
+Notice that the adaptivity algorithm
+of Hermes has increased the maximum polynomial degree for the $C$-space to~7, however,
+the maximum polynomial degree for the $\phi$-space is~2. Furthermore,
 the mesh is significantly more refined for $C$.
-For most cases using the multi-mesh results in similar or better CPU time, i.e.
-multi-mesh takes less computational resources. Only excpetion was HP\_ANISO\_H 
+For most of the cases using the multi-mesh results in similar or better CPU time.
+It means that multi-mesh takes less computational resources. Only excpetion was HP\_ANISO\_H 
 refinement mode for which the single mesh configuration resulted slightly faster
@@
   \caption{\label{fig:isoanisodof} NDOFs in case 
-  of multi-mesh solutions with H\_ISO, H\_ANISO,
-  HP\_ISO, HP\_ANISO, and single-mesh solution with HP\_ANISO\_H
+  of multi-mesh configuration with H\_ISO, H\_ANISO,
+  HP\_ISO, HP\_ANISO, and single-mesh configuration with HP\_ANISO\_H
   refinement modes. (Notice log Y scale)}
@@
 \end{figure}
-\begin{figure}
+
+\begin{figure}[!ht]
   \begin{centering}
@@
   \caption{\label{fig:isoanisocpu} CPU times in case 
-  of multi-mesh solutions with H\_ISO, H\_ANISO,
-  HP\_ISO, HP\_ANISO, and single-mesh solution with HP\_ANISO\_H
+  of multi-mesh configuration with H\_ISO, H\_ANISO,
+  HP\_ISO, HP\_ANISO, and single-mesh configuration with HP\_ANISO\_H
   refinement modes. (notice log Y scale)}
@@
   \caption{\label{fig:isoanisopdof} NDOFs in case 
-  of multi-mesh solutions with P\_ISO, P\_ANISO, and
+  of multi-mesh configuration with P\_ISO, P\_ANISO, and
   HP\_ANISO\_P refinement modes.}
@@
   \caption{\label{fig:isoanisopcpu} CPU times in case 
-  of multi-mesh solutions with P\_ISO, P\_ANISO, and
+  of multi-mesh configuration with P\_ISO, P\_ANISO, and
   HP\_ANISO\_P refinement modes.}
@@
 isotropic and anisotropic adaptivities were compared. The \emph{p}-adaptivity
-modes were compared separately as they used more refined mesh (Fig.~\ref{fig:mesh}~(c)).
-Fig.~\ref{fig:isoanisodof} and Fig.~\ref{fig:isoanisocpu} show the comparison
+modes were compared separately as they used more refined initial mesh 
+(shown in Fig.~\ref{fig:mesh}~(c)).
+Fig.~\ref{fig:isoanisodof} and Fig.~\ref{fig:isoanisocpu} provide the comparison
 of H\_ISO, H\_ANISO, HP\_ISO, HP\_ANISO, and HP\_ANISO\_H modes in terms of CPU time
-and problem size.
+and NDOFs.
 Fig.~\ref{fig:isoanisopdof} and Fig.~\ref{fig:isoanisopcpu} show the similar
 comparsion for the P\_ISO, P\_ANISO, and HP\_ANISO\_P modes.
-It can be clearly seen that the anisotropic refinement modes result in a reasonable problem
+It is not difficult to see that the anisotropic refinement modes result in a reasonable problem
 size and the problems solve within a reasonable calculation time. It is interesting
@@
 \emph{p}-adaptivity group, HP\_ANISO\_P results in the smallest problem size
-at each time step, whereas P\_ISO and P\_ANISO have a very largy problem size
+at each time step, whereas P\_ISO and P\_ANISO result in a very large problem size
 during the first time steps of the solution.
@@
 means that the number of degrees of freedom in time converges
-to so that $N_{dof}<500$, and the term ``reasonable calculation time''
+to so that $N_{DOF}<500$, and the term ``reasonable calculation time''
 means that the calculation (step $\tau=0.01\ s$, physical
@@
 Although these parameters are empirical, they serve as an upper limit, given
-that the most refinement modes give significantly smaller results:
-$t<<500\ s$ and $N_{dof} << 500$.
+that the most refinement modes give significantly better results, i.e.
+$t<<500\ s$ and $N_{DOF} << 500$.
 
@@
 from \emph{p}-adaptivity group will be compared
-in terms of problem size and cumulative CPU time. 
+in terms of NDOFs and cumulative CPU time. 
 In all of the cases, the relative 
 error at each time step remained below
-the threshold which were set to $e_{th}=0.5\%$ between the coarse mesh
+the threshold which was set to $e_{th}=0.5\%$ between the coarse mesh
 and fine mesh solutions, therefore the error-time plot will not be considered.
 
-\begin{figure}
+\begin{figure}[!ht]
   \begin{centering}
@@
 Fig.~\ref{fig:cpu} shows the cumulative CPU time for different refinement 
-modes at each time step. All the calculations were done on the same computer.
-Here we see that HP\_ANISO\_H and HP\_ANISO require the most
-resources which can be understood from the fact that these 
-refinement modes have the largest number of 
-candidates (see Section.~\ref{sec:model}) from which the refinement method is chosen.
-At the same time, HP\_ANISO\_P is the fastest among all the other refinement modes.
+modes at each time step --- the results were recorded on the same computer
+for the CPU times to be comparable.
+We see that HP\_ANISO\_H and HP\_ANISO require the most
+resources. This can be understood from the fact that in case of these 
+refinement modes the adaptivity algorithm has the largest number of 
+candidates (see Section.~\ref{sec:model} and Fig.~\ref{fig:refinements})
+from which a particular refinement can be chosen.
+At the same time, HP\_ANISO\_P is the fastest compared to the other refinement modes.
+This can be attributed to the finer inital mesh.
+
 Fig.~\ref{fig:dof} shows the NDOFs at each time step.
 It can be seen that the HP\_ANISO results in the 
-smallest problem size --- $N_{dof} \approx 125$. 
+smallest problem size --- $N_{DOF} \approx 125$. 
 All the other refinement modes result in a 
-problem size of approximately ($N_{dof} \approx 250$). So we have
-two notable refinement modes --- HP\_ANISO\_P because of the fast
-solution, and HP\_ANISO because of the small problem size. In the following
-subsection, optimization of those two modes will be considered.
+problem size of approximately ($N_{DOF} \approx 250$). Therefore
+the HP\_ANISO is the most efficient in terms of memory consumption.
+
+As we have filtered out
+two notable refinement modes for the given problem --- HP\_ANISO\_P because of the fast
+calculation, and HP\_ANISO because of the small problem size. In the following
+subsection, some optimizations to reduce the CPU time of
+HP\_ANISO and reduce the NDOFs of HP\_ANISO\_P will be considered.
 
@@
 
-So far we have seen that HP\_ANISO results in the smallest problem size, but requires
-quite a lot CPU time compared to HP\_ANISO\_P that is the fastest.
-When it comes to a large domain or 3D modeling the problem
-size becomes the most important factor. Therefore, we consider HP\_ANISO the most
-suitable refinement mode to the given problem. Thus some ways to optimize the time
-factor will be considered. The desirable output would be HP\_ANISO problem size
+When it comes to a large domain or 3D modeling, the problem
+size becomes a very important factor. Namely, 3D full scale solutions tend to use
+a lot of memory. Therefore, we consider HP\_ANISO the most
+suitable refinement mode for the given problem. 
+Hence, some ways to optimize the model based on HP\_ANISO
+mode to improve the CPU time
+%TODO, continue here
+factor without significantly compromising the NDOFs will be considered. 
+The desirable output would be HP\_ANISO problem size
 close to HP\_ANISO\_P CPU time. One way to optimize the problem
-is to choose somewhat more refined initial mesh. Other way one could think
-to optimize the problem would be to change
-the refinement frequency during the solving process. Recall that up to this point,
-the initial mesh has been loaded in the beginning of each time step. True,
-by employing the optimizations, we already must know something about the problem
+is to choose more refined initial mesh. Another way would be to change
+the refinement frequency during the solving process. In theory, this
+could result in a fewer adaptivity steps which are quite expensive in terms
+of CPU time. Recall that up to this point,
+the initial mesh has been loaded in the beginning of each time step. 
+True, by employing these optimizations, we must know something about the problem
 and its solution beforehand. However, it could still be practial when solving a real problem
@@
 \subsection{More general results}
-\begin{figure}
+\begin{figure}[!ht]
   \begin{centering}
@@
 results in 2D problem, refined initial mesh was more efficient to use.
-
-\emph{
-PAVEL: Should I try to include the similar solution from comsol and do
-some comparison here? I got this idea just before commiting the final
-draft to you?}

### 2010-10-19 conclusions.tex
Work on the first two pages.
Results and conclusions improved

@@
-\section{Conclusions}
+\section{Conclusion and Outlook}\label{sec:conc}
 
@@
 very different field gradients in the space and time.
-Conventional finite element solvers do not provide the means 
+Conventional finite element solvers do not necessarily provide the means 
 how to deal with such problems such that both the error of
 the solution and problem size remain small throughout the
-time dependent solving process.
+time dependent solving process. This is largely due to the
+fact that it is very difficult to find an optimal initial mesh.
 
@@
 size remains acceptably small throughout the solving process.
-Namely, hermes refinement modes HP\_ANISO and HP\_ANISO\_P
+Namely, Hermes refinement modes HP\_ANISO and HP\_ANISO\_P
 resulted the smallest and fastest problem, respectively.
@@
 is yet to be demonstrated, that this becomes especially
-important when dealing with 3D problems with a large physical
-domain.
+important when dealing with 3D problems in a large physical
+domain with non-uniform boundary conditions.

### 2010-10-19 model.tex
Results and conclusions improved

@@
 
-Hermes implements a novel adaptive multimesh $hp$-FEM [ADD REFERENCES]
+Hermes implements a novel adaptive multimesh $hp$-FEM~\cite{solin2010monolithic,
+solin2010adaptive,dubcova2010space}
 that makes it possible to approximate different fields on individual meshes,

### 2010-10-19 results.tex
Results and conclusions improved

@@
   \caption{\label{fig:mesh} Initial coarse mesh (a),
-  	half refined mesh (b) and refined mesh (c). The coarse mesh
-	and refined mesh were used in the initial calculations, the latter one
+  	half refined mesh (b) and refined mesh (c). The coarse mesh (a)
+	and refined mesh (c) were used in the initial calculations, the latter one
 	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
@@
 was used (see Fig.~\ref{fig:mesh}~(a)) to let the adaptivity
-algorithm find the most optimal mesh. So coarse initial mesh might not be
-suitable for most the practical applications, as will be demonstrated in the
+algorithm find the most optimal mesh. That coarse initial mesh might not be
+suitable for practical applications, as will be demonstrated in the
 end of this section, however, it provides a good insight into the
@@
   (HP\_ANISO refinement mode was used). This is a 2D solution shown
-  as in 3D, where the height indicates the values of $C$ and $\phi$.}
+  in 3D, where the height indicates the values of $C$ and $\phi$.}
   \end{centering}
@@
 the gradient $\nabla C$ is
-moving in time (this was also demonstrated in Fig.~\ref{fig:comsol-conc-volt}).
+shifting in time (this is also demonstrated in Fig.~\ref{fig:comsol-conc-volt}).
 
@@
   \caption{\label{fig:singlemultidof} NDOFs in case 
-  of single-mesh and multi-mesh solutions with HP\_ISO
+  of single-mesh and multi-mesh configurations with HP\_ISO
   and HP\_ANISO refinement modes. (Notice log Y scale)}
@@
   \includegraphics[width=\columnwidth]{singlemulti_cpu}
-  \caption{\label{fig:singlemulticpu} CPU times in case
-  of single-mesh and multi-mesh solutions with HP\_ISO
+  \caption{\label{fig:singlemulticpu} Cumulative CPU times in case
+  of single-mesh and multi-mesh configurations with HP\_ISO
   and HP\_ANISO refinement modes. (Notice log Y scale)}
@@
   \includegraphics[width=\columnwidth]{isoaniso_cpu}
-  \caption{\label{fig:isoanisocpu} CPU times in case 
+  \caption{\label{fig:isoanisocpu} Cumulative CPU times in case 
   of multi-mesh configuration with H\_ISO, H\_ANISO,
@@
   \includegraphics[width=\columnwidth]{isoanisop_cpu}
-  \caption{\label{fig:isoanisopcpu} CPU times in case 
+  \caption{\label{fig:isoanisopcpu} Cumulative CPU times in case 
   of multi-mesh configuration with P\_ISO, P\_ANISO, and
@@
 Fig.~\ref{fig:isoanisodof} and Fig.~\ref{fig:isoanisocpu} provide the comparison
-of H\_ISO, H\_ANISO, HP\_ISO, HP\_ANISO, and HP\_ANISO\_H modes in terms of CPU time
-and NDOFs.
+of H\_ISO, H\_ANISO, HP\_ISO, HP\_ANISO, and HP\_ANISO\_H modes in terms of 
+cumulative CPU time and NDOFs.
 Fig.~\ref{fig:isoanisopdof} and Fig.~\ref{fig:isoanisopcpu} show the similar
@@
 Although these parameters are empirical, they serve as an upper limit, given
-that the most refinement modes give significantly better results, i.e.
+that the most refinement modes give significantly better results ---
 $t<<500\ s$ and $N_{DOF} << 500$.
@@
   \includegraphics[width=\columnwidth]{cpu}
-  \caption{\label{fig:cpu} Comparative CPU time for different refinement modes.}
+  \caption{\label{fig:cpu} Comparative cumulative CPU time for different refinement modes.}
   \end{centering}
@@
 suitable refinement mode for the given problem. 
-Hence, some ways to optimize the model based on HP\_ANISO
-mode to improve the CPU time
-%TODO, continue here
-factor without significantly compromising the NDOFs will be considered. 
+Hence, some ways to optimize the HP\_ANISO model
+to improve the CPU time factor without significantly 
+compromising the NDOFs will be considered. 
 The desirable output would be HP\_ANISO problem size
-close to HP\_ANISO\_P CPU time. One way to optimize the problem
+close to HP\_ANISO\_P CPU time. 
+One way to optimize the problem
 is to choose more refined initial mesh. Another way would be to change
-the refinement frequency during the solving process. In theory, this
-could result in a fewer adaptivity steps which are quite expensive in terms
+the refinement frequency during the solving process. Theoretically it 
+could result in a fewer adaptivity steps which are rather expensive in terms
 of CPU time. Recall that up to this point,
-the initial mesh has been loaded in the beginning of each time step. 
-True, by employing these optimizations, we must know something about the problem
+the initial mesh was loaded in the beginning of each time step. 
+True, by employing the optimizations, one must know something about the problem
 and its solution beforehand. However, it could still be practial when solving a real problem
@@
 compared to the coarse initial mesh (Fig.~\ref{fig:mesh}~(a)) and 
-HP\_ANISO\_P solution is shown in Fig.~\ref{fig:refined-cpu} and Fig.~\ref{fig:refined-dof}.
+HP\_ANISO\_P solution are shown in Fig.~\ref{fig:refined-cpu} and Fig.~\ref{fig:refined-dof}.
 By using initially more refined mesh, the problem solving time
-can be reduced in case of HP\_ANISO, at the same time, the problem size increases.
-In this situation, HP\_ANISO\_P and HP\_ANISO perform equally well.
+can be reduced in case of HP\_ANISO, at the same time, the problem size increases
+as the initial mesh is not necessarily the most optimal one.
+However, in this situation, HP\_ANISO\_P and HP\_ANISO perform equally well.
 
@@
 unrefinement was performed in $\Delta t = 0.10\ s$ interval.
-However, this optimization did not result in a stable solution, i.e. the problem size 
+However, this optimization does not appear to result in a stable solution, 
+i.e. the problem size 
 does not remain steady, but starts to oscillate depending on the unrefinement
-frequency. This is shown in 
-Fig.~\ref{fig:unreffreq-dof}.
+frequency. This is shown in Fig.~\ref{fig:unreffreq-dof}.
 
 Therefore varying the unrefinement frequency will
-not likely result in desired results in real applications for given system of equation.
-At the same time, by varying a mesh size, optimal initial mesh could be found
+likely not result in desired results in real applications for given system of equation.
+At the same time, by varying the initial mesh size, optimal initial mesh could be found
 for both HP\_ANISO and HP\_ANISO\_P refinement modes.

### 2010-10-19 pugal-esco2010.tex
CiCP format

@@
-\documentclass[letterpaper,3p]{elsarticle}
+\documentclass[mathpazo]{cicp}
 
-\journal{Applied Mathematics and Computation}
+%\journal{Applied Mathematics and Computation}
 \usepackage{graphicx}
@@
 \usepackage{amsfonts}
-\usepackage{subfig}
+\usepackage{amsrefs}
+%\usepackage{subfig}
 
 \begin{document}
-\begin{frontmatter}
 
@@
 
-\author[unrme,tartu]{D.~Pugal}
-\ead{david.pugal@gmail.com}
+\author[Deivid Pugal et.~al.]{Deivid Pugal\affil{1}\comma\affil{2},
+Pavel Solin\affil{3}\comma\affil{4}\comma\corrauth,
+Kwang J. Kim\affil{1}, and Alvo Aabloo\affil{2}}
 
-\author[unrmath,czech]{P.~Solin\corref{cor2}}
-\ead{solin@unr.edu}
+\address{\affilnum{1}\ Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.\\
+\affilnum{2}\ Institute of Technology, Tartu University, Estonia\\
+\affilnum{3}\ Department of Mathematics and Statistics, University of Nevada, Reno, NV, U.S.A.\\
+\affilnum{4}\ Institute of Thermomechanics, Prague, Czech Republic}
 
-\author[unrme]{K.~J.~Kim\corref{cor1}}
-\ead{kwangkim@unr.edu}
+\emails{{\tt david.pugal@gmail.com} (D.~Pugal), {\tt solin@unr.edu} (P.~Solin),
+	{\tt kwangkim@unr.edu} (K.~Kim), {\tt alvo@ut.ee} (A.~Aabloo)}
 
-\author[tartu]{A.~Aabloo}
-\ead{alvo@ut.ee}
-
-\address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
-\address[unrmath]{Department of Mathematics and Statistics,
-University of Nevada, Reno, NV, U.S.A.}
-\address[czech]{Institute of Thermomechanics, Prague, Czech Republic}
-\address[tartu]{Institute of Technology, Tartu University, Estonia}
-
-\cortext[cor1]{Corresponding author}
-\cortext[cor2]{Principal corresponding author}
+%\author[unrme,tartu]{D.~Pugal}
+%\ead{david.pugal@gmail.com}
+%
+%\author[unrmath,czech]{P.~Solin\corref{cor2}}
+%\ead{solin@unr.edu}
+%
+%\author[unrme]{K.~J.~Kim\corref{cor1}}
+%\ead{kwangkim@unr.edu}
+%
+%\author[tartu]{A.~Aabloo}
+%\ead{alvo@ut.ee}
+%
+%\address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
+%\address[unrmath]{Department of Mathematics and Statistics,
+%University of Nevada, Reno, NV, U.S.A.}
+%\address[czech]{Institute of Thermomechanics, Prague, Czech Republic}
+%\address[tartu]{Institute of Technology, Tartu University, Estonia}
+%
+%\cortext[cor1]{Corresponding author}
+%\cortext[cor2]{Principal corresponding author}
 
@@
 
-\begin{keyword}
-  Ionic polymer-metal composites \sep IPMC \sep Nernst-Planck equation \sep Poisson equation 
-  \sep finite element method \sep space-time adaptivity, multimesh \emph{hp}-FEM 
-\end{keyword}
+%\begin{keyword}
+%\keywords{Ionic polymer-metal composites, IPMC, Nernst-Planck equation, Poisson equation,
+%finite element method, space-time adaptivity, multimesh \emph{hp}-FEM }
+%\end{keyword}
 
-\end{frontmatter}
+%see http://www.ams.org/mathscinet/msc/msc2010.html?t=35Qxx&btn=Current
+
+\ams{35Q84, 35Q05, 35J47}
+\keywords{Ionic polymer-metal composites, IPMC, Nernst-Planck equation, Poisson equation,
+finite element method, space-time adaptivity, multimesh \emph{hp}-FEM }
+\maketitle
+
+%\end{frontmatter}
 
@@
 
-\bibliographystyle{elsarticle-num}    % Bibliography: Author-Date system
+%\begin{thebibliography}{99}
+%\bibitem{\ldots}..
+
+%\end{thebibliography}
+
+%\bibliographystyle{amsrs}    % Bibliography: Author-Date system
 \bibliography{pugal-esco2010}      % pls. call your database here

### 2010-10-19 test.tex
CiCP format

\documentclass[mathpazo]{cicp}

%%%%% author macros %%%%%%%%%
% place your own macros HERE
%%%%% end %%%%%%%%%

\begin{document}
%%%%% title : short title may not be used but TITLE is required.
% \title{TITLE}
% \title[short title]{TITLE}
\title{A Demonstration of the \LaTeXe \ Class File for the
Communications in Computational Physics}

%%%%% author(s) :
% single author:
% \author[name in running head]{AUTHOR\corrauth}
% [name in running head] is NOT OPTIONAL, it is a MUST.
% Use \corrauth to indicate the corresponding author.
% Use \email to provide email address of author.
% \footnote and \thanks are not used in the heading section.
% Another acknowlegments/support of grants, state in Acknowledgments section
% \section*{Acknowledgments}
%\author[T.~Lam]{T.~Lam\corrauth}
%\address{Author Address}
%\email{{\tt cicp@global-sci.com} (T.~Lam)}

% multiple authors:
% Note the use of \affil and \affilnum to link names and addresses.
% The author for correspondence is marked by \corrauth.
% use \emails to provide email addresses of authors
% e.g. below example has 3 authors, first author is also the corresponding
%      author, author 1 and 3 having the same address.
 \author[Zhang Z R et.~al.]{Zhengru Zhang\affil{1}\comma\corrauth,
       Author Chan\affil{2}, and Author Zhao\affil{1}}
 \address{\affilnum{1}\ School of Mathematical Sciences,
          Beijing Normal University,
          Beijing 100875, P.R. China. \\
           \affilnum{2}\ Department of Mathematics,
           Hong Kong Baptist University, Hong Kong SAR}
 \emails{{\tt zhang@email} (Z.~Zhang), {\tt chan@email} (A.~Chan),
          {\tt zhao@email} (A.~Zhao)}
% \footnote and \thanks are not used in the heading section.
% Another acknowlegments/support of grants, state in Acknowledgments section
% \section*{Acknowledgments}

%%%%% Begin Abstract %%%%%%%%%%%
\begin{abstract}
This paper describes the use of the \LaTeXe \ {\sf cicp.cls} class file for
setting papers for the {\it Communications in Computational Physics}.
\end{abstract}
%%%%% end %%%%%%%%%%%

%%%%% AMS/PACs/Keywords %%%%%%%%%%%
\ams{52B10, 65D18, 68U05, 68U07}
% \pacs{}
\keywords{\LaTeXe}

%%%% maketitle %%%%%
\maketitle

%%%% Start %%%%%%
\section{Introduction}
This paper is described how to use the {\sf cicp.cls}\footnote{Current verions is 2.1. Please
ensure you use the most up to date class file, available from the
global-sci homepage at http://www.global-sci.com/.} class file for publication
in the {\it Communications in Computational Physics}.
The {\sf cicp.cls} class file preserves much of the standard \LaTeXe \ interface
so that authors can easily convert their standard \LaTeXe \ {\sf article} style
files to the {\sf cicp} style.

\section{Preparation of Manuscript}
The Title Page should contain the article title, authors' names and complete affiliations,
and email addresses of all authors. The Abstract should provide a brief summary of the main findings of the paper.

\medskip

References should be cited in the text by a number in square brackets. Literature cited should appear on a separate page at the
end of the article and should be styled and punctuated using standard abbreviations for journals
(see Thomson ISI list of journal abbreviations).
 For unpublished lectures of symposia,
include title of paper, name of sponsoring society in full, and date. Give titles of unpublished reports with ''(unpublished)''
following the reference. Only articles that have been published or are in press should be included in the references.
Unpublished results or personal communications should be cited as such in the text.
Please note the sample at the end of this paper.

Equations should be typewritten whenever possible and the number placed in parentheses at the right margin.
Reference to equations should use the form ''Eq. (2.1)'' or simply ''(2.1).''
Superscripts and subscripts should be typed or handwritten clearly above and below the line, respectively.

Figures should be in a finished form suitable for publication.
Number figures consecutively with Arabic numerals.
Lettering on drawings should be of professional quality or generated by high-resolution
computer graphics and must be large enough to withstand appropriate reduction for publication.
For example, if you use {\sf MATLAB} to do figure plots,
axis labels should be at least point 18. Title should be 24 points or above. Tick marks labels
better have 14 points or above. Line width should be 2 (or above).

Illustrations in color in most cases can be accepted only if the authors defray the cost.
At the Editor's discretion a limited number of color figures each year of special interest
will be published at no cost to the author.

\section{Header Information}
The heading for any file using {\sf cicp.cls} is like this;
\begin{verbatim}

\documentclass[mathpazo]{cicp}

\begin{document}

\title{Make the Title in Title Case}

\author[An Author et.~al]{First Author\affil{1},
Second Author\affil{2}\comma\corrauth
\and Third Author\affil{1}}

\address{\affilnum{1}\ Address for first and third authors \\
\affilnum{2}\ Address for second author}

\emails{{\tt cicp@global-sci.com} (A.~Author),
{\tt second@author.email} (S.~Author),
{\tt third@author.email} (T.~Author)}

\begin{abstract}
Text here, no equation, no citation, no reference.
\end{abstract}

\ams{list here}
\pacs{list here}
\keywords{list here}

\maketitle

\section{First Section}

\end{document}

\end{verbatim}

\noindent {\bf Notes:}
\begin{enumerate}
\item Starting from volume two, we use package {\sf mathpazo}. If you do not have this package,
you just remove the option {\sf mathpazo} in $\backslash$documentclass.
We can make it for you in the printing version.
\item The first argument in square bracket of $\backslash$author is a MUST.
It is for the running heads.
$\backslash$corrauth should be provided to indicate the
corresponding author. $\backslash$email(s) is used to show that
author(s) email address(es) in footnote.
\item The abstract should be captable of standing by itself, in the
absence of the body of the article and of the bibliography. It is forced
to print within one page, so there may be problem if it is too long.
\item You may have your own macros but keep it to an absolute minimum.
\item $\backslash$thanks is not working in this style. You should use
$\backslash$section*\{Acknowlegments\} for acknowlegments/grant support as
the last section (just before references).
\end{enumerate}

\section{Some Remarks}
\subsection{Mathematics}
{\sf cicp.cls} makes the full functionality of \AmS\TeX \ available. We encourage
the use of the {\sf align}, {\sf gather} and {\sf multline} environments for displayed
mathematics.

\subsection{Cross-referencing}
The use of the \LaTeX cross-reference system for figures, tables, equations
and citations is encouraged.

%%%% Acknowledgments %%%%%%%%
\section*{Acknowledgments}
The author would like to thank  ....

%%%% Bibliography  %%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{Goossens} Michel Goossens, Frank Mittelbach and Alexander Samarin,
The LaTeX Companion,
Addison-Wesley, 1994.
\bibitem{Kopka}Helmut Kopka and Patrick W.~Daly, A Guide to LaTeX,
Addison-Wesley, 1999.
\bibitem{Knuth}Donald E. Knuth, The TeXbook,
Addison-Wesley, 1992.
\bibitem{Other}A.~N.~Other, A demonstration of the LaTeX2e class file for
the International Journal for Numerical Methods in Engineering,
Int.~J.~Numer.~Meth.~Engng,  00 (2000), 1-6.
\bibitem{Yin}Z.~Yin, H.~J.~H.~Clercx and D.~C.~Montgomery,
An easily implemented task-based parallel scheme for the Fourier
pseudospectral solver applied to 2D Navier-Stokes turbulence,
Computers \& Fluids, 33 (2004), 509-520.
\end{thebibliography}

\end{document}

### 2010-10-25 intro.tex
Pavel's suggestions, improving the results section
Results and conclusions improved
CiCP format
New iteration, Pavel, October 24.

--- 2010-10-11 intro.tex
@@
 Ionic Polymer-Metal Composites (IPMC) have been studied during the past two 
-decades for their potential to serve as noiseless mechanoelectrical and electromechanical transducers.
+decades for their potential to serve as noiseless mechanoelectrical and electromechanical 
+transducers \cite{basu1997membrane,shahinpoor2001smartmat,
+nasser2002applied,newbury2003intelligent, wallmersperger2007appliedphysics,
+pugal2008appliedphysics,pugal2010polymer}.
 The advantages of IPMC over other electroactive polymer actuators
@@
   \begin{centering}
-    \subfloat[~]{\begin{centering}
-      \includegraphics[scale=0.6]{IPMC}
-      \par\end{centering}}~
-    \subfloat[~]{\begin{centering}
-      \includegraphics[scale=0.6]{IPMC_bent}
-      \par\end{centering}}
-  \par\end{centering}
+  \includegraphics[scale=0.7]{IPMC_bending}
   \caption{\label{fig:conceptual}Conceptual model of the actuation
@@
 	the distribution and resulting bending after applying a voltage (b).}
-\vspace{-1cm}
+  \end{centering}
+%\vspace{-1cm}
 \end{figure}
-\newpage
+%\newpage
 %The derived and implemented model helps to predict the actuation of the
@@
 that includes ionic migration, diffusion, and convection. The charge transport 
-process is a key mechanism for electromechanical transduction 
-\cite{basu1997membrane,shahinpoor2001smartmat,
-nasser2002applied,newbury2003intelligent, wallmersperger2007appliedphysics,
-pugal2008appliedphysics,pugal2010polymer}.
+process is a key mechanism for electromechanical transduction.
 
@@
 where $\varepsilon$ is the absolute dielectric permittivity. The
-charge density $\rho$ is defined via
-\begin{equation}
-  \rho=C-C_{0}
-  \label{eq:rho}
-\end{equation}
+charge density $\rho = C-C_{0}$ 
 where $C_{0}$ is a constant anion concentration.
 
-The outline of the paper is as follows: Section \ref{sec:moti} explains why 
-it is extremely difficult to find a good mesh for the PNP problem, and 
-hence why we are interested in exploring adaptive algorithms. The PNP model 
-is presented in Section \ref{sec:model} where also its weak formulation is derived. 
-Numerical results and comparisons are presented in Section \ref{sec:results},
-and conclusion and outlook are drawn in Section \ref{sec:conc}.
+The outline of the paper is as follows: Section \ref{sec:moti} shows that 
+the solution components $C$ and $\phi$ have very different behavior, which
+is the reason why it is difficult to find a common mesh that would be optimal 
+for both of them. This explains why we are interested in approximation them
+on individual meshes equipped with mutually independent adaptivity 
+mechanisms. The PNP model is presented in Section \ref{sec:model} where also its weak 
+formulation for the Newton's method is derived. Section \ref{sec:hermes}
+presents a brief overview of a novel adaptive multimesh $hp$-FEM 
+method~\cite{solin2010monolithic,solin2010adaptive,dubcova2010space,solini2010adaptive}
+that is used to solve the 
+problem numerically. Numerical results and comparisons are presented in Section 
+\ref{sec:results}, and conclusion and outlook are drawn in Section \ref{sec:conc}.

### 2010-10-25 model.tex
CiCP format
New iteration, Pavel, October 24.

@@
 
-\subsection{Weak form of Poisson-Nernst-Planck system}
+\subsection{Weak form of the PNP system}
 
@@
 %An implicit version of the weak form of PNP was derived in~\cite{pugal2010spie}.
-To make our results easily reproducible, we present a rather detailed
-derivation of weak forms of Eqs.~\eqref{eq:nernst-planck} and 
+To make our results easily reproducible, in the following we present the derivation 
+of weak forms of Eqs.~\eqref{eq:nernst-planck} and 
 \eqref{eq:poisson}, as well as formulas for the Jacobian matrix and residual 
 vector that are used in actual computations.
-To facilitate the derivation, we introduce two additional constants 
-\begin{eqnarray}
-  K & = &z \mu F,\\
-  L&=&\frac{F}{\varepsilon}.
+To simplify notation, we define
+\begin{equation}
+  K = z \mu F,\ \ \
+  L = \frac{F}{\varepsilon}.
   \label{eq:KL}
-\end{eqnarray}
-After using Eq.~\eqref{eq:rho} and the constants $K$ and $L$, 
-Eq.~\eqref{eq:nernst-planck} and Eq.~\eqref{eq:poisson} become
+\end{equation}
+Eqs.~\eqref{eq:nernst-planck} and \eqref{eq:poisson} yield
 \begin{eqnarray}
@@
 \end{eqnarray}
-The boundary condition Eq.~\eqref{eq:nernst-planck-boundary} now has the form
+Boundary condition Eq.~\eqref{eq:nernst-planck-boundary} has the form
 \begin{equation}
@@
 equations, the appropriate function space for them is the Sobolev space 
-$V=H^1\left(\Omega\right)$, where 
-$H^1\left(\Omega\right)=\left\{v\in L^2\left(\Omega\right);\ \nabla v \in \left[L^2\left(\Omega\right)\right]^2\right\}$.
-
+$V=H^1\left(\Omega\right)$ where 
+$$H^1\left(\Omega\right)=\left\{v\in L^2\left(\Omega\right);\ \nabla v \in \left[L^2\left(\Omega\right)\right]^2\right\}.
+$$
 In order to derive the weak form of the Nernst-Planck equation Eq.~\eqref{eq:nernst-planck-2},
@@
   \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}
-  -\int_{\Omega}D\nabla^2Cv^C d\mathbf{x}-\int_{\Omega}K\nabla C\cdot
-  \nabla\phi v^C d\mathbf{x} - \int_{\Omega}KC\nabla^2\phi v^C d\mathbf{x}=0.
+  -\int_{\Omega}D\nabla^2Cv^C d\mathbf{x}-\int_{\Omega}K\nabla C\cdot\nabla\phi v^C d\mathbf{x}
+   - \int_{\Omega}KC\nabla^2\phi v^C d\mathbf{x}=0.
   \label{eq:nernst-planck-weak1}
@@
 we obtain
-\begin{eqnarray}
- && \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}+
+$$
+ \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}+
   D\int_{\Omega}\nabla C\cdot\nabla v^C d\mathbf{x}-
-  K\int_{\Omega}\nabla C \cdot \nabla \phi v^C d\mathbf{x}+
-  K\int_{\Omega}\nabla\left(Cv^C\right)\cdot \nabla \phi d\mathbf{x}\\
-  &&-D\int_{\partial\Omega}\frac{\partial C}{\partial n}v^C d\mathbf{S}-
+  K\int_{\Omega}\nabla C \cdot \nabla \phi v^C d\mathbf{x}
+$$
+\begin{equation}
+  + K\int_{\Omega}\nabla\left(Cv^C\right)\cdot \nabla \phi d\mathbf{x}
+  -D\int_{\partial\Omega}\frac{\partial C}{\partial n}v^C d\mathbf{S}-
   \int_{\partial\Omega}K\frac{\partial\phi}{\partial n}Cv^C d\mathbf{S}=0.
   \label{eq:nernst-planck-weak2}
-\end{eqnarray}
+\end{equation}
 Expanding the nonlinear term and using the boundary condition 
 \eqref{eq:nernst-planck-boundary-2}, we have
-\begin{equation}
+$$
   \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}+
   D\int_{\Omega}\nabla C \cdot \nabla v^C d\mathbf{x}-
-  K\int_{\Omega}\nabla C \cdot \nabla \phi v^C d\mathbf{x}+
-  K\int_{\Omega}\nabla \phi \cdot \nabla C v^C d\mathbf{x}+
+  K\int_{\Omega}\nabla C \cdot \nabla \phi v^C d\mathbf{x}
+$$
+\begin{equation}
+  + K\int_{\Omega}\nabla \phi \cdot \nabla C v^C d\mathbf{x}+
   K\int_{\Omega} C \left(\nabla\phi\cdot\nabla v^C\right) d\mathbf{x}=0.
@@
 
+\newpage
+
+\noindent
 The Jacobian matrix $J(Y) = DF/DY$ has a $2\times 2$ block structure,
@@
 \end{eqnarray*}
-over $k$ until it converges. Then we set $Y^{n+1} := Y^{n+1}_{k+1}$. 
+over $k$ until it converges. Then we set $Y^{n+1} := Y^{n+1}_{k}$. 
 We use a combined stopping criterion 
@@
 
-In a traditional low-order FEM, refining an element is not algorithmically complicated,
+In traditional low-order FEM (based on piecewise-linear or piecewise quadratic elements), 
+refining an element is not algorithmically complicated,
 and so the most difficult part is to find out what elements should be refined. 
 To do this, various techniques ranging from rigorous guaranteed a-posteriori 
-error estimates to heuristic criteria such as residual error indicators, 
-error indicators based on steep gradients, etc are employed. 
-Unfortunately, none of these approaches are suitable for real-life 
+error estimates to heuristic criteria such as residual error indicators or
+error indicators based on steep gradients are employed.
+
+However, none of these approaches is suitable for
 multiphysics coupled problems or higher-order finite element methods: 
-rigorous guaranteed error estimates only exist for very simple problems 
-(such as linear elliptic PDE), and moreover only for low-order finite elements 
-(such as piecewise linear approximations). These heuristic techniques 
-may fail in more complicated situations, and moreover they lack a 
-transparent relation to the true approximation error.
+Rigorous guaranteed error estimates only exist for very simple problems 
+(such as linear elliptic PDE) and only for low-order finite elements.
+Heuristic techniques are usually somehow doable for all problems, but 
+they fail in more complicated situations. Moreover, they lack a 
+transparent relation to the true approximation error and thus they may
+give wrong results.
 
-In order to obtain fast, usable adaptivity, one has to resort to higher-order finite 
-elements and adaptive \emph{hp}-FEM.
-Automatic adaptivity in the \emph{hp}-FEM is substantially different from adaptivity 
-in low-order FEM, since every element can be refined in many different ways. 
-For illustration, Fig.~\ref{fig:refinements} shows several illustrative 
-refinement candidates for a fourth-order element.
+Automatic adaptivity in higher-order finite element methods (\emph{hp}-FEM) 
+is much different from adaptivity in low-order FEM. Firstly, analytical
+error estimates capable of guiding adaptive $hp$-FEM do not exist even for 
+the simplest linear elliptic equations, not speaking about nonlinear multiphysics 
+coupled systems. Secondly,
+a higher-order element can be refined in many different ways, as illustrated 
+in Fig.~\ref{fig:refinements}.
 \begin{figure}[!ht]
@@
   \end{centering}
-\vspace{-0.5cm}
+%\vspace{-0.5cm}
 \end{figure}
 
-\newpage
+%\newpage
 The number of possible element refinements is implementation dependent. 
-In general it is very low in \emph{h} or \emph{p} adaptivity, 
-and higher in \emph{hp}-adaptivity. It rises very fast when 
-anisotropic refinements are considered.
+In general it is very low in \emph{h}-adaptivity and \emph{p}-adaptivity, 
+and much higher in \emph{hp}-adaptivity. Moreover, this number grows very 
+fast when anisotropic refinements are enabled.
 
@@
   \begin{centering}
-  \includegraphics[width=0.7\columnwidth]{cand_list_quads}
+  \includegraphics[width=0.8\columnwidth]{cand_list_quads}
   \caption{\label{fig:candlist} Refinement candidates for every

### 2010-10-25 motivation.tex
CiCP format
New iteration, Pavel, October 24.

@@
 
-In this section we use a simplified one-dimensional model to illustrate the 
-principal difficulties encountered in the numerical solution of the 
-PNP system.
-Table~\ref{Table:used-constants} shows constants that we will use in 
-computations in this section as well as in the rest of the paper:
+In this section we use a simplified one-dimensional PNP model to illustrate the 
+principal difficulties encountered in the numerical solution. Table~\ref{Table:used-constants} 
+shows relevant constants.
 
@@
 
+\noindent
 Fig.~\ref{fig:comsol-conc-volt} shows a typical solution for $C$ and $\phi$
 at $t=0.1\ s$ and $t=3.0\ s$.
-The solution has 
-two notable characteristics: For the most part of the domain $\Omega$,
-the gradient $\nabla C = 0$. Close to $\partial \Omega_2$, $\nabla C$ is
-nonzero and moving in time, and $\nabla C$ is very large at $\partial \Omega_1$.
-At the same time, $\phi$ is a "nice" smooth function for the most part of 
-$\Omega$ but it has a large gradient at $\partial \Omega_2$.
-This makes the choice of an optimal mesh extremely difficult. Even if the 
-solution was stationary, an optimal mesh for $C$ could never be 
-optimal for $\phi$ and vice versa.
 
@@
   \begin{centering}
-      \includegraphics[]{comsol_conc_volt}
+      \includegraphics{comsol_conc_volt}
+      %\includegraphics{IPMC_bending}
   \caption{Sample concentration $C$ and voltage $\phi$
@@
 \end{figure}
+
+The reader can observe that the solution has 
+two notable characteristics: For the most part of the domain $\Omega$,
+the gradient $\nabla C = 0$. Close to $\partial \Omega_2$, $\nabla C$ is
+nonzero and moving in time, and $\nabla C$ is very large at $\partial \Omega_1$.
+At the same time, $\phi$ is a "nice" smooth function for the most part of 
+$\Omega$ but it has a large gradient at $\partial \Omega_2$.
+This makes the choice of an optimal mesh highly problematic. Even if the 
+solution was stationary, an optimal mesh for $C$ could never be 
+optimal for $\phi$ and vice versa.
 

### 2010-10-25 pugal-esco2010.tex
New iteration, Pavel, October 24.

@@
 
-\author[Deivid Pugal et.~al.]{Deivid Pugal\affil{1}\comma\affil{2},
-Pavel Solin\affil{3}\comma\affil{4}\comma\corrauth,
-Kwang J. Kim\affil{1}, and Alvo Aabloo\affil{2}}
+\author[Deivid Pugal et.~al.]{Deivid Pugal\affil{1}\comma\affil{4},
+Pavel Solin\affil{2}\comma\affil{3}\comma\corrauth,
+Kwang J. Kim\affil{1}, and Alvo Aabloo\affil{4}}
 
 \address{\affilnum{1}\ Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.\\
-\affilnum{2}\ Institute of Technology, Tartu University, Estonia\\
-\affilnum{3}\ Department of Mathematics and Statistics, University of Nevada, Reno, NV, U.S.A.\\
-\affilnum{4}\ Institute of Thermomechanics, Prague, Czech Republic}
+\affilnum{2}\ Department of Mathematics and Statistics, University of Nevada, Reno, NV, U.S.A.\\
+\affilnum{3}\ Institute of Thermomechanics, Prague, Czech Republic\\
+\affilnum{4}\ Institute of Technology, Tartu University, Estonia}
 
@@
 \begin{abstract}
-In this paper we study a multiphysics coupled problem consisting 
-of the Poisson and Nernst-Planck equations, that is used to 
-model ionic polymer-metal composite (IPMC) materials. 
-The problem is discretized using the finite element method (FEM) and solved using 
-space-time adaptive \emph{hp}-FEM algorithms provided by the Hermes 
-library. Numerical results are presented and discussed, including 
-comparison of various versions of adaptive $hp$-FEM and conventional 
-low-order FEM. In particular, we discuss the performance of a novel
-adaptive multimesh $hp$-FEM algorithm.
+We are concerned with a model of ionic polymer-metal composite (IPMC) materials
+that consists of a coupled system of the Poisson and Nernst-Planck equations, 
+discretized by means of the finite element method (FEM). We show that due to the 
+transient character of the problem it is efficient to use adaptive algorithms 
+that are capable of changing the mesh dynamically in time. We also show 
+that due to large qualitative and quantitative differences between the 
+two solution components, it is efficient to approximate them on different 
+meshes using a novel adaptive multimesh \emph{hp}-FEM. The study is 
+accompanied with numerous computations and comparisons of the adaptive 
+multimesh \emph{hp}-FEM with several other adaptive FEM algorithms. 
 \end{abstract}
@@
 \keywords{Ionic polymer-metal composites, IPMC, Nernst-Planck equation, Poisson equation,
-finite element method, space-time adaptivity, multimesh \emph{hp}-FEM }
+finite element method, FEM, adaptive multimesh \emph{hp}-FEM }
 \maketitle

### 2010-10-25 results.tex
Minor fixes
New iteration, Pavel, October 24.

@@
 \section{Numerical Results and Comparisons}\label{sec:results}
+
+The solutions to the PNP problem exhibit a specific behavior that was 
+described above. In order to find the best adaptive method to deal with 
+this type of problems, we performed numerous computations using all 
+adaptivity modes in both the single-mesh and multi-mesh regimes.
+In the numerical experiments we paid attention to the 
+relative error, cumulative CPU time, and problem size 
+in terms of number of degrees of freedom (DOF) in each 
+time step.
+
+We used two types of initial meshes --- a finer mesh shown 
+in Fig.~\ref{fig:mesh}~(c) was used for \emph{p}-adaptivity
+and a very coarse initial mesh shown in  Fig.~\ref{fig:mesh}~(a) was 
+used for $h$-adaptivity and $hp$-adaptivity.
 
@@
 	and refined mesh (c) were used in the initial calculations, the latter one
-	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
+	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh (b) was
 	used later to optimize the \emph{hp}-adaptive refinement solutions.}
@@
 \end{figure}
-Calculation for all the refinement modes were performed
-in both single-mesh and multi-mesh configurations. 
-The following numerical results were recorded for each 
-refinement mode: converged relative error, cumulative CPU
-time, and the problem size in terms of number
-of degrees of freedoms (NDOFs) at each time step. 
-Two types of initial meshes were used --- in case of only \emph{p}-adaptivity,
-more refined mesh was used (Fig.~\ref{fig:mesh}~(c)) to ensure
-the error convergence.
-When the element size refinement
-was also enabled (all \emph{h}/\emph{hp} refinement modes), very coarse initial mesh
-was used (see Fig.~\ref{fig:mesh}~(a)) to let the adaptivity
-algorithm find the most optimal mesh. That coarse initial mesh might not be
-suitable for practical applications, as will be demonstrated in the
-end of this section, however, it provides a good insight into the
-adaptivity performance of Hermes.
-In both cases, the initial mesh was loaded at each time step of the
-calculation.
+
+An example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
+calculated with the HP\_ANISO refinement mode is shown
+in Figs.~\ref{fig:cphi-1} and \ref{fig:cphi-2}.
 
@@
   \begin{centering}
-  \includegraphics[width=.75\columnwidth]{cphi}
-  \caption{\label{fig:cphi} Concentration $C$
-  and voltage $\phi$ at two different time steps
-  (HP\_ANISO refinement mode was used). This is a 2D solution shown
-  in 3D, where the height indicates the values of $C$ and $\phi$.}
+  \includegraphics[width=.75\columnwidth]{cphi-1}
+  \caption{\label{fig:cphi-1} Concentration $C$
+  and voltage $\phi$ at $t=0.7\ s$.}
   \end{centering}
 \end{figure}
-Example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
-calculated with HP\_ANISO refinement mode is shown
-in Fig.~\ref{fig:cphi}. The time $t=0.7\ s$ was chosen because
-by that time (with given constants in Table~\ref{Table:used-constants}),
-some ionic migration has already taken place and
-the concentration gradients near the boundaries $\partial\Omega_1$ and
-$\partial\Omega_3$ have formed. The automatic mesh refinements
-at different time steps are clearly visible in the figure --- especially
-near $\partial\Omega_1$, where the $C_{\Omega_1}\approx 0$ and
-the gradient $\nabla C$ is
-shifting in time (this is also demonstrated in Fig.~\ref{fig:comsol-conc-volt}).
 
-The following subsections provide a detailed comparison of
-the different refinement modes and try to estimate the most suitable
-one for the given problem.
+\newpage
 
-\subsection{Optimal refinement modes}
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=.75\columnwidth]{cphi-2}
+  \caption{\label{fig:cphi-2} Concentration $C$
+  and voltage $\phi$ at $t=3.0\ s$.}
+  \end{centering}
+\end{figure}
+
+The reader can see that at $t=0.7\ s$ some ionic migration has already 
+taken place and large concentration gradients near the boundaries $\partial\Omega_1$ 
+and $\partial\Omega_3$ have formed. The figures also show that the meshes 
+at $t=0.7\ s$ and $t=3.0\ s$ are different.
+
+\subsection{Comparison of single mesh low-order FEM and $hp$-FEM}
+
+Comparison of single mesh H\_ANISO with p=1, single mesh H\_ANISO with p=2
+and single mesh HP\_ANISO should be added here to make the point that 
+hp-FEM is much better than low-order FEM. 
+Otherwise the reader does not know 
+why we are just using hp-FEM in the following. Or is there a reason 
+why you do not want to add this here --  long computing time for hp-FEM or something 
+else?
+
+\subsection{Comparison of single-mesh and multi-mesh $hp$-FEM}
+
+Running the simulation with different adaptivity modes 
+and meshes showed that the multi-mesh $hp$-FEM configuration resulted into
+the smallest problems, shortest computing times, and better or the same error 
+convergence compared to any single-mesh configuration.
+This is illustrated in Figs.~\ref{fig:singlemultidof} 
+and Fig.~\ref{fig:singlemulticpu}.
 
@@
   \includegraphics[width=\columnwidth]{singlemulti_dof}
-  \caption{\label{fig:singlemultidof} NDOFs in case 
-  of single-mesh and multi-mesh configurations with HP\_ISO
-  and HP\_ANISO refinement modes. (Notice log Y scale)}
+  \caption{\label{fig:singlemultidof} Number of degrees of freedom (DOF) as a function 
+  of physical time for single-mesh and multi-mesh configurations with the HP\_ISO
+  and HP\_ANISO adaptivity modes. Note logarithmic scale on the vertical axis.}
+\vspace{-6mm}
   \end{centering}
@@
   \includegraphics[width=\columnwidth]{singlemulti_cpu}
-  \caption{\label{fig:singlemulticpu} Cumulative CPU times in case
-  of single-mesh and multi-mesh configurations with HP\_ISO
-  and HP\_ANISO refinement modes. (Notice log Y scale)}
+  \caption{\label{fig:singlemulticpu} Cumulative CPU time as a function 
+  of physical time for single-mesh and multi-mesh configurations with the HP\_ISO
+  and HP\_ANISO adaptivity modes. Note logarithmic scale on the vertical axis.}
   \end{centering}
 \end{figure}
+
+\noindent 
+Fig. \ref{fig:poly} shows higher-order meshes in the adaptive multimesh $hp$-FEM
+computation for $C$ and $\phi$ at $t = 0.7$ s. Different 
+colors mean different polynomial degrees. A diagonal pattern inside an element 
+tells that the element has different polynomial degrees in the 
+horizontal and vertical directions.
 
@@
   \includegraphics[width=.75\columnwidth]{poly}
-  \caption{\label{fig:poly} Polynomial degree space
-  for $C$ and $\phi$ at $t=0.7\ s$ The color indicates
-  the maximum polynomial degree of the corresponding element.}
+  \caption{\label{fig:poly} Higher-order FEM mesh for 
+  $C$ and $\phi$ at $t=0.7\ s$. }
   \end{centering}
@@
 
-Running the simulation with different refinement modes 
-and meshes showed that the multi-mesh configuration generally results in
-a smaller problem, faster calculation, and better or similar error convergence
-compared to the single-mesh configuration.
-This is well illustrated in Fig.~\ref{fig:singlemultidof} 
-and Fig.~\ref{fig:singlemulticpu}.
-The result can be understood when considering Fig.~\ref{fig:cphi} --- in the vicinity
-of the boundaries $\partial \Omega_1$ and $\partial\Omega_3$ the concentration gradient
-is greate than voltage gradient, namely $\nabla C >> \nabla \phi$. Therefore,
-adapting the mesh for both variables is not reasonable in terms of
-number of degrees of freedom. For instance,
-the solution space with corresponding mesh in case of
-HP\_ANISO at $t=0.7\ s$ is shown in Fig.~\ref{fig:cphi}. The corresponding polynomial
-degree space for multi-mesh configuration is shown in Fig.~\ref{fig:poly}. 
-Notice that the adaptivity algorithm
-of Hermes has increased the maximum polynomial degree for the $C$-space to~7, however,
-the maximum polynomial degree for the $\phi$-space is~2. Furthermore,
-the mesh is significantly more refined for $C$.
-For most of the cases using the multi-mesh results in similar or better CPU time.
-It means that multi-mesh takes less computational resources. Only excpetion was HP\_ANISO\_H 
-refinement mode for which the single mesh configuration resulted slightly faster
-calculation time. 
-Based on the results, only multi-mesh configurations will be considered
-in the following comparisons.
+These result are in good agreement with Fig.~\ref{fig:cphi-2} -- in the vicinity
+of the boundaries $\partial \Omega_1$ and $\partial\Omega_3$, the concentration gradient
+is much greater than the voltage gradient. Therefore the multimesh $hp$-FEM adaptivity 
+algorithm has increased the maximum polynomial degree for the $C$-space to~7 while 
+the maximum polynomial degree for the $\phi$-space is~2. One can also see that the mesh 
+is significantly more refined for $C$.
+Since these results are representative for all adaptivity modes, only multi-mesh 
+configurations are considered in the following.
+
+\subsection{Comparison of isotropic and anisotropic refinements}
+
+Next we would like to illustrate the role of anisotropic mesh refinements.
+Figs.~\ref{fig:isoanisodof} and \ref{fig:isoanisocpu} show typical results 
+for the H\_ISO, H\_ANISO, HP\_ISO, HP\_ANISO adaptivity modes in terms 
+of DOF and cumulative CPU time.
 
@@
   \includegraphics[width=\columnwidth]{isoaniso_dof}
-  \caption{\label{fig:isoanisodof} NDOFs in case 
-  of multi-mesh configuration with H\_ISO, H\_ANISO,
-  HP\_ISO, HP\_ANISO, and single-mesh configuration with HP\_ANISO\_H
-  refinement modes. (Notice log Y scale)}
+  \caption{\label{fig:isoanisodof} Number of DOF as a function of physical time for 
+  multi-mesh configurations with H\_ISO, H\_ANISO,
+  HP\_ISO, and HP\_ANISO adaptivity modes.}
   \end{centering}
@@
   \includegraphics[width=\columnwidth]{isoaniso_cpu}
-  \caption{\label{fig:isoanisocpu} Cumulative CPU times in case 
-  of multi-mesh configuration with H\_ISO, H\_ANISO,
-  HP\_ISO, HP\_ANISO, and single-mesh configuration with HP\_ANISO\_H
-  refinement modes. (notice log Y scale)}
+  \caption{\label{fig:isoanisocpu} Cumulative CPU time as a function of physical time 
+  for multi-mesh configurations with H\_ISO, H\_ANISO,
+  HP\_ISO, and HP\_ANISO adaptivity modes.}
   \end{centering}
 \end{figure}
+
+\noindent
+Figs.~\ref{fig:isoanisopdof} and \ref{fig:isoanisopcpu} present a similar 
+comparsion for the P\_ISO, P\_ANISO, and HP\_ANISO\_P modes. Recall that these 
+computations use a different initial mesh that was a-priori refined in space.
+
+\newpage
 
@@
   \includegraphics[width=\columnwidth]{isoanisop_dof}
-  \caption{\label{fig:isoanisopdof} NDOFs in case 
-  of multi-mesh configuration with P\_ISO, P\_ANISO, and
-  HP\_ANISO\_P refinement modes.}
+  \caption{\label{fig:isoanisopdof} Number of DOF as a function of physical time
+  for multi-mesh configurations with P\_ISO, P\_ANISO, and
+  HP\_ANISO\_P adaptivity modes.}
   \end{centering}
@@
   \includegraphics[width=\columnwidth]{isoanisop_cpu}
-  \caption{\label{fig:isoanisopcpu} Cumulative CPU times in case 
-  of multi-mesh configuration with P\_ISO, P\_ANISO, and
-  HP\_ANISO\_P refinement modes.}
-  \end{centering}
-\end{figure}
-To narrow down the list of refinement modes for the given problem, first the
-isotropic and anisotropic adaptivities were compared. The \emph{p}-adaptivity
-modes were compared separately as they used more refined initial mesh 
-(shown in Fig.~\ref{fig:mesh}~(c)).
-Fig.~\ref{fig:isoanisodof} and Fig.~\ref{fig:isoanisocpu} provide the comparison
-of H\_ISO, H\_ANISO, HP\_ISO, HP\_ANISO, and HP\_ANISO\_H modes in terms of 
-cumulative CPU time and NDOFs.
-Fig.~\ref{fig:isoanisopdof} and Fig.~\ref{fig:isoanisopcpu} show the similar
-comparsion for the P\_ISO, P\_ANISO, and HP\_ANISO\_P modes.
-It is not difficult to see that the anisotropic refinement modes result in a reasonable problem
-size and the problems solve within a reasonable calculation time. It is interesting
-to note that HP\_ANISO results in the smallest problem size. Also, in
-\emph{p}-adaptivity group, HP\_ANISO\_P results in the smallest problem size
-at each time step, whereas P\_ISO and P\_ANISO result in a very large problem size
-during the first time steps of the solution.
-Here the term ``reasonable problem size''
-means that the number of degrees of freedom in time converges
-to so that $N_{DOF}<500$, and the term ``reasonable calculation time''
-means that the calculation (step $\tau=0.01\ s$, physical
-time $t_{end}=3.0\ s$) time $t$ on a givem system was $t<500\ s$.
-Although these parameters are empirical, they serve as an upper limit, given
-that the most refinement modes give significantly better results ---
-$t<<500\ s$ and $N_{DOF} << 500$.
-
-\subsection{Quantitative analysis of the refinement modes}
-
-Based on the results in the previous subsection, H\_ANISO, HP\_ANISO,
-and HP\_ANISO\_H from the \emph{hp/h}-adaptivity group and HP\_ANISO\_P
-from \emph{p}-adaptivity group will be compared
-in terms of NDOFs and cumulative CPU time. 
-In all of the cases, the relative 
-error at each time step remained below
-the threshold which was set to $e_{th}=0.5\%$ between the coarse mesh
-and fine mesh solutions, therefore the error-time plot will not be considered.
-
-\begin{figure}[!ht]
-  \begin{centering}
-  \includegraphics[width=\columnwidth]{cpu}
-  \caption{\label{fig:cpu} Comparative cumulative CPU time for different refinement modes.}
+  \caption{\label{fig:isoanisopcpu} Cumulative CPU times as a function of physical time
+  for multi-mesh configurations with P\_ISO, P\_ANISO, and
+  HP\_ANISO\_P adaptivity modes.}
   \end{centering}
@@
 
-\begin{figure}[!ht]
-  \begin{centering}
-  \includegraphics[width=\columnwidth]{dof}
-  \caption{\label{fig:dof} Comparative NDOFs at each time step for 
-  different refinement modes.}
-  \end{centering}
-\end{figure}
+As a conclusion, the reader can see that the anisotropic adaptivity modes always perform better than 
+the isotropic ones. In particular, HP\_ANISO results into the smallest problem size. 
+In the \emph{p}-adaptivity group, HP\_ANISO\_P leads to a small problem size
+consistently in each time step, whereas P\_ISO and P\_ANISO yield large problems
+during the first few time steps.
 
-Fig.~\ref{fig:cpu} shows the cumulative CPU time for different refinement 
-modes at each time step --- the results were recorded on the same computer
-for the CPU times to be comparable.
-We see that HP\_ANISO\_H and HP\_ANISO require the most
-resources. This can be understood from the fact that in case of these 
-refinement modes the adaptivity algorithm has the largest number of 
-candidates (see Section.~\ref{sec:model} and Fig.~\ref{fig:refinements})
-from which a particular refinement can be chosen.
-At the same time, HP\_ANISO\_P is the fastest compared to the other refinement modes.
-This can be attributed to the finer inital mesh.
+%
+%\subsection{Quantitative analysis of the refinement modes}
+%
+%Based on the results in the previous subsection, H\_ANISO, HP\_ANISO,
+%and HP\_ANISO\_H from the \emph{hp/h}-adaptivity group and HP\_ANISO\_P
+%from \emph{p}-adaptivity group will be compared
+%in terms of NDOFs and cumulative CPU time. 
+%In all of the cases, the relative 
+%error at each time step remained below
+%the threshold which was set to $e_{th}=0.5\%$ between the coarse mesh
+%and fine mesh solutions, therefore the error-time plot will not be considered.
+%
+%\begin{figure}[!ht]
+%  \begin{centering}
+%  \includegraphics[width=\columnwidth]{cpu}
+%  \caption{\label{fig:cpu} Comparative cumulative CPU time for different refinement modes.}
+%  \end{centering}
+%\end{figure}
+%
+%\begin{figure}[!ht]
+%  \begin{centering}
+%  \includegraphics[width=\columnwidth]{dof}
+%  \caption{\label{fig:dof} Comparative NDOFs at each time step for 
+%  different refinement modes.}
+%  \end{centering}
+%\end{figure}
+%
+%Fig.~\ref{fig:cpu} shows the cumulative CPU time for different refinement 
+%modes at each time step --- the results were recorded on the same computer
+%for the CPU times to be comparable.
+%We see that HP\_ANISO\_H and HP\_ANISO require the most
+%resources. This can be understood from the fact that in case of these 
+%refinement modes the adaptivity algorithm has the largest number of 
+%candidates (see Section.~\ref{sec:model} and Fig.~\ref{fig:refinements})
+%from which a particular refinement can be chosen.
+%At the same time, HP\_ANISO\_P is the fastest compared to the other refinement modes.
+%This can be attributed to the finer inital mesh.
+%
+%Fig.~\ref{fig:dof} shows the NDOFs at each time step.
+%It can be seen that the HP\_ANISO results in the 
+%smallest problem size --- $N_{DOF} \approx 125$. 
+%All the other refinement modes result in a 
+%problem size of approximately ($N_{DOF} \approx 250$). Therefore
+%the HP\_ANISO is the most efficient in terms of memory consumption.
+%
+%As we have filtered out
+%two notable refinement modes for the given problem --- HP\_ANISO\_P because of the fast
+%calculation, and HP\_ANISO because of the small problem size. In the following
+%subsection, some optimizations to reduce the CPU time of
+%HP\_ANISO and reduce the NDOFs of HP\_ANISO\_P will be considered.
 
-Fig.~\ref{fig:dof} shows the NDOFs at each time step.
-It can be seen that the HP\_ANISO results in the 
-smallest problem size --- $N_{DOF} \approx 125$. 
-All the other refinement modes result in a 
-problem size of approximately ($N_{DOF} \approx 250$). Therefore
-the HP\_ANISO is the most efficient in terms of memory consumption.
-
-As we have filtered out
-two notable refinement modes for the given problem --- HP\_ANISO\_P because of the fast
-calculation, and HP\_ANISO because of the small problem size. In the following
-subsection, some optimizations to reduce the CPU time of
-HP\_ANISO and reduce the NDOFs of HP\_ANISO\_P will be considered.
-
-\subsection{Optimizations of HP\_ANISO and HP\_ANISO\_P refinement modes}
+\subsection{Optimization of the HP\_ANISO and HP\_ANISO\_P adaptivity modes}
 

### 2010-10-27 results.tex
Some changes

@@
 calculated with the HP\_ANISO refinement mode is shown
-in Figs.~\ref{fig:cphi-1} and \ref{fig:cphi-2}.
+in Figs.~\ref{fig:cphi-1}~and~\ref{fig:cphi-2}.
 
@@
   \begin{centering}
-  \includegraphics[width=.75\columnwidth]{cphi-1}
+  \includegraphics[width=\columnwidth]{cphi-1}
   \caption{\label{fig:cphi-1} Concentration $C$
@@
   \begin{centering}
-  \includegraphics[width=.75\columnwidth]{cphi-2}
+  \includegraphics[width=\columnwidth]{cphi-2}
   \caption{\label{fig:cphi-2} Concentration $C$
@@
 
+First of all, the low-order FEM and $hp$-FEM were compared.
 Comparison of single mesh H\_ANISO with p=1, single mesh H\_ANISO with p=2
@@
 
-\subsection{More general results}
+\subsection{HP\_ANISO adaptivity with non-uniform boundary conditions}
 \begin{figure}[!ht]

### 2010-10-28 results.tex
Results section improved

@@
 
-\newpage
+%\newpage
 
@@
 
-First of all, the low-order FEM and $hp$-FEM were compared.
-Comparison of single mesh H\_ANISO with p=1, single mesh H\_ANISO with p=2
-and single mesh HP\_ANISO should be added here to make the point that 
-hp-FEM is much better than low-order FEM. 
-Otherwise the reader does not know 
-why we are just using hp-FEM in the following. Or is there a reason 
-why you do not want to add this here --  long computing time for hp-FEM or something 
-else?
+First of all, the low-order FEM and $hp$-FEM were compared. A single mesh
+H\_ANISO with polynomial degrees $p=1$ and $p=2$ were compared to
+HP\_ANISO mode. The coarse initial mesh as shown in Fig.~\ref{fig:mesh}~(a)
+was used in the solutions.
+The results are shown in Figs.~\ref{fig:singlehhpdof} 
+and~\ref{fig:singlehhpcpu}.
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{singleh_hp_dof}
+  \caption{\label{fig:singlehhpdof} Number of degrees of freedom (DOF) as a function 
+  of physical time for single-mesh H\_ANISO (in case of
+  $p=1$ and $p=2$) and single-mesh HP\_ANISO.}
+  \end{centering}
+\end{figure}
+
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{singleh_hp_cpu}
+  \caption{\label{fig:singlehhpcpu} Cumulative CPU time as a function 
+  of physical time for single-mesh H\_ANISO (in case of $p=1$ and $p=2$)
+  and single mesh HP\_ANISO.}
+  \end{centering}
+\end{figure}
+
+\noindent
+It can be seen that $hp$-FEM results in the shorter computing 
+time and smaller number
+of degrees of freedom (DOF) than the low-order FEM. The same holds true
+for H\_ISO and HP\_ISO modes. In fact, in case of H\_ISO the relative error did not
+converge to the pre-set threshold value of $0.5\%$.
+Therefore, the $h$-FEM solutions will be omitted from the further comparisons.
+Instead, only $hp$-FEM solutions on the coarse mesh and $p$-FEM solutions
+on the fine mesh will be discussed. It must be also noted that the error
+converged to or below $0.5\%$ for all $p$-FEM and $hp$-FEM results, therefore
+the error graphs will not be presented.
 
@@
   and HP\_ANISO adaptivity modes. Note logarithmic scale on the vertical axis.}
-\vspace{-6mm}
+%\vspace{-6mm}
   \end{centering}
@@
 
-These result are in good agreement with Fig.~\ref{fig:cphi-2} -- in the vicinity
+These result are in good agreement with Fig.~\ref{fig:cphi-2} --- in the vicinity
 of the boundaries $\partial \Omega_1$ and $\partial\Omega_3$, the concentration gradient
@@
 
-\subsection{Optimization of the HP\_ANISO and HP\_ANISO\_P adaptivity modes}
+\subsection{Optimization of the HP\_ANISO adaptivity modes}
 

### 2010-10-28 results.tex
Results section almost re-done

@@
 We used two types of initial meshes --- a finer mesh shown 
-in Fig.~\ref{fig:mesh}~(c) was used for \emph{p}-adaptivity
+in Fig.~\ref{fig:mesh}~(b) was used for \emph{p}-adaptivity
 and a very coarse initial mesh shown in  Fig.~\ref{fig:mesh}~(a) was 
@@
   \begin{centering}
-  \includegraphics[width=.8\columnwidth]{mesh}
-  \caption{\label{fig:mesh} Initial coarse mesh (a),
-  	half refined mesh (b) and refined mesh (c). The coarse mesh (a)
-	and refined mesh (c) were used in the initial calculations, the latter one
-	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh (b) was
-	used later to optimize the \emph{hp}-adaptive refinement solutions.}
+  \includegraphics[width=.6\columnwidth]{mesh}
+  \caption{\label{fig:mesh} Initial coarse mesh (a)
+  	and refined mesh (b). The coarse mesh (a)
+	and refined mesh (b) were used in the initial calculations, the latter one
+	in case of \emph{p}-adaptivity (including HP\_ANISO\_P).}
   \end{centering}
@@
 \noindent
-It can be seen that $hp$-FEM results in the shorter computing 
+It can be seen that $hp$-FEM results in a shorter computing 
 time and smaller number
-of degrees of freedom (DOF) than the low-order FEM. The same holds true
+of DOF than the low-order FEM. The same holds true
 for H\_ISO and HP\_ISO modes. In fact, in case of H\_ISO the relative error did not
@@
 converged to or below $0.5\%$ for all $p$-FEM and $hp$-FEM results, therefore
-the error graphs will not be presented.
+the graphs of the error as a function of physical time will not be presented.
 
@@
 Running the simulation with different adaptivity modes 
-and meshes showed that the multi-mesh $hp$-FEM configuration resulted into
+and meshes showed that the multi-mesh $hp$-FEM configuration resulted in
 the smallest problems, shortest computing times, and better or the same error 
@@
 This is illustrated in Figs.~\ref{fig:singlemultidof} 
-and Fig.~\ref{fig:singlemulticpu}.
+and Fig.~\ref{fig:singlemulticpu}. Notice that the HP\_ISO with the single-mesh
+configuratio did not even converge in terms of number of degrees of freedom --- the
+adaptivity resulted in an unreasonable problem size and the calculation was
+not finished.
 
@@
   \includegraphics[width=\columnwidth]{singlemulti_dof}
-  \caption{\label{fig:singlemultidof} Number of degrees of freedom (DOF) as a function 
+  \caption{\label{fig:singlemultidof} Number of DOF as a function 
   of physical time for single-mesh and multi-mesh configurations with the HP\_ISO
@@
 
-%
-%\subsection{Quantitative analysis of the refinement modes}
-%
-%Based on the results in the previous subsection, H\_ANISO, HP\_ANISO,
-%and HP\_ANISO\_H from the \emph{hp/h}-adaptivity group and HP\_ANISO\_P
-%from \emph{p}-adaptivity group will be compared
-%in terms of NDOFs and cumulative CPU time. 
-%In all of the cases, the relative 
-%error at each time step remained below
-%the threshold which was set to $e_{th}=0.5\%$ between the coarse mesh
-%and fine mesh solutions, therefore the error-time plot will not be considered.
-%
-%\begin{figure}[!ht]
-%  \begin{centering}
-%  \includegraphics[width=\columnwidth]{cpu}
-%  \caption{\label{fig:cpu} Comparative cumulative CPU time for different refinement modes.}
-%  \end{centering}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%  \begin{centering}
-%  \includegraphics[width=\columnwidth]{dof}
-%  \caption{\label{fig:dof} Comparative NDOFs at each time step for 
-%  different refinement modes.}
-%  \end{centering}
-%\end{figure}
-%
-%Fig.~\ref{fig:cpu} shows the cumulative CPU time for different refinement 
-%modes at each time step --- the results were recorded on the same computer
-%for the CPU times to be comparable.
-%We see that HP\_ANISO\_H and HP\_ANISO require the most
-%resources. This can be understood from the fact that in case of these 
-%refinement modes the adaptivity algorithm has the largest number of 
-%candidates (see Section.~\ref{sec:model} and Fig.~\ref{fig:refinements})
-%from which a particular refinement can be chosen.
-%At the same time, HP\_ANISO\_P is the fastest compared to the other refinement modes.
-%This can be attributed to the finer inital mesh.
-%
-%Fig.~\ref{fig:dof} shows the NDOFs at each time step.
-%It can be seen that the HP\_ANISO results in the 
-%smallest problem size --- $N_{DOF} \approx 125$. 
-%All the other refinement modes result in a 
-%problem size of approximately ($N_{DOF} \approx 250$). Therefore
-%the HP\_ANISO is the most efficient in terms of memory consumption.
-%
-%As we have filtered out
-%two notable refinement modes for the given problem --- HP\_ANISO\_P because of the fast
-%calculation, and HP\_ANISO because of the small problem size. In the following
-%subsection, some optimizations to reduce the CPU time of
-%HP\_ANISO and reduce the NDOFs of HP\_ANISO\_P will be considered.
+HP\_ANISO also results in the fastest
+computing time among $hp$-adaptivity group whereas HP\_ANISO\_P
+results in the fastest overall computing time. This is due to the fact
+that HP\_ANISO\_P calculation is performed on the refined mesh. 
+Regardless, the HP\_ANISO adaptivity mode is the most suitable
+for the PNP problem due to the small size and relative fastness compared
+to the other adaptivity modes. A way to optimize the computing time
+of HP\_ANISO will be considered next.
 
-\subsection{Optimization of the HP\_ANISO adaptivity modes}
+\subsection{Time stpe control of HP\_ANISO adaptivity}
 
@@
   \begin{centering}
-  \includegraphics[width=\columnwidth]{refined_cpu}
-  \caption{\label{fig:refined-cpu} Cumulative CPU time for HP\_ANISO and HP\_ANISO\_P
-  with different initial meshes.}
+  \includegraphics[width=\columnwidth]{cphi_relerr}
+  \caption{\label{fig:cphirelerr} Relative difference $e_{C}^n$ and $e_{\phi}^n$.}
+  \end{centering}
+\end{figure}
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{timeadapt_dof}
+  \caption{\label{fig:timeadapt_dof} Number of DOF
+  as a function of physical time for HP\_ANISO with and without
+  time step adaptivity. The markers on the graphs indicate the
+  time steps.}
+  \end{centering}
+\end{figure}
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{timeadapt_cpu}
+  \caption{\label{fig:timeadapt_cpu} Cumulative CPU times
+  as a function of physical time for HP\_ANISO with and without
+  time step adaptivity. The markers on the graphs indicate the
+  time steps.}
   \end{centering}
@@
 
+To optimize the calculation time of HP\_ANISO, an adaptive time step control was employed.
+The classical PID controller was used~\cite{valli2002control,dubcova2010space}.
+Since $C$ and $\phi$ change differently in time as was demonstrated in Figs.~\ref{fig:cphi-1}
+and~\ref{fig:cphi-2}, the relative changes between the solutions at different
+time steps were monitored:
+\begin{eqnarray}
+  e_C^n & = & \frac{\lVert C^n-C^{n-1}\rVert}{\lVert C^n \rVert},\\
+  e_\phi^n & = & \frac{\lVert \phi^n-\phi^{n-1}\rVert}{\lVert \phi^n \rVert}.
+\end{eqnarray}
+The relative changes to control the time step was calculated as follows:
+\begin{equation}
+  e^n=\max\left\{ e_C^n,\ e_\phi^n \right\}.
+\end{equation}
+If $e^n < \delta$ where $\delta>0$ is a defined tolerance, then the time
+step for the next iteration is increased smoothly to
+\begin{equation}
+  \tau^{n+1}=\left( \frac{e^{n-1}}{e^n} \right)^{k_P}\ \left( \frac \delta e^n \right)^{k_l}\
+  \left[ \frac{\left( e^{n-1} \right)^2}{e^n e^{n-2}} \right]^{k_D} \tau^n,
+\end{equation}
+where parameters are from~\cite{valli2002control}:
+\begin{equation}
+  k_p=0.075,\quad k_l=0.175,\quad k_D=0.01.
+\end{equation}
+The tolerance $\delta$ was set to $\delta=0.25$ in the current optimization
+example. The calculated $e_C^n$ and $e_\phi^n$ are shown in Fig.~\ref{fig:cphirelerr}.
+The HP\_ANISO problem size and computing time with and without time step control
+are shown in Figs.~\ref{fig:timeadapt_dof} and~\ref{fig:timeadapt_cpu}. The reader
+can notice that the computing time was reduced approximately 3 times when the time
+step adaptivity was employed.
+
+\subsection{HP\_ANISO adaptivity with physically more realistic boundary conditions}
 \begin{figure}[!ht]
   \begin{centering}
-  \includegraphics[width=\columnwidth]{refined_dof}
-  \caption{\label{fig:refined-dof} NDOFs at each time step for
-  HP\_ANISO and HP\_ANISO\_P with different meshes.}
-  \end{centering}
-\end{figure}
-
-When it comes to a large domain or 3D modeling, the problem
-size becomes a very important factor. Namely, 3D full scale solutions tend to use
-a lot of memory. Therefore, we consider HP\_ANISO the most
-suitable refinement mode for the given problem. 
-Hence, some ways to optimize the HP\_ANISO model
-to improve the CPU time factor without significantly 
-compromising the NDOFs will be considered. 
-The desirable output would be HP\_ANISO problem size
-close to HP\_ANISO\_P CPU time. 
-One way to optimize the problem
-is to choose more refined initial mesh. Another way would be to change
-the refinement frequency during the solving process. Theoretically it 
-could result in a fewer adaptivity steps which are rather expensive in terms
-of CPU time. Recall that up to this point,
-the initial mesh was loaded in the beginning of each time step. 
-True, by employing the optimizations, one must know something about the problem
-and its solution beforehand. However, it could still be practial when solving a real problem
-in a large domain.
-
-The problem size and CPU time with HP\_ANISO
-and HP\_ANISO\_P adaptivities on more refined initial mesh (see Fig.~\ref{fig:mesh}~(c))
-compared to the coarse initial mesh (Fig.~\ref{fig:mesh}~(a)) and 
-HP\_ANISO\_P solution are shown in Fig.~\ref{fig:refined-cpu} and Fig.~\ref{fig:refined-dof}.
-By using initially more refined mesh, the problem solving time
-can be reduced in case of HP\_ANISO, at the same time, the problem size increases
-as the initial mesh is not necessarily the most optimal one.
-However, in this situation, HP\_ANISO\_P and HP\_ANISO perform equally well.
-
-\begin{figure}[!ht]
-  \begin{centering}
-  \includegraphics[width=\columnwidth]{unreffreq_dof}
-  \caption{\label{fig:unreffreq-dof} NDOFs at each time step for
-  HP\_ANISO and HP\_ANISO\_P with mesh unrefinement at each time step and at over each
-  	time step after first $0.5\ s$ physical solution time.}
-  \end{centering}
-\end{figure}
-The next proposed optimization involved changing the unrefinement frequency.
-It is known that the concentration gradient $\nabla C$ changes the most in the initial phase
-of the calculation, therefore, the unrefinement after each time step was performed
-until $t=0.5\ s$ (physical time). After that, the
-unrefinement was performed in $\Delta t = 0.10\ s$ interval.
-However, this optimization does not appear to result in a stable solution, 
-i.e. the problem size 
-does not remain steady, but starts to oscillate depending on the unrefinement
-frequency. This is shown in Fig.~\ref{fig:unreffreq-dof}.
-
-Therefore varying the unrefinement frequency will
-likely not result in desired results in real applications for given system of equation.
-At the same time, by varying the initial mesh size, optimal initial mesh could be found
-for both HP\_ANISO and HP\_ANISO\_P refinement modes.
-
-\subsection{HP\_ANISO adaptivity with non-uniform boundary conditions}
-\begin{figure}[!ht]
-  \begin{centering}
-  \includegraphics[width=.75\columnwidth]{cphiorders}
+  \includegraphics[width=\columnwidth]{cphiorders}
   \caption{\label{fig:cphi-orders} Solutions $C$ and $\phi$
@@
 
-Based on the results, cation concentration and voltage was calculated
-for different boundary conditions.
-For instance, when voltage is applied as follows
+In real physics calculations, the applied voltage on boundary $\partial\Omega_1$
+is not constant. This can be, for instance, due to the high resistance of
+the electrodes as explained in~\cite{pugal2009}.
+To see how the HP\_ANISO adaptivity works for such situations, the
+voltage on the boundary was applied as follows:
 \begin{equation}
-  \phi_{\Omega_1}=0.5\frac{x}{width_{\Omega_1}}+0.5,
+  \phi_{\Omega_1}\left( x \right)=0.5\left[V \right] \frac{x\left[ m \right ]}{\text{width}_{\Omega_1}\left[ m \right]}+0.5\left[ V \right],
 \end{equation}
-the concentration gradient $\nabla C$ and the voltage gradient $\nabla \phi$ are no
-longer effectively 1D.
+where $\text{width}_{\Omega_1}$ is the width of the boundary. The given boundary is effectively
+a linear incrase of the voltage from $\phi_{\Omega_1}\left(x = 0 \right)=0.5\ V$ to
+$\phi_{\Omega_1}\left(x=\text{width}_{\Omega_1}\right) = 1.0\ V$.
+Now the concentration gradient $\nabla C$ and the voltage gradient $\nabla \phi$ are no
+longer effectively in 1D.
+
 The calculated $C$ and $\phi$ in $\Omega$ and corresponding meshes and polynomial
-degrees of the elements are shown in Fig.~\ref{fig:cphi-orders}.
-HP\_ANISO refinement mode was used. Notice that the solution
-is different to the one in Fig.~\ref{fig:cphi} and the adapted mesh and the
-polynomial degrees are also more complicated than in Fig.~\ref{fig:poly}.
-It must be noted that in case of non uniform boundary conditions which
-results in 2D problem, refined initial mesh was more efficient to use.
+degrees of the elements at $t=0.7\ s$ are shown in Figs.~\ref{fig:cphi-orders}.
+Notice that the solution
+is different to the one in Fig.~\ref{fig:cphi-1}. The HP\_ANISO
+adaptivity algorithm has particularly increased the polynomial degree
+and refined the mesh near $\Omega_1$ where a sharp concentration
+peak exists (compare to Fig.~\ref{fig:poly}).
+At $t=3.0\ s$, the shape of the solution $C$ is similar to the one
+in Fig.~\ref{fig:cphi-2} and therefore the polynomial space and mesh gets adapted
+accordingly. This example clearly illustrates how 
+the solution of PNP with non-uniform
+boundary conditions is very dynamic in time, particularly for $C$,
+and how the HP\_ANISO time dependent adaptivity 
+finds an optimal mesh and polynomial space to adapt to the dynamics
+of the problem.

### 2010-10-28 conclusions.tex
Conclusions, model HP_ANISO_P and HP_ANISO_H briefly explained

--- 2010-10-09 conclusions.tex
@@
 was solved using \emph{hp}-finite element method with adaptive
-multimesh configuration. The weak form, residuals and
+multi-mesh configuration. The weak form, residuals and
 the Jacobian matrix of the system were explicitly derived
-and implemented in Hermes \emph{hp}-FEM adaptive solver.
+and implemented in Hermes \emph{hp}-FEM time dependent
+adaptive solver.
 The solution for Nernst-Planck-Poisson
@@
 very different field gradients in the space and time.
-Conventional finite element solvers do not provide the means 
-how to deal with such problems such that both the error of
+When using a conventional low order
+FEM, finding an optimal mesh for this
+type of problem such that both the error of
 the solution and problem size remain small throughout the
-time dependent solving process.
+time dependent solving process is difficult.
 
-It was shown that using time dependent adaptivity, multi-mesh
-configuration, and anisotropic \emph{hp} refinements, the problem
-size remains acceptably small throughout the solving process.
-Namely, hermes refinement modes HP\_ANISO and HP\_ANISO\_P
-resulted the smallest and fastest problem, respectively.
-At the same time, relative error of the solution was known.
+In the current work we showed that using the time dependent adaptivity, 
+multi-mesh configuration, and anisotropic \emph{hp} refinements, the problem
+size remains very small throughout the solving process while
+maintainging pre-set relative error of the solution.
+Namely, Hermes refinement mode HP\_ANISO 
+resulted in the smallest and fastest problem solution.
 Furthermore, using the multi-mesh configuration for the variables
@@
 We believe, and this
-is yet to be demonstrated, that this becomes especially
-important when dealing with 3D problems with a large physical
-domain.
+is yet to be demonstrated, that this is especially
+important when dealing with 3D problems in a large physical
+domain with non-uniform boundary conditions.

### 2010-10-29 results.tex
Conclusions, model HP_ANISO_P and HP_ANISO_H briefly explained
Some graphs improved, minor errors fixed

@@
 convergence compared to any single-mesh configuration.
-This is illustrated in Figs.~\ref{fig:singlemultidof} 
-and Fig.~\ref{fig:singlemulticpu}. Notice that the HP\_ISO with the single-mesh
-configuratio did not even converge in terms of number of degrees of freedom --- the
-adaptivity resulted in an unreasonable problem size and the calculation was
-not finished.
+This is illustrated for HP\_ANISO adaptivity mode in Figs.~\ref{fig:singlemultidof} 
+and Fig.~\ref{fig:singlemulticpu}. The same holds true for HP\_ISO mode.
 
@@
   \caption{\label{fig:singlemultidof} Number of DOF as a function 
-  of physical time for single-mesh and multi-mesh configurations with the HP\_ISO
-  and HP\_ANISO adaptivity modes. Note logarithmic scale on the vertical axis.}
+  of physical time for single-mesh and multi-mesh configurations with 
+  HP\_ANISO adaptivity mode.}
 %\vspace{-6mm}
@@
   \caption{\label{fig:singlemulticpu} Cumulative CPU time as a function 
-  of physical time for single-mesh and multi-mesh configurations with the HP\_ISO
-  and HP\_ANISO adaptivity modes. Note logarithmic scale on the vertical axis.}
+  of physical time for single-mesh and multi-mesh configurations with 
+  HP\_ANISO adaptivity mode.}
   \end{centering}
@@
 \begin{equation}
-  \tau^{n+1}=\left( \frac{e^{n-1}}{e^n} \right)^{k_P}\ \left( \frac \delta e^n \right)^{k_l}\
+  \tau^{n+1}=\left( \frac{e^{n-1}}{e^n} \right)^{k_P}\ \left( \frac{\delta}{e^n} \right)^{k_l}\
   \left[ \frac{\left( e^{n-1} \right)^2}{e^n e^{n-2}} \right]^{k_D} \tau^n,
@@
 can notice that the computing time was reduced approximately 3 times when the time
-step adaptivity was employed.
+step control was employed.
 

### 2010-11-03 model.tex
Results section almost re-done
Some type fixes

@@
 \emph{hp}-anisotropic-p (HP\_ANISO\_P), and \emph{hp}-anisotropic (HP\_ANISO).
-The eight adaptivity modes are summarized in Fig.~\ref{fig:candlist}.
+The eight adaptivity modes are summarized in Fig.~\ref{fig:candlist}. It must
+be noted that in case of HP\_ANISO\_H, only element size is adapted anisotropically
+whereas polynomial degree is adapted isotropically. The opposite holds true
+for HP\_ANISO\_P.
 
@@
 Hermes uses a pair of approximations with different orders of accuracy 
-to obtain this information: coarse mesh solution and fine mesh solution. 
+to obtain this information: coarse mesh solution and fine mesh solution~\cite{solin2010pde}. 
 The initial coarse mesh is read from the mesh file, and the initial 
@@
 The adaptivity algorithm is guided by the difference between the 
-reference solution and its low-order part~\cite{solin2010pde}.
+reference solution and its low-order part.
 Note that this approach to automatic adaptivity is PDE-independent

### 2011-01-12 results.tex
Some type fixes
Rev1: initial fixes

@@
 Figs.~\ref{fig:isoanisodof} and \ref{fig:isoanisocpu} show typical results 
-for the H\_ISO, H\_ANISO, HP\_ISO, HP\_ANISO adaptivity modes in terms 
+for the HP\_ISO, HP\_ANISO\_H,  HP\_ANISO adaptivity modes in terms 
 of DOF and cumulative CPU time.
@@
   \caption{\label{fig:isoanisodof} Number of DOF as a function of physical time for 
-  multi-mesh configurations with H\_ISO, H\_ANISO,
-  HP\_ISO, and HP\_ANISO adaptivity modes.}
+  multi-mesh configurations with HP\_ANISO,
+  HP\_ANISO\_H, and HP\_ISO adaptivity modes.}
   \end{centering}
@@
   \caption{\label{fig:isoanisocpu} Cumulative CPU time as a function of physical time 
-  for multi-mesh configurations with H\_ISO, H\_ANISO,
-  HP\_ISO, and HP\_ANISO adaptivity modes.}
+  for multi-mesh configurations with HP\_ANISO,
+  HP\_ANISO\_H, and HP\_ISO adaptivity modes.}
   \end{centering}
@@
 
-\subsection{Time stpe control of HP\_ANISO adaptivity}
+\subsection{Time step control of HP\_ANISO adaptivity}
 

### 2011-02-10 intro.tex
Dimensionless conversion... start

@@
 \begin{equation}
-  \frac{\partial C}{\partial t}+\nabla\cdot(-D\nabla C-z\mu FC\nabla\phi)=0.
+  \frac{\partial C}{\partial t}+\nabla\cdot(-D\nabla C-\mu FC\nabla\phi)=0.
   \label{eq:nernst-planck}
@@
 Here $C$ stands for the counter ion concentration, $D$ is diffusion, $\mu$ mobility,
-$F$ Faraday constant, $\phi$ voltage, and $z$ the charge number. We have neglected 
+$F$ Faraday constant, and $\phi$ voltage. We have neglected 
 the velocity of the species as in our case it can be assumed zero. 

### 2011-02-10 model.tex
Dimensionless conversion... start

@@
 \begin{equation}
-  -D \frac{\partial C}{\partial n} - z \mu F C \frac{\partial \phi} {\partial n} = 0.
+  -D \frac{\partial C}{\partial n} - \mu F C \frac{\partial \phi} {\partial n} = 0.
   \label{eq:nernst-planck-boundary}
@@
 
-% IF YOU WANT TO CITE THIS WORK< YOU HAVE TO SAY WHY WE ARE DOING 
-% THE DERIVATION AGAIN -- OTHERWISE IT IS CONTRAPRODUCTIVE. SO 
-% I COMMENTED THIS OUT.
-% I guess it can be left out as the work in SPIE is quite preliminary
-% and not that complete
-%An implicit version of the weak form of PNP was derived in~\cite{pugal2010spie}.
 To make our results easily reproducible, in the following we present the derivation 
@@
 vector that are used in actual computations.
-To simplify notation, we define
+To simplify notation, we use dimensionless formulation of Eqs.~\eqref{eq:nernst-planck}
+and~\eqref{eq:poisson}. The following new notations for the independent variables
+$x$, $y$, $t$ and for the dependent variables $C$ and $\phi$ are used~\cite{bazant2004diffuse}:
 \begin{equation}
-  K = z \mu F,\ \ \
-  L = \frac{F}{\varepsilon}.
-  \label{eq:KL}
+  X=\frac xL,\ \ \
+  Y=\frac yL,\ \ \
+  \tau=\frac{tD}{\lambda_D L},\ \ \
+  \varphi=\frac{\phi F}{RT},\ \ \
+  c=\frac C C_0.\label{eq:dimensionless}
 \end{equation}
-Eqs.~\eqref{eq:nernst-planck} and \eqref{eq:poisson} yield
+Here $\lambda_D$ is the Debye screening length and it is expressed as follows~\cite{bazant2004diffuse}:
+\begin{equation}
+  \lambda_D=\sqrt{\frac{\varepsilon R T}{2 F^2 C_0}}.\label{eq:debye}
+\end{equation}
+After inserting variables~\eqref{eq:dimensionless} into Eq.~\eqref{eq:nernst-planck} the Nernst-Planck
+equation and Poisson equation become:
 \begin{eqnarray}
-  \frac{\partial C}{\partial t}-D\nabla^2 C-K\nabla\cdot \left(C\nabla\phi\right)&=&0,\label{eq:nernst-planck-2}\\
-  -\nabla^2\phi-L\left(C-C_{0}\right)&=&0.\label{eq:poisson-2}
+  \frac{DC_0}{\lambda_D L}\frac{\partial c}{\partial \tau} + \frac 1L \nabla_d\cdot
+    \left(-\frac{DC_0}{L}\nabla_dc-c\frac{DC_0}{L}\nabla_d\varphi\right) &=& 0\label{eq:dim1}\\
+  - \frac{\varepsilon R T}{L^2F^2C_0}\nabla_d\varphi&=&c-1\label{eq:dim2},
+\end{eqnarray}
+where
+\begin{equation}
+  \nabla_d=\left(\frac{\partial}{\partial X},\ \frac{\partial}{\partial Y}\right).
+\end{equation}
+After simplifying Eqs.~\eqref{eq:dim1} and~\eqref{eq:dim2} and denoting
+\begin{equation}
+  \epsilon=\frac{\lambda_D}{L},
+\end{equation}
+the dimensionless form of the PNP system of equations is
+\begin{eqnarray}
+  \frac{\partial c}{\partial \tau} + \epsilon \nabla_d\cdot
+    \left(-\nabla_d c - c \nabla_d \varphi\right) &=&0,\label{eq:dimensionless-nernst-planck}\\
+  -2\epsilon^2\nabla_d\varphi&=&c-1\label{eq:dimensionless-poisson}.
 \end{eqnarray}
@@
 \begin{equation}
-  -D\frac{\partial C}{\partial n}-KC\frac{\partial\phi}{\partial n}=0.
-  \label{eq:nernst-planck-boundary-2}
+  -\frac{\partial c}{\partial n}-c\frac{\partial\varphi}{\partial n}=0.
+  \label{eq:dimensionless-nernst-planck-boundary}
 \end{equation}
-As the second derivatives of both $C$ and $\phi$ are present in the 
+As the second derivatives of both $c$ and $\varphi$ are present in the 
 equations, the appropriate function space for them is the Sobolev space 
@@
 $$
-In order to derive the weak form of the Nernst-Planck equation Eq.~\eqref{eq:nernst-planck-2},
-we first multiply it with a test function $v^C \in V$ and integrate over the domain~$\Omega$,
+In order to derive the weak form of the Nernst-Planck equation Eq.~\eqref{eq:dimensionless-nernst-planck},
+we first multiply it with a test function $v^c \in V$ and integrate over the domain~$\Omega$,
 \begin{equation}

### 2011-02-10 intro.tex
Non-dimensionalized equations, some minor fixes

@@
 the following). These equations are used to model charge transport in materials 
-that includes ionic migration, diffusion, and convection. The charge transport 
+that include ionic migration, diffusion, and convection. The charge transport 
 process is a key mechanism for electromechanical transduction.
@@
 region near the boundary. The computing power required for a full scale problem 
-is significant. This is why we are interested in exploring adaptive algorithms
+is significant~\cite{pugal2010spie3d}. This is why we are interested in exploring adaptive algorithms
 -- we hope to obtain meshes that are optimal in terms of calculation time and 

### 2011-02-10 model.tex
Non-dimensionalized equations, some minor fixes

@@
 \begin{equation}
-  X=\frac xL,\ \ \
-  Y=\frac yL,\ \ \
-  \tau=\frac{tD}{\lambda_D L},\ \ \
+  X=\frac xl,\ \ \
+  Y=\frac yl,\ \ \
+  \tau=\frac{tD}{\lambda_D l},\ \ \
   \varphi=\frac{\phi F}{RT},\ \ \
@@
 \begin{eqnarray}
-  \frac{DC_0}{\lambda_D L}\frac{\partial c}{\partial \tau} + \frac 1L \nabla_d\cdot
-    \left(-\frac{DC_0}{L}\nabla_dc-c\frac{DC_0}{L}\nabla_d\varphi\right) &=& 0\label{eq:dim1}\\
-  - \frac{\varepsilon R T}{L^2F^2C_0}\nabla_d\varphi&=&c-1\label{eq:dim2},
+  \frac{DC_0}{\lambda_D l}\frac{\partial c}{\partial \tau} + \frac 1L \nabla_d\cdot
+    \left(-\frac{DC_0}{l}\nabla_dc-c\frac{DC_0}{l}\nabla_d\varphi\right) &=& 0\label{eq:dim1}\\
+  - \frac{\varepsilon R T}{l^2F^2C_0}\nabla_d^2\varphi&=&c-1\label{eq:dim2},
 \end{eqnarray}
@@
 \begin{equation}
-  \epsilon=\frac{\lambda_D}{L},
+  \epsilon=\frac{\lambda_D}{l},
 \end{equation}
@@
 \begin{eqnarray}
-  \frac{\partial c}{\partial \tau} + \epsilon \nabla_d\cdot
-    \left(-\nabla_d c - c \nabla_d \varphi\right) &=&0,\label{eq:dimensionless-nernst-planck}\\
-  -2\epsilon^2\nabla_d\varphi&=&c-1\label{eq:dimensionless-poisson}.
+  \frac{\partial c}{\partial \tau}
+    -\epsilon\nabla_d^2 c - \epsilon \nabla_d \cdot \left( c\nabla_d \varphi\right)  &=&0,\label{eq:dimensionless-nernst-planck}\\
+  -2\epsilon^2\nabla_d^2\varphi&=&c-1\label{eq:dimensionless-poisson}.
 \end{eqnarray}
@@
 $V=H^1\left(\Omega\right)$ where 
-$$H^1\left(\Omega\right)=\left\{v\in L^2\left(\Omega\right);\ \nabla v \in \left[L^2\left(\Omega\right)\right]^2\right\}.
+$$H^1\left(\Omega\right)=\left\{v\in L^2\left(\Omega\right);\ \nabla_d v \in \left[L^2\left(\Omega\right)\right]^2\right\}.
 $$
@@
 \begin{equation}
-  \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}
-  -\int_{\Omega}D\nabla^2Cv^C d\mathbf{x}-\int_{\Omega}K\nabla C\cdot\nabla\phi v^C d\mathbf{x}
-   - \int_{\Omega}KC\nabla^2\phi v^C d\mathbf{x}=0.
+  \int_{\Omega}\frac{\partial c}{\partial \tau}v^c d\mathbf{x}-
+  \int_{\Omega}\epsilon\nabla_d^2cv^c d\mathbf{x}-\int_{\Omega}\epsilon\nabla_d c\cdot\nabla_d\varphi v^c d\mathbf{x}-
+  \int_{\Omega}\epsilon c\nabla_d^2\varphi v^c d\mathbf{x}=0.
   \label{eq:nernst-planck-weak1}
@@
 $$
- \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}+
-  D\int_{\Omega}\nabla C\cdot\nabla v^C d\mathbf{x}-
-  K\int_{\Omega}\nabla C \cdot \nabla \phi v^C d\mathbf{x}
+ \int_{\Omega}\frac{\partial c}{\partial \tau}v^c d\mathbf{x}+
+  \epsilon\int_{\Omega}\nabla_d c\cdot\nabla_d v^c d\mathbf{x}-
+  \epsilon\int_{\Omega}\nabla_d c\cdot\nabla_d\varphi v^c d\mathbf{x}
 $$
 \begin{equation}
-  + K\int_{\Omega}\nabla\left(Cv^C\right)\cdot \nabla \phi d\mathbf{x}
-  -D\int_{\partial\Omega}\frac{\partial C}{\partial n}v^C d\mathbf{S}-
-  \int_{\partial\Omega}K\frac{\partial\phi}{\partial n}Cv^C d\mathbf{S}=0.
+  + \epsilon\int_{\Omega}\nabla_d\left(cv^c\right)\cdot \nabla_d \varphi d\mathbf{x}
+  -\epsilon\int_{\partial\Omega}\frac{\partial c}{\partial n}v^c d\mathbf{S}-
+  \int_{\partial\Omega}\epsilon\frac{\partial\varphi}{\partial n}cv^c d\mathbf{S}=0.
   \label{eq:nernst-planck-weak2}
@@
 Expanding the nonlinear term and using the boundary condition 
-\eqref{eq:nernst-planck-boundary-2}, we have
+\eqref{eq:dimensionless-nernst-planck-boundary}, we have
 $$
-  \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}+
-  D\int_{\Omega}\nabla C \cdot \nabla v^C d\mathbf{x}-
-  K\int_{\Omega}\nabla C \cdot \nabla \phi v^C d\mathbf{x}
+  \int_{\Omega}\frac{\partial c}{\partial \tau}v^c d\mathbf{x}+
+  \epsilon\int_{\Omega}\nabla_d c\cdot\nabla_d v^c d\mathbf{x}-
+  \epsilon\int_{\Omega}\nabla_d c\cdot\nabla_d\varphi v^c d\mathbf{x}
 $$
 \begin{equation}
-  + K\int_{\Omega}\nabla \phi \cdot \nabla C v^C d\mathbf{x}+
-  K\int_{\Omega} C \left(\nabla\phi\cdot\nabla v^C\right) d\mathbf{x}=0.
+  + \epsilon\int_{\Omega}\nabla_d \varphi \cdot \nabla_d c v^c d\mathbf{x}+
+  \epsilon \int_{\Omega} c \left(\nabla_d\varphi\cdot\nabla_d v^c\right) d\mathbf{x}=0.
   \label{eq:nernst-planck-weak3}
 \end{equation}
-After the second and third terms cancel out, we obtain the final weak form of 
+After the third and fourth terms cancel out, we obtain the final weak form of 
 the Nernst-Planck equation
 \begin{equation}
-  \int_{\Omega}\frac{\partial C}{\partial t}v^C d\mathbf{x}+
-  D\int_{\Omega}\nabla C \cdot \nabla v^C d\mathbf{x}+
-  K\int_{\Omega} C \left(\nabla\phi\cdot\nabla v^C\right) d\mathbf{x}=0.
+  \int_{\Omega}\frac{\partial c}{\partial \tau}v^c d\mathbf{x}+
+  \epsilon\int_{\Omega}\nabla_d c\cdot\nabla_d v^c d\mathbf{x}+
+  \epsilon \int_{\Omega} c \left(\nabla_d\varphi\cdot\nabla_d v^c\right) d\mathbf{x}=0.
   \label{eq:nernst-planck-weak-final}
 \end{equation}
-Analogously we derive also the weak form of the Poisson equation (\ref{eq:poisson-2}),
+Analogously we derive also the weak form of the Poisson equation (\ref{eq:dimensionless-poisson}),
 \begin{equation}
-  -\int_{\Omega}\nabla^2\phi v^\phi d\mathbf{x}-\int_{\Omega}LCv^\phi d\mathbf{x}+
-  \int_{\Omega}LC_{0}v^\phi d\mathbf{x}=0.
+  -2\epsilon^2\int_{\Omega}\nabla_d^2\varphi v^\varphi d\mathbf{x}-\int_{\Omega}cv^\varphi d\mathbf{x}+
+  \int_{\Omega}v^\varphi d\mathbf{x}=0.
   \label{eq:poisson-weak1}
@@
 \begin{equation}
-  \int_{\Omega}\nabla\phi\cdot\nabla v^\phi d\mathbf{x}-\int_{\Omega}LCv^\phi d\mathbf{x}+
-  \int_{\Omega}LC_{0}v^\phi d\mathbf{x}=0.
+  -2\epsilon^2\int_{\Omega}\nabla_d\varphi\cdot\nabla_d v^\varphi d\mathbf{x}-\int_{\Omega}cv^\varphi d\mathbf{x}+
+  \int_{\Omega}v^\varphi d\mathbf{x}=0.
   \label{eq:poisson-weak-final}
@@
 method. The unknown solution components 
-$C^{n+1}$ and $\phi^{n+1}$ at the end of the time step are expressed 
-as linear combinations of finite element basis functions $v_k^{C}$ 
-and $v_k^{\phi}$ with unknown coefficients,
+$c^{n+1}$ and $\varphi^{n+1}$ at the end of the time step $\delta\tau$ are expressed 
+as linear combinations of finite element basis functions $v_k^{c}$ 
+and $v_k^{\varphi}$ with unknown coefficients,
 \begin{eqnarray}
-  C^{n+1} = C(Y^{n+1}) &=& \sum_{k=1}^{N^C} y_k^{C} v_k^{C}, \label{eq:cnotation}\\
-  \phi^{n+1} = \phi(Y^{n+1}) &=& \sum_{k=1}^{N^{\phi}} y_k^{\phi} v_k^{\phi}\label{eq:phinotation}.
+  c^{n+1} = c(Y^{n+1}) &=& \sum_{k=1}^{N^c} y_k^{c} v_k^{c}, \label{eq:cnotation}\\
+  \varphi^{n+1} = \varphi(Y^{n+1}) &=& \sum_{k=1}^{N^{\varphi}} y_k^{\varphi} v_k^{\varphi}\label{eq:phinotation}.
 \end{eqnarray}
-Here $Y^{n+1}$ is a coefficient vector of length $N^C + N^{\phi}$ comprising the unknown 
-solution coefficients $y_k^{C}$ and $y_k^{\phi}$ (in this order). We will also be 
-using $C^n = C(Y^n)$ and $\phi^n = \phi(Y^n)$ for the previous time step solutions.
+Here $Y^{n+1}$ is a coefficient vector of length $N^c + N^{\varphi}$ comprising the unknown 
+solution coefficients $y_k^{C}$ and $y_k^{\varphi}$ (in this order). We will also be 
+using $c^n = c(Y^n)$ and $\varphi^n = \varphi(Y^n)$ for the previous time step solutions.
 
@@
 Eq.~\eqref{eq:nernst-planck-weak-final} leads to the formula for the 
-first part $F^C$ of the residual vector $F$,
+first part $F^c$ of the residual vector $F$,
 \begin{eqnarray}
-  F_i^C\left(Y\right) & = & \int_{\Omega} \frac{C(Y)}{\tau}v_i^C d\mathbf{x} - 
-  \int_{\Omega} \frac{C^{n}}{\tau}v_i^C d\mathbf{x}\nonumber\\
-  &&+\frac 12 \left[D\int_{\Omega} \nabla C(Y) \cdot \nabla v_i^C d\mathbf{x}+ 
-  	D\int_{\Omega} \nabla C^{n} \cdot \nabla v_i^C d\mathbf{x}\right]\nonumber\\
-  &&+ \frac 12 \left[K\int_{\Omega}C(Y) \left(\nabla \phi(Y) \cdot \nabla v_i^C\right) d\mathbf{x}+
-  K\int_{\Omega}C^{n} \left(\nabla \phi^{n} \cdot \nabla v_i^C\right) d\mathbf{x}\right]\label{eq:Fc}
+  F_i^c\left(Y\right) & = & \int_{\Omega} \frac{c(Y)}{\delta\tau}v_i^c d\mathbf{x} - 
+  \int_{\Omega} \frac{c^{n}}{\delta\tau}v_i^c d\mathbf{x}\nonumber\\
+  &&+\frac 12 \epsilon \left[\int_{\Omega} \nabla_d c(Y) \cdot \nabla_d v_i^c d\mathbf{x}+ 
+  	\int_{\Omega} \nabla_d c^{n} \cdot \nabla_d v_i^c d\mathbf{x}\right.\nonumber\\
+  &&+ \left.\int_{\Omega}c(Y) \left(\nabla_d \varphi(Y) \cdot \nabla_d v_i^c\right) d\mathbf{x}+
+  \int_{\Omega}c^{n} \left(\nabla_d \varphi^{n} \cdot \nabla_d v_i^c\right) d\mathbf{x}\right]\label{eq:Fc}
 \end{eqnarray}
-where $i = 1, 2, \ldots, N^C$.
-Analogously, Eq.~\eqref{eq:poisson-weak-final} defines the second part $F^{\phi}$ 
+where $i = 1, 2, \ldots, N^c$.
+Analogously, Eq.~\eqref{eq:poisson-weak-final} defines the second part $F^{\varphi}$ 
 of the residual vector $F$,
 \begin{equation}
-  F_i^{\phi}\left(Y\right) = \int_{\Omega} \nabla \phi(Y) \cdot \nabla v_i^{\phi} d\mathbf{x} 
-  - \int_{\Omega} LC(Y)v_i^{\phi} d\mathbf{x} + \int_{\Omega} LC_0 v_i^{\phi} d\mathbf{x}
+  F_i^{\varphi}\left(Y\right) = -2\epsilon^2\int_{\Omega} \nabla_d \varphi(Y) \cdot \nabla_d v_i^{\varphi} d\mathbf{x} 
+  - \int_{\Omega} c(Y)v_i^{\varphi} d\mathbf{x} + \int_{\Omega} v_i^{\varphi} d\mathbf{x}
   \label{eq:Fphi}
 \end{equation}
-where $i = N^C + 1, N^C + 2, \ldots, N^C + N^{\phi}$. The nonlinear discrete problem 
+where $i = N^c + 1, N^c + 2, \ldots, N^c + N^{\varphi}$. The nonlinear discrete problem 
 that needs to be solved at the end of each time step thus has the form 
@@
 \begin{array}{cc}
-  \displaystyle \frac{\partial F_i^C}{\partial y_j^C} & \displaystyle \frac{\partial F_i^C}{\partial y_j^{\phi}} \\ 
-  \displaystyle \frac{\partial F_i^{\phi}}{\partial y_j^C} & \displaystyle \frac{\partial F_i^{\phi}}{\partial y_j^{\phi}}
+  \displaystyle \frac{\partial F_i^c}{\partial y_j^c} & \displaystyle \frac{\partial F_i^c}{\partial y_j^{\varphi}} \\ 
+  \displaystyle \frac{\partial F_i^{\varphi}}{\partial y_j^c} & \displaystyle \frac{\partial F_i^{\varphi}}{\partial y_j^{\varphi}}
 \end{array}
@@
 $$
-\frac{\partial C(Y)}{\partial y_j^C} = v_j^C, \ \ \ 
-\frac{\partial \nabla C(Y)}{\partial y_j^C} = \nabla v_j^C,\ \ \ \mbox{etc.}.
+\frac{\partial c(Y)}{\partial y_j^c} = v_j^c, \ \ \ 
+\frac{\partial \nabla_d c(Y)}{\partial y_j^c} = \nabla_d v_j^c,\ \ \ \mbox{etc.}.
 $$
@@
 \begin{eqnarray}
-  \frac{\partial F_i^C}{\partial y_j^C}(Y) &=& 
-  \int_{\Omega} \frac{1}{\tau} v_j^C v_i^C d\mathbf{x} + 
-  \frac 12 D\int_{\Omega} \nabla v_j^C \cdot \nabla v_i^C d\mathbf{x}
-  + \frac 12 K\int_{\Omega} v_j^C \left(\nabla \phi(Y) \cdot \nabla v_i^C\right) d\mathbf{x},\label{eq:dFcdyc}\\
-  \frac{\partial F_i^C}{\partial y_j^{\phi}}(Y) &=&
-  \frac 12 K \int_{\Omega} C(Y) \left(\nabla v_j^{\phi} \cdot \nabla v_i^C\right) d\mathbf{x},\\
-  \frac{\partial F_i^{\phi}}{\partial y_j^C}(Y) &=&
-  - \int_{\Omega} L v_j^C v_i^{\phi} d\mathbf{x},\\
-  \frac{\partial F_i^{\phi}}{\partial y_j^{\phi}}(Y) &=&
-  \int_{\Omega} \nabla v_j^{\phi} \cdot \nabla v_i^{\phi} d\mathbf{x}\label{eq:dFphidyphi}.
+  \frac{\partial F_i^c}{\partial y_j^c}(Y) &=& 
+  \int_{\Omega} \frac{1}{\delta\tau} v_j^c v_i^c d\mathbf{x} + 
+  \frac 12 \epsilon\left[\int_{\Omega} \nabla_d v_j^c \cdot \nabla_d v_i^c d\mathbf{x}
+  + \int_{\Omega} v_j^c \left(\nabla_d \varphi(Y) \cdot \nabla_d v_i^c\right) d\mathbf{x}\right],\label{eq:dFcdyc}\\
+  \frac{\partial F_i^c}{\partial y_j^{\varphi}}(Y) &=&
+  \frac 12 \epsilon \int_{\Omega} c(Y) \left(\nabla_d v_j^{\varphi} \cdot \nabla_d v_i^c\right) d\mathbf{x},\\
+  \frac{\partial F_i^{\varphi}}{\partial y_j^c}(Y) &=&
+  - \int_{\Omega} v_j^c v_i^{\varphi} d\mathbf{x},\\
+  \frac{\partial F_i^{\varphi}}{\partial y_j^{\varphi}}(Y) &=&
+  -2\epsilon^2\int_{\Omega} \nabla_d v_j^{\varphi} \cdot \nabla_d v_i^{\varphi} d\mathbf{x}\label{eq:dFphidyphi}.
 \end{eqnarray}
@@
 \begin{eqnarray*}
-J(Y^{n+1}_k) \delta Y^{n+1}_{k+1} &=& -F(Y^{n+1}_k), \\ 
-Y^{n+1}_{k+1} &=& Y^{n+1}_k + \delta Y^{n+1}_{k+1}, \\
+J(Y^{n+1}_k) \delta\tau Y^{n+1}_{k+1} &=& -F(Y^{n+1}_k), \\ 
+Y^{n+1}_{k+1} &=& Y^{n+1}_k + \delta\tau Y^{n+1}_{k+1}, \\
 k &:=& k+1
@@
 
+% Pavel
+% The reader might loose at this point the interest in reading further
+% since there is no motivation which favros a hp-FEM discretization over traditional
+% low order FEM. One sentence regarding computational performance
+% or a related comment might be useful...
 Automatic adaptivity in higher-order finite element methods (\emph{hp}-FEM) 
@@
 reference solution and its low-order part.
+% Pavel
+% A short explanation, how Hermes further deals with this difference without
+% going to much into details, might be interesting here...
 Note that this approach to automatic adaptivity is PDE-independent

### 2011-02-10 results.tex
Non-dimensionalized equations, some minor fixes

@@
 in terms of number of degrees of freedom (DOF) in each 
-time step.
+time step. The dimensional variables $x$, $y$, $t$, $C$,
+and $\phi$ are used to present the solutions.
 
@@
 \subsection{Comparison of single-mesh and multi-mesh $hp$-FEM}
-
+% David: Error convergence plots here.
 Running the simulation with different adaptivity modes 
@@
 convergence compared to any single-mesh configuration.
-This is illustrated for HP\_ANISO adaptivity mode in Figs.~\ref{fig:singlemultidof} 
-and Fig.~\ref{fig:singlemulticpu}. The same holds true for HP\_ISO mode.
+This is illustrated for HP\_ANISO adaptivity mode in Fig.~\ref{fig:singlemultidof}, Fig.~\ref{fig:singlemulticpu} and Fig.~\ref{fig:singlemultierror}.
+The same holds true for HP\_ISO mode.
 
@@
 
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{singlemulti_error}
+  \caption{\label{fig:singlemultierror} Relative solution error as a function 
+  of physical time for single-mesh and multi-mesh configurations with 
+  HP\_ANISO adaptivity mode.}
+  \end{centering}
+\end{figure}
 \noindent 
-Fig. \ref{fig:poly} shows higher-order meshes in the adaptive multimesh $hp$-FEM
+Fig. \ref{fig:poly} shows higher-order meshes in the adaptive multi-mesh $hp$-FEM
 computation for $C$ and $\phi$ at $t = 0.7$ s. Different 
@@
 
-These result are in good agreement with Fig.~\ref{fig:cphi-2} --- in the vicinity
+The result are in good agreement with Fig.~\ref{fig:cphi-2} --- in the vicinity
 of the boundaries $\partial \Omega_1$ and $\partial\Omega_3$, the concentration gradient
-is much greater than the voltage gradient. Therefore the multimesh $hp$-FEM adaptivity 
+is much greater than the voltage gradient. Therefore the multi-mesh $hp$-FEM adaptivity 
 algorithm has increased the maximum polynomial degree for the $C$-space to~7 while 
@@
 \begin{equation}
-  \tau^{n+1}=\left( \frac{e^{n-1}}{e^n} \right)^{k_P}\ \left( \frac{\delta}{e^n} \right)^{k_l}\
-  \left[ \frac{\left( e^{n-1} \right)^2}{e^n e^{n-2}} \right]^{k_D} \tau^n,
+  \delta\tau^{n+1}=\left( \frac{e^{n-1}}{e^n} \right)^{k_P}\ \left( \frac{\delta}{e^n} \right)^{k_l}\
+  \left[ \frac{\left( e^{n-1} \right)^2}{e^n e^{n-2}} \right]^{k_D} \delta\tau^n,
 \end{equation}
@@
 The tolerance $\delta$ was set to $\delta=0.25$ in the current optimization
-example. The calculated $e_C^n$ and $e_\phi^n$ are shown in Fig.~\ref{fig:cphirelerr}.
+example. At this point, the implementation does not support
+reducing the time step when $e^n\geq \delta$. The calculated $e_C^n$ and $e_\phi^n$ are shown in Fig.~\ref{fig:cphirelerr}.
 The HP\_ANISO problem size and computing time with and without time step control

### 2011-02-16 response.tex
Half of the graphs redone in nondimensional form

\documentclass[mathpazo]{cicp}

%\journal{Applied Mathematics and Computation}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsrefs}
%\usepackage{subfig}

\begin{document}

\title{Response to the reviewers of \emph{Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh hp-FEM}}

\author[Deivid Pugal et.~al.]{Deivid Pugal\affil{1}\comma\affil{4},
Pavel Solin\affil{2}\comma\affil{3}\comma\corrauth,
Kwang J. Kim\affil{1}, and Alvo Aabloo\affil{4}}

\address{\affilnum{1}\ Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.\\
\affilnum{2}\ Department of Mathematics and Statistics, University of Nevada, Reno, NV, U.S.A.\\
\affilnum{3}\ Institute of Thermomechanics, Prague, Czech Republic\\
\affilnum{4}\ Institute of Technology, Tartu University, Estonia}

\emails{{\tt david.pugal@gmail.com} (D.~Pugal), {\tt solin@unr.edu} (P.~Solin),
	{\tt kwangkim@unr.edu} (K.~Kim), {\tt alvo@ut.ee} (A.~Aabloo)}

\begin{abstract}
We are concerned with a model of ionic polymer-metal composite (IPMC) materials
that consists of a coupled system of the Poisson and Nernst-Planck equations, 
discretized by means of the finite element method (FEM). We show that due to the 
transient character of the problem it is efficient to use adaptive algorithms 
that are capable of changing the mesh dynamically in time. We also show 
that due to large qualitative and quantitative differences between the 
two solution components, it is efficient to approximate them on different 
meshes using a novel adaptive multimesh \emph{hp}-FEM. The study is 
accompanied with numerous computations and comparisons of the adaptive 
multimesh \emph{hp}-FEM with several other adaptive FEM algorithms. 
\end{abstract}

\maketitle

\section{Reviewer \#1}

\begin{enumerate}
\item \emph{The comparisons presented by the authors are interesting. One important aspect regarding the
Poisson-Nernst-Planck equations might be missing. A characteristic quantity of the system is the
dimensionless Debye length. It is well-known that the case of small Debye length’s provides severe
numerical difficulties. Hence, it would be very interesting to see how hp-FEM are able to handle
such cases. This might also lead to a different picture where possibly the electrostatic potential
needs more adaptivity than the concentration of counter ions in contrast to examples considered so
far.}

TODO
\item \emph{last sentence and Figure 1 Could the authors give a schematic picture presenting the electrostatic forces causing the deformation/bending of the IPMC?}

An explanation was added to the images in Figure 1.

\item \emph{3rd line "materials that includes"}

Fixed.

\item \emph{2nd paragraph, The computing power ... Are there references which elucidate this statement?}

A reference was added to a previous study where solving the PNP system in 3D was discussed.

\item \emph{1st sentence, ... principal difficulties ... As mentioned above, there are also other issues
known for the Poisson-Nernst-Planck system in the case of small Debye lenghts. Are the
authors sure that the motivation given in Section is numerical more demanding? If yes, are
there references available?}

TODO

\item \emph{eq. (3.5) It might be more appropriate to present the dimensionless formulation of the problem instead of introducing the physically less motivated notations (3.5). Such a formulation then
immediately provides the characteristic dimensionless parameter of the system, i.e. the Debye
length.}

This was very good point. The dimensionless form of the equations was derived. $\mathbf{All}$ the
results were recalculated and each graph and image in the Results section was redone.
Instead of using $C$
and $\phi$, the corresponding scaled variables $c$ and $\varphi$ are now used throughout the results section.

Furthermore, this time, all the results were calculated using adaptivity where the relative error
of the physical fields was considered separately.  Previously, absolute errors were compared
and the absolute error of the physical field $\phi$ was always very  much smaller compared to
$C$. Therefore no adaptivity of whatsoever was observed in case of $\phi$. The new results
(for instance, Figures~14 and~15) show that the mesh and the polynomial
space of physical field $\varphi$ is also adapted, however, not as much as in case of $c$.
We feel that this approach makes physically more sense.

\item \emph{3rd paragraph The reader might loose at this point the interest in reading further since there
is no motivation which favors a hp-FEM discretization over traditional low-order FEM. One
sentence regarding computational performance or a related comment might be useful ...}

TODO Pavel

\item \emph{2nd last sentence in 1st paragraph A short explanation, how Hermes further deals with this
difference without going to much into details, might be interesting here ...}

TODO Pavel

\item \emph{1st sentence in Sec. 5.2 Convergence plots of the error, which the authors mention, would be interesting...}

Figure 13 was added to show an example error convergence in case of HP\_ANISO.

\item \emph{last paragraph "The results"}

Fixed.

\item \emph{Section 5.4, eq. (5.4) What does Hermes do in the case $e^n\geq\delta$?}

Currently Hermes does not support the time step reduction. However, this is planned to be added
in future. A comment was also added below (5.5): \emph{At this point,
the implementation does not support reducing the time step when $e^n \geq \delta$.}

\end{enumerate}

\section{Reviewer \#2}

\begin{enumerate}

\item \emph{The authors have not given the initial values of $C$}

The initial value was added below Eq.~(1.1).

\item \emph{The authors have not given the size of time-step and the relation
of time step size and h; p or CFL stability condition.}

TODO Pavel?

\end{enumerate}
\end{document}

### 2011-02-16 intro.tex
Half of the graphs redone in nondimensional form

@@
 \end{equation}
-Here $C$ stands for the counter ion concentration, $D$ is diffusion, $\mu$ mobility,
+Here $C$ stands for the counter ion concentration with the initial value of $C_0$,
+$D$ is diffusion, $\mu$ mobility,
 $F$ Faraday constant, and $\phi$ voltage. We have neglected 

### 2011-02-16 motivation.tex
Half of the graphs redone in nondimensional form

@@
   $\varepsilon$&0.025&$\frac{F}{m}$&Electric permittivity\\
+  $l$&$200\times10^{-6}$&$m$& length scale\\
   \hline

### 2011-02-16 results.tex
Half of the graphs redone in nondimensional form

@@
 in terms of number of degrees of freedom (DOF) in each 
-time step. The dimensional variables $x$, $y$, $t$, $C$,
-and $\phi$ are used to present the solutions.
+time step. The scaled variables $c$
+and $\varphi$ and the unscaled time $t$ are used to present the solutions.
 
@@
 
-An example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
+An example of the solution at $t=0.1\ s$ and $t=3.0\ s$ 
 calculated with the HP\_ANISO refinement mode is shown
@@
   \includegraphics[width=\columnwidth]{cphi-1}
-  \caption{\label{fig:cphi-1} Concentration $C$
-  and voltage $\phi$ at $t=0.7\ s$.}
+  \caption{\label{fig:cphi-1} Scaled concentration $c$
+  and voltage $\varphi$ at $t=0.1\ s$.}
   \end{centering}
@@
   \includegraphics[width=\columnwidth]{cphi-2}
-  \caption{\label{fig:cphi-2} Concentration $C$
-  and voltage $\phi$ at $t=3.0\ s$.}
+  \caption{\label{fig:cphi-2} Scaled concentration $c$
+  and voltage $\varphi$ at $t=3.0\ s$.}
   \end{centering}
@@
 
-The reader can see that at $t=0.7\ s$ some ionic migration has already 
+The reader can see that at $t=0.1\ s$ some ionic migration has already 
 taken place and large concentration gradients near the boundaries $\partial\Omega_1$ 
 and $\partial\Omega_3$ have formed. The figures also show that the meshes 
-at $t=0.7\ s$ and $t=3.0\ s$ are different.
+at $t=0.1\ s$ and $t=3.0\ s$ are different.
 
@@
 Instead, only $hp$-FEM solutions on the coarse mesh and $p$-FEM solutions
-on the fine mesh will be discussed. It must be also noted that the error
-converged to or below $0.5\%$ for all $p$-FEM and $hp$-FEM results, therefore
-the graphs of the error as a function of physical time will not be presented.
+on the fine mesh will be discussed.
 
@@
 and meshes showed that the multi-mesh $hp$-FEM configuration resulted in
-the smallest problems, shortest computing times, and better or the same error 
-convergence compared to any single-mesh configuration.
-This is illustrated for HP\_ANISO adaptivity mode in Fig.~\ref{fig:singlemultidof}, Fig.~\ref{fig:singlemulticpu} and Fig.~\ref{fig:singlemultierror}.
-The same holds true for HP\_ISO mode.
+the smallest problems and similar error 
+convergence compared to any single-mesh configuration. However,
+multi-mesh problems generally resulted in longer computing times. This is a known
+shortcoming of Hermes at this point and it is due to the fact that
+multi-mesh uses the union mesh (see Section~\ref{sec:hermes}) where 
+the numerical integration of high order is done on very small elements.
+The problem size and computing time are illustrated for HP\_ANISO adaptivity mode in Fig.~\ref{fig:singlemultidof} and Fig.~\ref{fig:singlemulticpu}.
+The same holds true for HP\_ISO mode.  It must be also noted that the error
+converged to or below $0.5\%$ for all $p$-FEM and $hp$-FEM results. This is illustrated in
+Fig.~\ref{fig:singlemultierror} for $hp$-FEM single and multi-mesh configurations.
 
@@
 \noindent 
-Fig. \ref{fig:poly} shows higher-order meshes in the adaptive multi-mesh $hp$-FEM
-computation for $C$ and $\phi$ at $t = 0.7$ s. Different 
+Figs.~\ref{fig:poly} and~\ref{fig:poly2} show higher-order meshes in the adaptive multi-mesh $hp$-FEM
+computation for $c$ and $\varphi$ at $t = 0.1$~s and $t=3.0$~s, respectively. Different 
 colors mean different polynomial degrees. A diagonal pattern inside an element 
@@
   \caption{\label{fig:poly} Higher-order FEM mesh for 
-  $C$ and $\phi$ at $t=0.7\ s$. }
+  $c$ and $\varphi$ at $t=0.1\ s$. }
   \end{centering}
@@
 
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=.75\columnwidth]{poly2}
+  \caption{\label{fig:poly2} Higher-order FEM mesh for 
+  $c$ and $\varphi$ at $t=3.0\ s$. }
+  \end{centering}
+\end{figure}
+\noindent
 The result are in good agreement with Fig.~\ref{fig:cphi-2} --- in the vicinity
 of the boundaries $\partial \Omega_1$ and $\partial\Omega_3$, the concentration gradient
-is much greater than the voltage gradient. Therefore the multi-mesh $hp$-FEM adaptivity 
-algorithm has increased the maximum polynomial degree for the $C$-space to~7 while 
-the maximum polynomial degree for the $\phi$-space is~2. One can also see that the mesh 
-is significantly more refined for $C$.
+is much greater than the voltage gradient. Therefore at $t=0.1$~s, 
+the multi-mesh $hp$-FEM adaptivity 
+algorithm has increased the maximum polynomial degree for the $c$-space to~6 while 
+the maximum polynomial degree for the $\varphi$-space is~4. The meshes are not
+that different in the beginning of the calculation. However, one can also see that the mesh 
+refinement for $c$ at $t=3.0$~s is notably different compared to $\varphi$. For instance,
+the highest polynomial degree for $c$-space is~8 whereas for $\varphi$-space is~4.
 Since these results are representative for all adaptivity modes, only multi-mesh 

### 2011-02-16 conclusions.tex
All graphs updated

@@
 size remains very small throughout the solving process while
-maintainging pre-set relative error of the solution.
+maintaining a pre-set relative error of the solution.
 Namely, Hermes refinement mode HP\_ANISO 
 resulted in the smallest and fastest problem solution.
-Furthermore, using the multi-mesh configuration for the variables
-$C$ and $\phi$ was justified --- the adaptivity algorithm
-did not refine the mesh of $\phi$ nor did increase the
-polynomial degree throughout the adaptivity process. However,
-the mesh was significantly refined for $C$ and also the
+Furthermore, using the multi-mesh configuration for the physical fields
+$c$ and $\varphi$ --- scaled variables for $C$ and $\phi$, respectively ---
+was justified. The adaptivity algorithm
+refined the meshes of $\varphi$  and $c$ and increased the
+polynomial degrees of the corresponding spaces differently.
+The mesh was significantly refined for $c$ and also the
 maximum polynomial degree was varied in the range of
-$2\ldots 9$. So it is efficient to use multi-mesh in terms of
+$2\ldots 9$ whereas for $\varphi$, the maximum polynomial degree
+remained lower. So it is efficient to use multi-mesh in terms of
 the number of degrees of freedom.

### 2011-02-16 results.tex
All graphs updated

@@
 for H\_ISO and HP\_ISO modes. In fact, in case of H\_ISO the relative error did not
-converge to the pre-set threshold value of $0.5\%$.
+converge to the pre-set threshold value of $0.5\%$ within acceptable range 
+of degrees of freedom of $nDOF_{threshold}=5000$.
 Therefore, the $h$-FEM solutions will be omitted from the further comparisons.
@@
 The same holds true for HP\_ISO mode.  It must be also noted that the error
-converged to or below $0.5\%$ for all $p$-FEM and $hp$-FEM results. This is illustrated in
-Fig.~\ref{fig:singlemultierror} for $hp$-FEM single and multi-mesh configurations.
+converged to or below $0.5\%$ for all $p$-FEM and anisotropic $hp$-FEM results.
 
@@
 
-\begin{figure}[!ht]
-  \begin{centering}
-  \includegraphics[width=\columnwidth]{singlemulti_error}
-  \caption{\label{fig:singlemultierror} Relative solution error as a function 
-  of physical time for single-mesh and multi-mesh configurations with 
-  HP\_ANISO adaptivity mode.}
-  \end{centering}
-\end{figure}
 \noindent 
@@
 for the HP\_ISO, HP\_ANISO\_H,  HP\_ANISO adaptivity modes in terms 
-of DOF and cumulative CPU time.
+of DOF and cumulative CPU time. Fig.~\ref{fig:isoanisoerror} shows corresponding
+error convergence. It can be seen that HP\_ISO is notoriously inefficient as the
+error does not converge within the limited number of degrees of freedom 
+of $nDOF_{threshold}=5000$ and computing time is very large. Due to that fact,
+the calculation of HP\_ISO was canceled before $t=3.0$~s.
 
@@
   multi-mesh configurations with HP\_ANISO,
-  HP\_ANISO\_H, and HP\_ISO adaptivity modes.}
+  HP\_ANISO\_H, and HP\_ISO adaptivity modes (log~$y$ scale).}
   \end{centering}
@@
   \caption{\label{fig:isoanisocpu} Cumulative CPU time as a function of physical time 
+  for multi-mesh configurations with HP\_ANISO,
+  HP\_ANISO\_H, and HP\_ISO adaptivity modes (log~$y$ scale).}
+  \end{centering}
+\end{figure}
+
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{isoaniso_error}
+  \caption{\label{fig:isoanisoerror} Relative solution error as a function of physical time 
   for multi-mesh configurations with HP\_ANISO,
@@
 the isotropic ones. In particular, HP\_ANISO results into the smallest problem size. 
-In the \emph{p}-adaptivity group, HP\_ANISO\_P leads to a small problem size
-consistently in each time step, whereas P\_ISO and P\_ANISO yield large problems
-during the first few time steps.
+In the \emph{p}-adaptivity group, HP\_ANISO\_P and P\_ANISO lead to a small problem size
+consistently in each time step, whereas P\_ISO yields large problems
+during the first time steps.
 
@@
   \includegraphics[width=\columnwidth]{cphi_relerr}
-  \caption{\label{fig:cphirelerr} Relative difference $e_{C}^n$ and $e_{\phi}^n$.}
+  \caption{\label{fig:cphirelerr} Relative difference $e_{c}^n$ and $e_{\varphi}^n$.}
   \end{centering}
@@
 The classical PID controller was used~\cite{valli2002control,dubcova2010space}.
-Since $C$ and $\phi$ change differently in time as was demonstrated in Figs.~\ref{fig:cphi-1}
+Since $c$ and $\varphi$ change differently in time as was demonstrated in Figs.~\ref{fig:cphi-1}
 and~\ref{fig:cphi-2}, the relative changes between the solutions at different
@@
 \begin{eqnarray}
-  e_C^n & = & \frac{\lVert C^n-C^{n-1}\rVert}{\lVert C^n \rVert},\\
-  e_\phi^n & = & \frac{\lVert \phi^n-\phi^{n-1}\rVert}{\lVert \phi^n \rVert}.
+  e_c^n & = & \frac{\lVert c^n-c^{n-1}\rVert}{\lVert c^n \rVert},\\
+  e_\varphi^n & = & \frac{\lVert \varphi^n-\varphi^{n-1}\rVert}{\lVert \varphi^n \rVert}.
 \end{eqnarray}
@@
 \begin{equation}
-  e^n=\max\left\{ e_C^n,\ e_\phi^n \right\}.
+  e^n=\max\left\{ e_c^n,\ e_\varphi^n \right\}.
 \end{equation}
@@
 example. At this point, the implementation does not support
-reducing the time step when $e^n\geq \delta$. The calculated $e_C^n$ and $e_\phi^n$ are shown in Fig.~\ref{fig:cphirelerr}.
+reducing the time step when $e^n\geq \delta$. The calculated $e_c^n$ and $e_\varphi^n$ are shown in Fig.~\ref{fig:cphirelerr}.
 The HP\_ANISO problem size and computing time with and without time step control
 are shown in Figs.~\ref{fig:timeadapt_dof} and~\ref{fig:timeadapt_cpu}. The reader
-can notice that the computing time was reduced approximately 3 times when the time
+can notice that the computing time was reduced more than two times when the time
 step control was employed.
@@
   \includegraphics[width=\columnwidth]{cphiorders}
-  \caption{\label{fig:cphi-orders} Solutions $C$ and $\phi$
+  \caption{\label{fig:cphi-orders} Solutions $c$ and $\varphi$
   and corresponding polynomial degrees of the elements at
-  $t=0.7\ s$. HP\_ANISO refinement mode was used. The height
+  $t=0.1\ s$. HP\_ANISO refinement mode was used. The height
   in the solution graphs indicates the value.}
@@
 $\phi_{\Omega_1}\left(x=\text{width}_{\Omega_1}\right) = 1.0\ V$.
-Now the concentration gradient $\nabla C$ and the voltage gradient $\nabla \phi$ are no
+Now the concentration gradient $\nabla c$ and the voltage gradient $\nabla \varphi$ are no
 longer effectively in 1D.
 
-The calculated $C$ and $\phi$ in $\Omega$ and corresponding meshes and polynomial
-degrees of the elements at $t=0.7\ s$ are shown in Figs.~\ref{fig:cphi-orders}.
+The calculated scaled values $c$ and $\varphi$ in $\Omega$ and corresponding meshes and polynomial
+degrees of the elements at $t=0.1\ s$ are shown in Fig.~\ref{fig:cphi-orders}.
 Notice that the solution
@@
 peak exists (compare to Fig.~\ref{fig:poly}).
-At $t=3.0\ s$, the shape of the solution $C$ is similar to the one
+At $t=3.0\ s$, the shape of the solutions $c$ and $\varphi$ are similar to the one
 in Fig.~\ref{fig:cphi-2} and therefore the polynomial space and mesh gets adapted
@@
 the solution of PNP with non-uniform
-boundary conditions is very dynamic in time, particularly for $C$,
+boundary conditions is very dynamic in time
 and how the HP\_ANISO time dependent adaptivity 

### 2011-02-17 results.tex
Length scale study beginning...

@@
 of the problem.
+
+\subsection{Length scale study}
+
+Debye's length $\lambda_D$ is commonly used to estimate the screening length in electrolyte
+solutions. In the given PNP model, it serves as well as an estimation of the boundary layer thickness
+--- thickness of the layer in the vicinity of the boundaries $\partial\Omega_1$ 
+and $\partial\Omega_2$  where $c \neq 1$.
+The Debye's length in all the previous simulations was determined by the constants in
+Table~\ref{Table:used-constants}: $\lambda_D=XXX$. It is known that computation gets increasingly
+difficult with reducing the value of $\lambda_D$.
+It was our interest to see how small length scales can Hermes HP\_ANISO automatic
+adaptivity handle. The parameter $\varepsilon$ was varied as follows:
+$$\varepsilon_n=\varepsilon\times 0.5^n$ where $\varepsilon$ is taken from Table~\ref{Table:used-constants}.

### 2011-02-17 results.tex
Length scale study beginning, an error fixed

@@
 adaptivity handle. The parameter $\varepsilon$ was varied as follows:
-$$\varepsilon_n=\varepsilon\times 0.5^n$ where $\varepsilon$ is taken from Table~\ref{Table:used-constants}.
+$$\varepsilon_n=\varepsilon\times 0.5^n,$$ where $\varepsilon$ is taken from Table~\ref{Table:used-constants}.

### 2011-02-18 results.tex
Length scale study

--- 2011-02-16 results.tex
@@
 and $\varphi$ and the unscaled time $t$ are used to present the solutions.
+The simulations were performed with physical time step of $0.05$~s and
+the final time of $3.0$~s was chosen as it is close to the time
+scaling constant~$\tau$.
 
@@
 of the problem.
+
+\subsection{Length scale study}
+
+The Debye length $\lambda_D$ is the screening length in the electrolyte
+solutions. Its numerical value shows the
+thickness of the layer in the vicinity of the boundaries $\partial\Omega_1$ 
+and $\partial\Omega_2$  where $c \neq 1$.
+In all the previous simulations, the Debye screening length was determined by  the constants in
+Table~\ref{Table:used-constants} and Eq.~\ref{eq:debye}: $\lambda_D=XXX$. It is known that computation gets increasingly
+difficult when reducing the value of $\lambda_D$.
+It was our interest to see how small screening lengths can Hermes HP\_ANISO automatic
+adaptivity handle. The parameter $\varepsilon$ was varied as follows:
+$$\varepsilon_n=\varepsilon\times 0.5^n,$$ where $\varepsilon$ is taken from Table~\ref{Table:used-constants}. The simulations were run for each $\varepsilon_n$ and corresponding $\lambda_D$ value
+and maximum number of degrees of freedom and cumulative CPU time were recorded.
+The simulation time $t$ for each $\lambda_D$ was chosen to be $\tau$ --- the
+characteristic time scale --- and each simulation
+was divided equally into fifteen time steps. No PID controller was used.

### 2011-02-19 results.tex
Results section improved

@@
 was divided equally into fifteen time steps. No PID controller was used.
+Fig.~XXX shows the maximum number of degrees of freedom during calculation
+as a function of the Debye length and Fig.~XXX shows cumulative CPU time as a function
+of the Debye length. The simulations up to XXX m screening length were carried out on
+the initial coarse mesh. However, from $\lambda_D > XXX$ the finer initial mesh had to
+be used so the existence of the large gradients of the
+physical fields $c$ and $\varphi$ near the boundaries could be captured in the first place.
+The fine mesh allowed simulations with the Debye length down to $XXX$~m. The calculated
+$c$ and $\varphi$ at $t=\tau$ for $\lambda_D=XXX$ are shown in Fig.~XXX.
+It appears that when using even finer initial mesh and higher initial polynomial degrees, even
+smaller Debye lengths could be used when necessary.

### 2011-02-21 response.tex
All graphs updated
Length scale study completed

@@
 
-TODO
+Section 5.6 was added with a length scale study.
+
 \item \emph{last sentence and Figure 1 Could the authors give a schematic picture presenting the electrostatic forces causing the deformation/bending of the IPMC?}
@@
 
-TODO
+In some practical cases such as in case of modeling the Ionic Polymer Metal Composites,
+often the values of diffusion constant $D$ and dielectric permittivity $\varepsilon$ are such
+that the gradients of $\varphi$ do not become significantly high in a studied time scale, however,
+the gradients of $c$ do. This is one reason why it is hard to find an optimal mesh, especially
+in case of a 3D domain.
 
@@
 
-Figure 13 was added to show an example error convergence in case of HP\_ANISO.
+Figure 17 shows an example error convergence in case of HP\_ANISO, HP\_ANISO\_H, and HP\_ISO.
 

### 2011-02-21 results.tex
Length scale study completed

--- 2011-02-18 results.tex
@@
   \begin{centering}
-  \includegraphics[width=.6\columnwidth]{mesh}
-  \caption{\label{fig:mesh} Initial coarse mesh (a)
-  	and refined mesh (b). The coarse mesh (a)
+  \includegraphics[width=.9\columnwidth]{mesh}
+  \caption{\label{fig:mesh} Initial coarse mesh (a),
+  	refined mesh (b), and symmetrically refined mesh for length scale study (c). 
+	The coarse mesh (a)
 	and refined mesh (b) were used in the initial calculations, the latter one
@@
 
-\subsection{Length scale study}
+\subsection{Length scale analysis}
 
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{debye_dof}
+  \caption{\label{fig:debye_dof} Problem size depending on the
+	Debye length. Initially the coarse mesh (shown in Fig.~\ref{fig:mesh}~(a))
+	was used. It was necessary to use the fine mesh (see Fig.~\ref{fig:mesh}~(c)) 
+	for smaller $\lambda_D$ values.}
+  \end{centering}
+\end{figure}
+
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{debye_cpu}
+  \caption{\label{fig:debye_cpu} CPU time depending on the
+	Debye length. Initially the coarse mesh (shown in Fig.~\ref{fig:mesh}~(a))
+	was used. It was necessary to use the fine mesh (see Fig.~\ref{fig:mesh}~(c)) 
+	for smaller $\lambda_D$ values.}
+  \end{centering}
+\end{figure}
 The Debye length $\lambda_D$ is the screening length in the electrolyte
 solutions. Its numerical value shows the
-thickness of the layer in the vicinity of the boundaries $\partial\Omega_1$ 
-and $\partial\Omega_2$  where $c \neq 1$.
+thickness of the charged layer in the vicinity of the boundaries $\partial\Omega_1$ 
+and $\partial\Omega_2$.
 In all the previous simulations, the Debye screening length was determined by  the constants in
-Table~\ref{Table:used-constants} and Eq.~\ref{eq:debye}: $\lambda_D=XXX$. It is known that computation gets increasingly
+Table~\ref{Table:used-constants} and Eq.~\ref{eq:debye}: $\lambda_D=1.7\ \mu m$. It is known that computation gets increasingly
 difficult when reducing the value of $\lambda_D$.
@@
 characteristic time scale --- and each simulation
-was divided equally into fifteen time steps. No PID controller was used.
+was divided equally into fifteen time steps. The PID controller was not used.
+Fig.~\ref{fig:debye_dof} shows the maximum and average number of degrees of 
+freedom during calculation
+as a function of the Debye length and Fig.~\ref{fig:debye_cpu} shows cumulative CPU time as a function
+of the Debye length. The simulations up to $0.52\ nm$
+screening length were carried out on
+the initial coarse mesh. However, from $\lambda_D > 0.52\ nm$, the finer initial mesh had to
+be used so the existence of the large gradients of the
+physical fields $c$ and $\varphi$ near the boundaries could be captured in the first place.
+\begin{figure}[!ht]
+  \begin{centering}
+  \includegraphics[width=\columnwidth]{cphitau}
+  \caption{\label{fig:cphitau} Calculated fields $c$ and $\varphi$ at $t=\tau=0.81\ ms$
+	for $\lambda_D=0.4\ nm$.}
+  \end{centering}
+\end{figure}
+\noindent
+The fine mesh allowed simulations with the Debye length down to $0.40\ nm$~m. The calculated
+$c$ and $\varphi$ at $t=\tau$ for $\lambda_D=0.40\ nm$ are shown in Fig.~\ref{fig:cphitau}.
+It appears that when using even finer initial mesh and higher initial polynomial degrees, even
+smaller Debye lengths could be used when necessary. The polynomial space of $c$ had
+consistently higher maximum polynomial degree than that of $\varphi$, however, the difference
+was less noticeable for smaller Debye lengths.

### 2011-02-24 response.tex
Changes by Pavel.

@@
 
+\pagestyle{empty}
+
 \begin{document}
 
-\title{Response to the reviewers of \emph{Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh hp-FEM}}
+%\title{Response to the reviewers of \emph{Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh hp-FEM}}
 
-\author[Deivid Pugal et.~al.]{Deivid Pugal\affil{1}\comma\affil{4},
-Pavel Solin\affil{2}\comma\affil{3}\comma\corrauth,
-Kwang J. Kim\affil{1}, and Alvo Aabloo\affil{4}}
+\begin{center}
+{\huge \bf Response to the Referees}
+\end{center}
 
-\address{\affilnum{1}\ Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.\\
-\affilnum{2}\ Department of Mathematics and Statistics, University of Nevada, Reno, NV, U.S.A.\\
-\affilnum{3}\ Institute of Thermomechanics, Prague, Czech Republic\\
-\affilnum{4}\ Institute of Technology, Tartu University, Estonia}
+%\author[Deivid Pugal et.~al.]{Deivid Pugal\affil{1}\comma\affil{4},
+%Pavel Solin\affil{2}\comma\affil{3}\comma\corrauth,
+%Kwang J. Kim\affil{1}, and Alvo Aabloo\affil{4}}
 
-\emails{{\tt david.pugal@gmail.com} (D.~Pugal), {\tt solin@unr.edu} (P.~Solin),
-	{\tt kwangkim@unr.edu} (K.~Kim), {\tt alvo@ut.ee} (A.~Aabloo)}
+%\address{\affilnum{1}\ Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.\\
+%\affilnum{2}\ Department of Mathematics and Statistics, University of Nevada, Reno, NV, U.S.A.\\
+%\affilnum{3}\ Institute of Thermomechanics, Prague, Czech Republic\\
+%\affilnum{4}\ Institute of Technology, Tartu University, Estonia}
 
-\begin{abstract}
-We are concerned with a model of ionic polymer-metal composite (IPMC) materials
-that consists of a coupled system of the Poisson and Nernst-Planck equations, 
-discretized by means of the finite element method (FEM). We show that due to the 
-transient character of the problem it is efficient to use adaptive algorithms 
-that are capable of changing the mesh dynamically in time. We also show 
-that due to large qualitative and quantitative differences between the 
-two solution components, it is efficient to approximate them on different 
-meshes using a novel adaptive multimesh \emph{hp}-FEM. The study is 
-accompanied with numerous computations and comparisons of the adaptive 
-multimesh \emph{hp}-FEM with several other adaptive FEM algorithms. 
-\end{abstract}
+%\emails{{\tt david.pugal@gmail.com} (D.~Pugal), {\tt solin@unr.edu} (P.~Solin),
+%	{\tt kwangkim@unr.edu} (K.~Kim), {\tt alvo@ut.ee} (A.~Aabloo)}
 
-\maketitle
+%\begin{abstract}
+%We are concerned with a model of ionic polymer-metal composite (IPMC) materials
+%that consists of a coupled system of the Poisson and Nernst-Planck equations, 
+%discretized by means of the finite element method (FEM). We show that due to the 
+%transient character of the problem it is efficient to use adaptive algorithms 
+%that are capable of changing the mesh dynamically in time. We also show 
+%that due to large qualitative and quantitative differences between the 
+%two solution components, it is efficient to approximate them on different 
+%meshes using a novel adaptive multimesh \emph{hp}-FEM. The study is 
+%accompanied with numerous computations and comparisons of the adaptive 
+%multimesh \emph{hp}-FEM with several other adaptive FEM algorithms. 
+%\end{abstract}
+
+%\maketitle
+
+\vspace{4mm}
+
+We would like to thank the referees for their insightful comments 
+that helped to improve the quality of the paper. We did our best to 
+accommodate all of them. This required a substantial effort,
+including the implementation of dimensionless transformation of 
+the equations and re-doing all computations.
 
@@
 
-Section 5.6 was added with a length scale study.
+Section 5.6 addressing these concerns was added.
 
@@
 
-An explanation was added to the images in Figure 1.
+An explanation was added to Figure 1.
 
@@
 
-A reference was added to a previous study where solving the PNP system in 3D was discussed.
+A reference was added to a previous study on solving the PNP system in 3D.
 
@@
 
-This was very good point. The dimensionless form of the equations was derived. $\mathbf{All}$ the
-results were recalculated and each graph and image in the Results section was redone.
+This was very good point. The dimensionless form of the equations was derived. All
+results were re-calculated and each graph and image in the Results section was re-done.
 Instead of using $C$
@@
 is no motivation which favors a hp-FEM discretization over traditional low-order FEM. One
-sentence regarding computational performance or a related comment might be useful ...}
+sentence regarding computational performance or a related comment might be useful~...}
 
-TODO Pavel
+A motivation sentence describing different convergence properties of low-order FEM 
+and hp-FEM was added to the beginning of Section 4 along with a reference.
 
@@
 
-TODO Pavel
+The title of this section was slightly changed (Hermes was left out), so mentioning Hermes here would not be 
+appropriate. However, a better explanation was added to Paragraph 4.1 which describes Hermes.
 
@@
 
-Currently Hermes does not support the time step reduction. However, this is planned to be added
-in future. A comment was also added below (5.5): \emph{At this point,
-the implementation does not support reducing the time step when $e^n \geq \delta$.}
+Adaptive time stepping was not supported in Hermes until mid-February 2011. Recently we have 
+implemented a new method that allows Hermes to perform time integration based on arbitrary Butcher's 
+tables (including adaptivity based on arbitrary embedded Runge-Kutta methods). However, another paper on this subject 
+is in preparation and thus we would prefer not to discuss details in the present paper. 
+The following comment was added below (5.5): \emph{At this point, the implementation does not support
+adaptive time stepping if $e^n\geq \delta$. However, the implementation 
+of advanced adaptive higher-order time-stepping methods is in progress.}
 
@@
 
-TODO Pavel?
+All computations performed in this paper were done using the absolutely stable 
+second-order Crank-Nicolson method. This method does not require any 
+limitation of time step such as the CFL condition. Of course, the 
+accuracy is still an issue and the size of the time step was chosen 
+based on multiple experiments, so that the size of the temporal error 
+was approximately the same as the error in space. The ultimate answer 
+to this issue is adaptive time stepping which is the subject of a forthcoming 
+paper. We have given the size of the time step, and 
+we explained in more detail how the choice of the fixed time step
+for the Crank-Nicolson method was made.
 

### 2011-02-24 model.tex
Correct dimensionless form of the equations
Changes by Pavel.

@@
 \begin{eqnarray}
-  \frac{DC_0}{\lambda_D l}\frac{\partial c}{\partial \tau} + \frac 1L \nabla_d\cdot
+  \frac{DC_0}{\lambda_D l}\frac{\partial c}{\partial \tau} + \frac 1l  \nabla_d\cdot
     \left(-\frac{DC_0}{l}\nabla_dc-c\frac{DC_0}{l}\nabla_d\varphi\right) &=& 0\label{eq:dim1}\\
@@
     -\epsilon\nabla_d^2 c - \epsilon \nabla_d \cdot \left( c\nabla_d \varphi\right)  &=&0,\label{eq:dimensionless-nernst-planck}\\
-  -2\epsilon^2\nabla_d^2\varphi&=&c-1\label{eq:dimensionless-poisson}.
+  -\nabla_d^2\varphi&=&\frac{c-1}{2\epsilon^2}\label{eq:dimensionless-poisson}.
 \end{eqnarray}
@@
 \begin{equation}
-  -2\epsilon^2\int_{\Omega}\nabla_d^2\varphi v^\varphi d\mathbf{x}-\int_{\Omega}cv^\varphi d\mathbf{x}+
-  \int_{\Omega}v^\varphi d\mathbf{x}=0.
+  -\int_{\Omega}\nabla_d^2\varphi v^\varphi d\mathbf{x}-
+  \frac{1}{2\epsilon^2}\left[\int_{\Omega}cv^\varphi d\mathbf{x}-
+  \int_{\Omega}v^\varphi d\mathbf{x}\right]=0.
   \label{eq:poisson-weak1}
@@
 \begin{equation}
-  -2\epsilon^2\int_{\Omega}\nabla_d\varphi\cdot\nabla_d v^\varphi d\mathbf{x}-\int_{\Omega}cv^\varphi d\mathbf{x}+
-  \int_{\Omega}v^\varphi d\mathbf{x}=0.
+  \int_{\Omega}\nabla_d\varphi\cdot\nabla_d v^\varphi d\mathbf{x}-
+  \frac{1}{2\epsilon^2}\left[\int_{\Omega}cv^\varphi d\mathbf{x}-
+  \int_{\Omega}v^\varphi d\mathbf{x}\right]=0.
   \label{eq:poisson-weak-final}
@@
 \begin{equation}
-  F_i^{\varphi}\left(Y\right) = -2\epsilon^2\int_{\Omega} \nabla_d \varphi(Y) \cdot \nabla_d v_i^{\varphi} d\mathbf{x} 
-  - \int_{\Omega} c(Y)v_i^{\varphi} d\mathbf{x} + \int_{\Omega} v_i^{\varphi} d\mathbf{x}
+  F_i^{\varphi}\left(Y\right) = \int_{\Omega} \nabla_d \varphi(Y) \cdot \nabla_d v_i^{\varphi} d\mathbf{x} 
+  -\frac{1}{2\epsilon^2}\left[ \int_{\Omega} c(Y)v_i^{\varphi} d\mathbf{x} -
+   \int_{\Omega} v_i^{\varphi} d\mathbf{x}\right]
   \label{eq:Fphi}
@@
   \frac{\partial F_i^{\varphi}}{\partial y_j^c}(Y) &=&
-  - \int_{\Omega} v_j^c v_i^{\varphi} d\mathbf{x},\\
+  - \frac{1}{2\epsilon^2}\int_{\Omega} v_j^c v_i^{\varphi} d\mathbf{x},\\
   \frac{\partial F_i^{\varphi}}{\partial y_j^{\varphi}}(Y) &=&
-  -2\epsilon^2\int_{\Omega} \nabla_d v_j^{\varphi} \cdot \nabla_d v_i^{\varphi} d\mathbf{x}\label{eq:dFphidyphi}.
+  \int_{\Omega} \nabla_d v_j^{\varphi} \cdot \nabla_d v_i^{\varphi} d\mathbf{x}\label{eq:dFphidyphi}.
 \end{eqnarray}
@@
 
-\section{Adaptive $hp$-FEM and the Open-Source Library Hermes}
+\section{Adaptive $hp$-FEM}
 \label{sec:hermes}
+
+The $hp$-FEM is a modern version of the Finite Element Method (FEM) that is 
+capable of exponential convergence (the approximation error drops exponentially 
+as new degrees of freedom are added during adaptivity) while standard FEM can 
+only attain algebraic (polynomial) convergence rates which are much slower
+[REFERENCE SOLIN-BOOK-2003].
 
@@
 
-However, none of these approaches is suitable for
+However, these approaches are in general not very well suited for 
 multiphysics coupled problems or higher-order finite element methods: 

### 2011-02-25 response.tex
Revision1 done

@@
 we explained in more detail how the choice of the fixed time step
-for the Crank-Nicolson method was made.
+for the Crank-Nicolson method was made in the very beginning
+of Section 5.
 

### 2011-02-25 intro.tex
Revision1 done

@@
 decades for their potential to serve as noiseless mechanoelectrical and electromechanical 
-transducers \cite{basu1997membrane,shahinpoor2001smartmat,
+transducers \cites{basu1997membrane,shahinpoor2001smartmat,
 nasser2002applied,newbury2003intelligent, wallmersperger2007appliedphysics,

### 2011-02-25 model.tex
Revision1 done

@@
+\newpage
 \section{Model}\label{sec:model}
@@
 Performing integration by parts and taking into account the boundary 
-conditions for $\phi$, we obtain
+conditions for $\varphi$, we obtain
 \begin{equation}
@@
 as new degrees of freedom are added during adaptivity) while standard FEM can 
-only attain algebraic (polynomial) convergence rates which are much slower
-[REFERENCE SOLIN-BOOK-2003].
+only attain algebraic (polynomial) convergence rates which are much slower~\cite{Hermes-book}.
 

### 2011-02-25 results.tex
Changes by Pavel.
Revision1 done

@@
 the final time of $3.0$~s was chosen as it is close to the time
-scaling constant~$\tau$.
+scaling constant~$\tau$.  The time step was chosen after many
+numerical experiments in such a way that the error
+in time was approximately the same as the error in
+space. The implementation of advanced adaptive
+implicit higher-order Runge-Kutta methods is in progress.
 
@@
 example. At this point, the implementation does not support
-reducing the time step when $e^n\geq \delta$. The calculated $e_c^n$ and $e_\varphi^n$ are shown in Fig.~\ref{fig:cphirelerr}.
+adaptive time stepping if $e^n\geq \delta$. However, the implementation 
+of advanced adaptive higher-order time-stepping methods is in progress.
+The calculated $e_c^n$ and $e_\varphi^n$ are shown in Fig.~\ref{fig:cphirelerr}.
 The HP\_ANISO problem size and computing time with and without time step control

### 2011-03-21 intro.tex
The final version

@@
 %\newpage
-%The derived and implemented model helps to predict the actuation of the
-%material. Furthermore, it is expected that the \emph{hp}-FEM implementation
-%results in a smaller problem size, thus likely allowing faster calculation
-%in both 2D and 3D domains.
 
@@
 on individual meshes equipped with mutually independent adaptivity 
-mechanisms. The PNP model is presented in Section \ref{sec:model} where also its weak 
-formulation for the Newton's method is derived. Section \ref{sec:hermes}
-presents a brief overview of a novel adaptive multimesh $hp$-FEM 
+mechanisms. The PNP model is presented in Section~\ref{sec:model} where also its weak 
+formulation for the Newton's method is derived. Section~\ref{sec:hermes}
+presents a brief overview of a novel adaptive multi-mesh $hp$-FEM 
 method~\cite{solin2010monolithic,solin2010adaptive,dubcova2010space,solini2010adaptive}
 that is used to solve the 
-problem numerically. Numerical results and comparisons are presented in Section 
-\ref{sec:results}, and conclusion and outlook are drawn in Section \ref{sec:conc}.
+problem numerically. Numerical results and comparisons are presented in Section~\ref{sec:results}, 
+and conclusion and outlook are drawn in Section~\ref{sec:conc}.

### 2011-03-21 model.tex
The final version

@@
 \end{equation}
-Performing integration by parts and taking into account the boundary 
+After performing integration by parts and taking into account the boundary 
 conditions for $\varphi$, we obtain
@@
 Here $Y^{n+1}$ is a coefficient vector of length $N^c + N^{\varphi}$ comprising the unknown 
-solution coefficients $y_k^{C}$ and $y_k^{\varphi}$ (in this order). We will also be 
+solution coefficients $y_k^{c}$ and $y_k^{\varphi}$ (in this order). We will also be 
 using $c^n = c(Y^n)$ and $\varphi^n = \varphi(Y^n)$ for the previous time step solutions.
@@
 $F(Y) = 0$.
-
-%\newpage
 
@@
 
-% Pavel
-% The reader might loose at this point the interest in reading further
-% since there is no motivation which favros a hp-FEM discretization over traditional
-% low order FEM. One sentence regarding computational performance
-% or a related comment might be useful...
 Automatic adaptivity in higher-order finite element methods (\emph{hp}-FEM) 

### 2011-03-21 pugal-cicp2010.tex
Revision1 done
The final version

--- 2010-10-25 pugal-esco2010.tex
@@
 
-%\journal{Applied Mathematics and Computation}
 \usepackage{graphicx}
@@
 \usepackage{amsrefs}
-%\usepackage{subfig}
 
@@
 
-%\title{\emph{hp}-Finite Element Model of Poisson and Nernst-Planck\\ System of Equations}
 \title{Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM}
@@
 
-%\author[unrme,tartu]{D.~Pugal}
-%\ead{david.pugal@gmail.com}
-%
-%\author[unrmath,czech]{P.~Solin\corref{cor2}}
-%\ead{solin@unr.edu}
-%
-%\author[unrme]{K.~J.~Kim\corref{cor1}}
-%\ead{kwangkim@unr.edu}
-%
-%\author[tartu]{A.~Aabloo}
-%\ead{alvo@ut.ee}
-%
-%\address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
-%\address[unrmath]{Department of Mathematics and Statistics,
-%University of Nevada, Reno, NV, U.S.A.}
-%\address[czech]{Institute of Thermomechanics, Prague, Czech Republic}
-%\address[tartu]{Institute of Technology, Tartu University, Estonia}
-%
-%\cortext[cor1]{Corresponding author}
-%\cortext[cor2]{Principal corresponding author}
-
 \begin{abstract}
@@
 
-%\begin{keyword}
-%\keywords{Ionic polymer-metal composites, IPMC, Nernst-Planck equation, Poisson equation,
-%finite element method, space-time adaptivity, multimesh \emph{hp}-FEM }
-%\end{keyword}
-
-%see http://www.ams.org/mathscinet/msc/msc2010.html?t=35Qxx&btn=Current
-
 \ams{35Q84, 35Q05, 35J47}
 \keywords{Ionic polymer-metal composites, IPMC, Nernst-Planck equation, Poisson equation,
-finite element method, FEM, adaptive multimesh \emph{hp}-FEM }
+finite element method, FEM, adaptive multi-mesh \emph{hp}-FEM }
 \maketitle
-
-%\end{frontmatter}
 
@@
 The third author acknowledges the financial support of the U.S. Office of Naval Research 
-under Award N000140910218.
+under Award N000140910218. The fourth author acknowledges the financial support of
+the Estonian Ministry of Education, grant \#SF0180008s08.
 
-%\begin{thebibliography}{99}
-%\bibitem{\ldots}..
+\newpage
 
-%\end{thebibliography}
-
-%\bibliographystyle{amsrs}    % Bibliography: Author-Date system
+\bibliographystyle{amsrn}    % Bibliography: Author-Date system
 \bibliography{pugal-esco2010}      % pls. call your database here

### 2011-03-22 pugal-cicp2010.tex
Submitted final version

@@
 \bibliographystyle{amsrn}    % Bibliography: Author-Date system
-\bibliography{pugal-esco2010}      % pls. call your database here
+%\bibliography{pugal-cicp2010}      % pls. call your database here
+\begin{bibdiv}
+\begin{biblist}
+
+\bib{basu1997membrane}{article}{
+      author={Basu, S.},
+      author={Sharma, M.M.},
+       title={{An improved space-charge model for flow through charged
+  microporous membranes}},
+        date={1997},
+     journal={Journal of Membrane Science},
+      volume={124},
+      number={1},
+       pages={77\ndash 91},
+}
+
+\bib{bazant2004diffuse}{article}{
+      author={Bazant, M.Z.},
+      author={Thornton, K.},
+      author={Ajdari, A.},
+       title={{Diffuse-charge dynamics in electrochemical systems}},
+        date={2004},
+        ISSN={1550-2376},
+     journal={Physical Review E},
+      volume={70},
+      number={2},
+       pages={21506},
+}
+
+\bib{dubcova2010space}{article}{
+      author={Dubcova, L.},
+      author={Solin, P.},
+      author={Cerveny, J.},
+      author={Kus, P.},
+       title={{Space and Time Adaptive Two-Mesh $hp$-Finite Element Method for
+  Transient Microwave Heating Problems}},
+        date={2010},
+     journal={Electromagnetics},
+      volume={30},
+      number={1},
+       pages={23\ndash 40},
+}
+
+\bib{nasser2002applied}{article}{
+      author={Nemat-Nasser, S.},
+       title={Micromechanics of actuation of ionic polymer-metal composites},
+        date={2002},
+     journal={Journal of Applied Physics},
+      volume={92},
+      number={5},
+       pages={2899\ndash 2915},
+}
+
+\bib{newbury2003intelligent}{article}{
+      author={Newbury, K.M.},
+      author={Leo, D.J.},
+       title={{Linear electromechanical model of ionic polymer transducers-Part
+  I: Model Development}},
+        date={2003},
+     journal={Journal of Intelligent Material Systems and Structures},
+      volume={14},
+      number={6},
+       pages={333},
+}
+
+\bib{pugal2009}{inproceedings}{
+      author={Pugal, D.},
+      author={Aabloo, A.},
+      author={Kim, K.~J.},
+       title={Dynamic surface resistance model of ipmc},
+        date={2009},
+      editor={Ounaies, Zoubeida},
+      editor={Li, Jiangyu},
+      volume={7289},
+   publisher={SPIE},
+       pages={72891E},
+}
+
+\bib{pugal2010polymer}{article}{
+      author={Pugal, D.},
+      author={Jung, K.},
+      author={Aabloo, A.},
+      author={Kim, K.J.},
+       title={{Ionic polymer-metal composite mechanoelectrical transduction:
+  review and perspectives}},
+        date={2010},
+     journal={Polymer international},
+      volume={59},
+      number={3},
+       pages={279\ndash 289},
+}
+
+\bib{pugal2010spie3d}{inproceedings}{
+      author={Pugal, D.},
+      author={Kim, K.~J.},
+      author={Aabloo, A.},
+       title={Modeling the transduction of ipmc in 3d configurations},
+        date={2010},
+      editor={Ounaies, Zoubeida},
+      editor={Li, Jiangyu},
+      volume={7644},
+   publisher={SPIE},
+       pages={76441T},
+}
+
+\bib{pugal2008appliedphysics}{article}{
+      author={Pugal, D.},
+      author={Kim, K.~J.},
+      author={Punning, A.},
+      author={Kasemagi, H.},
+      author={Kruusmaa, M.},
+      author={Aabloo, A.},
+       title={A self-oscillating ionic polymer-metal composite bending
+  actuator},
+        date={2008},
+     journal={Journal of Applied Physics},
+      volume={103},
+      number={8},
+       pages={084908},
+}
+
+\bib{shahinpoor2001smartmat}{article}{
+      author={Shahinpoor, M.},
+      author={Kim, K.~J.},
+       title={Ionic polymer-metal composites: I. fundamentals},
+        date={2001},
+     journal={Smart Materials and Structures},
+      volume={10},
+      number={4},
+       pages={819},
+}
+
+\bib{solin2010pde}{article}{
+      author={Solin, P.},
+      author={Andrs, D.},
+      author={Cerveny, J.},
+      author={Simko, M.},
+       title={{PDE-independent adaptive $hp$-FEM based on hierarchic extension
+  of finite element spaces}},
+        date={2010},
+     journal={Journal of computational and applied mathematics},
+      volume={233},
+      number={12},
+       pages={3086\ndash 3094},
+}
+
+\bib{solin2010monolithic}{article}{
+      author={Solin, P.},
+      author={Cerveny, J.},
+      author={Dubcova, L.},
+      author={Andrs, D.},
+       title={{Monolithic discretization of linear thermoelasticity problems
+  via adaptive multimesh hp-FEM}},
+        date={2010},
+     journal={Journal of computational and applied mathematics},
+      volume={234},
+      number={7},
+       pages={2350\ndash 2357},
+}
+
+\bib{solini2010adaptive}{article}{
+      author={Solin, P.},
+      author={Dubcova, L.},
+      author={Dolezel, I.},
+       title={{Adaptive $hp$-FEM with arbitrary-level hanging nodes for
+  Maxwell’s equations}},
+        date={2010},
+     journal={Advances in Applied Mathematics and Mechanics},
+      volume={2},
+      number={4},
+       pages={518\ndash 532},
+}
+
+\bib{solin2010adaptive}{article}{
+      author={Solin, P.},
+      author={Dubcova, L.},
+      author={Kruis, J.},
+       title={{Adaptive $hp$-FEM with dynamical meshes for transient heat and
+  moisture transfer problems}},
+        date={2010},
+     journal={Journal of computational and applied mathematics},
+      volume={233},
+      number={12},
+       pages={3103\ndash 3112},
+}
+
+\bib{Hermes-book}{book}{
+      author={Solin, P.},
+      author={Segeth, K.},
+      author={Dolezel, I.},
+       title={Higher-order finite element methods},
+   publisher={Chapman \& Hall / CRC Press},
+        date={2003},
+}
+
+\bib{valli2002control}{article}{
+      author={Valli, A. M.~P.},
+      author={Carey, G.~F.},
+      author={Coutinho, A.},
+       title={{Control strategies for timestep selection in simulation of
+  coupled viscous flow and heat transfer}},
+        date={2002},
+     journal={Communications in Numerical Methods in Engineering},
+      volume={18},
+      number={2},
+       pages={131\ndash 139},
+}
+
+\bib{wallmersperger2007appliedphysics}{article}{
+      author={Wallmersperger, T.},
+      author={Leo, D.~J.},
+      author={Kothera, C.~S.},
+       title={Transport modeling in ionomeric polymer transducers and its
+  relationship to electromechanical coupling},
+        date={2007},
+     journal={Journal of Applied Physics},
+      volume={101},
+      number={2},
+       pages={024912},
+}
+
+\end{biblist}
+\end{bibdiv}
 

### 2014-07-01 results.tex

@@
 
-An example of the solution at $t=0.1\ s$ and $t=3.0\ s$ 
+An example of the solution at $t=0.1$~s and $t=3.0$~s
 calculated with the HP\_ANISO refinement mode is shown
@@
 \end{figure}
-
-%\newpage
 
@@
 \subsection{Comparison of single-mesh and multi-mesh $hp$-FEM}
-% David: Error convergence plots here.
 Running the simulation with different adaptivity modes 
@@
 Figs.~\ref{fig:isoanisopdof} and \ref{fig:isoanisopcpu} present a similar 
-comparsion for the P\_ISO, P\_ANISO, and HP\_ANISO\_P modes. Recall that these 
+comparison for the P\_ISO, P\_ANISO, and HP\_ANISO\_P modes. Recall that these 
 computations use a different initial mesh that was a-priori refined in space.
@@
 where $\text{width}_{\Omega_1}$ is the width of the boundary. The given boundary is effectively
-a linear incrase of the voltage from $\phi_{\Omega_1}\left(x = 0 \right)=0.5\ V$ to
-$\phi_{\Omega_1}\left(x=\text{width}_{\Omega_1}\right) = 1.0\ V$.
+a linear increase of the voltage from $\phi_{\Omega_1}\left(x = 0 \right)=0.5$~V to
+$\phi_{\Omega_1}\left(x=\text{width}_{\Omega_1}\right) = 1.0$~V.
 Now the concentration gradient $\nabla c$ and the voltage gradient $\nabla \varphi$ are no
@@
 The calculated scaled values $c$ and $\varphi$ in $\Omega$ and corresponding meshes and polynomial
-degrees of the elements at $t=0.1\ s$ are shown in Fig.~\ref{fig:cphi-orders}.
+degrees of the elements at $t=0.1$~s are shown in Fig.~\ref{fig:cphi-orders}.
 Notice that the solution
@@
 peak exists (compare to Fig.~\ref{fig:poly}).
-At $t=3.0\ s$, the shape of the solutions $c$ and $\varphi$ are similar to the one
+At $t=3.0$~s, the shape of the solutions $c$ and $\varphi$ are similar to the one
 in Fig.~\ref{fig:cphi-2} and therefore the polynomial space and mesh gets adapted
@@
 In all the previous simulations, the Debye screening length was determined by  the constants in
-Table~\ref{Table:used-constants} and Eq.~\ref{eq:debye}: $\lambda_D=1.7\ \mu m$. It is known that computation gets increasingly
+Table~\ref{Table:used-constants} and Eq.~\eqref{eq:debye}: $\lambda_D=1.7\ \mu m$. It is known that computation gets increasingly
 difficult when reducing the value of $\lambda_D$.
@@
 as a function of the Debye length and Fig.~\ref{fig:debye_cpu} shows cumulative CPU time as a function
-of the Debye length. The simulations up to $0.52\ nm$
+of the Debye length. The simulations up to $0.52$~nm
 screening length were carried out on
-the initial coarse mesh. However, from $\lambda_D > 0.52\ nm$, the finer initial mesh had to
+the initial coarse mesh. However, from $\lambda_D > 0.52$~nm, the finer initial mesh had to
 be used so the existence of the large gradients of the
@@
 \noindent
-The fine mesh allowed simulations with the Debye length down to $0.40\ nm$~m. The calculated
-$c$ and $\varphi$ at $t=\tau$ for $\lambda_D=0.40\ nm$ are shown in Fig.~\ref{fig:cphitau}.
+The fine mesh allowed simulations with the Debye length down to $0.40$~nm. The calculated
+$c$ and $\varphi$ at $t=\tau$ for $\lambda_D=0.40$~nm are shown in Fig.~\ref{fig:cphitau}.
 It appears that when using even finer initial mesh and higher initial polynomial degrees, even
